### 2021-06-22 docs/paper/paper.tex
3D section, pdf

\documentclass{article}

\usepackage{arxiv}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{lipsum}		% Can be removed after putting your text content
\usepackage{graphicx}
\graphicspath{ {./images/} }
\usepackage[square,numbers]{natbib}
\usepackage{doi}

\title{ZPY: Open Source Synthetic Data for Computer Vision}

\author{
	{\hspace{1mm}Hugo Ponte}\thanks{correspondence author} \\ 
	Zumo Labs \\
	\texttt{hugo@zumolabs.ai} \\
	\And
	{\hspace{1mm}Norman Ponte} \\
	Zumo Labs \\
	\texttt{norman@zumolabs.ai} \\
	\And
	{\hspace{1mm}Sammie Crowder} \\
	Zumo Labs \\
	\texttt{sammie@zumolabs.ai} \\
	\And
	{\hspace{1mm}Kory Stiger} \\
	Zumo Labs \\
	\texttt{kory@zumolabs.ai} \\
	\And
	{\hspace{1mm}Steven Pecht} \\
	Zumo Labs \\
	\texttt{steven@zumolabs.ai} \\
	\And
	{\hspace{1mm}Michael Stewart} \\
	Zumo Labs \\
	\texttt{michael@zumolabs.ai} \\
	\And
	{\hspace{1mm}Elena Ponte} \\
	Zumo Labs \\
	\texttt{elena@zumolabs.ai} \\
}

% Uncomment to remove the date
\date{}

\renewcommand{\headeright}{Technical Report}
\renewcommand{\undertitle}{Technical Report}

% PDF metadata
\hypersetup{
pdftitle={ZPY: Open Source Synthetic Data for Computer Vision},
pdfsubject={cs.CV},
pdfauthor={Hugo Ponte, Norman Ponte, Sammie Crowder, Kory Stiger, Steven Pecht, Elena Ponte},
pdfkeywords={Computer Vision, Synthetic Data, Machine Learning, Open Source, Python, Blender},
}

\begin{document}
\maketitle

\begin{abstract}
Synthetic data presents a unique solution to the huge data requirements of computer vision with deep learning. In this work, we present zpy \footnote{All code is available on GitHub at \url{http://github.com/ZumoLabs/zpy}}, an open source framework for creating synthetic data. Built on top of Blender, and designed with modularity and readability in mind.
\end{abstract}

\keywords{Computer Vision \and Synthetic Data \and Machine Learning \and Open Source \and Python \and Blender}

% https://www.overleaf.com/learn/latex/Inserting_Images
\begin{figure}[!ht]
	\centering
	\includegraphics[width=\textwidth]{cover.png}
	\caption{Synthetic images of a raspberri pi created with zpy: (A) color image, (B) segmentation image, (C) depth image, (D) prediction image}
	\label{fig:fig1}
\end{figure}

\section{Introduction}
\label{sec:introduction}

Open source machine learning frameworks (references)

Deep learning has exploded in popularity due to large open source frameworks such as tensorflow and pytorch
What is synthetic data (references)

Challenges with synthetic data

Sim2Real Gap and domain randomization

Black box nature of ML

\section{Background}
\label{sec:background}

\subsection{3D}
\label{sec:3d}

3D, short for the three dimensions of space we experience, is a catch-all term used to describe the varied technologies used to create virtual worlds. The technology stack for 3D can be roughly split into two broad categories \emph{asset creation} and \emph{asset scripting}. Asset creation \ref{sec:assetcreation} is the process of creating virtual objects, scenes, and materials. Asset scripting \ref{sec:assetscripting} is the process of controlling those assets and their behavior over time. Both of these technologies require human expertise and artistic talent \ref{sec:humanexpertise}.

\subsubsection{Asset Creation}
\label{sec:assetcreation}

Assets are digital representations of a 3D object. In the engineering and manufacturing world, assets are created using computer aided design (CAD) software such as AutoCAD \citep{autocad}, Solidworks \citep{solidworks}, Onshape \citep{onshape}, and Rhino \citep{rhino}. In the entertainment industry, assets are created using modeling software such as Maya \citep{maya}, 3DSMax \citep{3dsmax}, and Cinema4D \citep{cinema4d}. Modeling and CAD are two different words for the same thing: deciding the connectivity and placement of a graph of points, also called vertices, which define the boundaries of an object. Vertices are connected by edges, and a closed loop creates a polygon known as a face. Many 3D assets can be organized into scenes, which may contain other unique virtual objects such as simulated lights and cameras. Finally, asset creation also encompasses teh process of material creation. The appearance of a virtual object is determined by a material, which may define rules for the reflectivity, specularity, and metallic-ness of the object as a function of lighting conditions.

\subsubsection{Asset Scripting}
\label{sec:assetscripting}

There is a fourth dimmension to our reality which is time. Asset scripting is the process of defining the behavior of assets and scenes over the dimmension of time. One such process is called animation, which consists of an expert human artist pupeteering and deforming a mesh frame by frame to create the illusion of natural movement. Specialized software is often used to automate this task as much as possible, and technologies such as Motion Capture (MoCap) are often used to record the movement of real objects and play those movements back on virtual assets.

Game Engines are software tools which allow for manipulation of assets in a more structured and systematic way by providing software interfaces to control the virtual world. Used extensively in the video game industry after which they were named, examples include Unity \citep{unity3d}, Unreal Engine \citep{unrealengine}, GoDot \citep{godot}, and Roblox \citep{roblox}. These game engines allow for rule-based spawning, animation, and complex interactions between assets in the virtual world.

\subsubsection{Human Expertise}
\label{sec:humanexpertise}

Houdini \citep{houdini} and Blender \citep{blender}

\subsection{Deep Learning}
\label{sec:deeplearning}

Modern deep learning can be implemented in a variety of programming languages including Python, R, Julia, Scala, Ruby, Octave, MATLAB, and even C/C++. Amongst these, Python has emerged as the lingua franca, rising to the top in part due to the popularity of open source frameworks such as TensorFlow \citep{tensorflow}, PyTorch \citep{pytorch}, and Scikit-Learn \citep{scikit-learn}.

\subsection{Synthetic Data}
\label{sec:syntheticdata}

The synthetic data workflow can be broadly divided into three categories: simulation design, generation, and tuning.

BlenderProc, Synthesis, LexSet

\section{Motivation}
\label{sec:motivation}

\subsection{Democratization of Data}

The datasets used by companies today are almost exclusively collected.

Data for ML systems is collected. Only companies that have the scale and have set up the infrastructure to collect and store large datasets will have the datasets required to train models.

A huge market for the selling and reselling of collected data has emerged, which presents an existential threat to privacy.

The high cost of data labeling makes it unavailable to those without huge resources

\subsection{Fairness and Bias}

The real world is biased and unfair.

ML systems trained on this data will reflect the same bias during inference.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{software3.png}
	\caption{Software 3.0: the developer transitions from writing explicit algorithms to creating and curating datasets which are used to train machine learning models.}
	\label{fig:fig2}
\end{figure}

\subsection{Software 3.0}
\label{sec:software3.0}

Data creation as a new paradigm for “programming”.

In the software world today, developers write explicit sets of rules (known as algorithms). These algorithms are then deployed into production systems, which consume input data and output actions.

In the software of tomorrow, developers will curate a dataset which will be used to train a deep learning model. This model will then be deployed into a production system, which will consume input data and output actions. This changes the workflow of developers from explicitly writing rules to instead creating the datasets which are then parsed to create algorithms.

\section{Project Features}
\label{sec:projectfeatures}

TODO

\subsection{Blender Addon}
\label{sec:blenderaddon}

As explained in section X, deep learning is a python-first discipline. If we wish to include deep learning practitioners in the 3D stack it is thus of critical importance that we provide a python interface for the 3D workflow.

\subsection{Cloud Backend}
\label{sec:cloudbackend}

Computing has traditionally relied on Moore’s Law to increase the power of individual computers. In the past decade the individual compute power of a single computer has not increased significantly, and instead the ability to coordinate a large number of individual computers on a single task has become the method for increasing computation. This type of parallel computing has been democratized through the availability of cloud computing platforms such as AWS, GCP, and Azure. However, these platforms remain difficult for the average developer to use effectively, and domain experts are usually required to take software running on a single computer and scale it across many computers in parallel.

Abstracting away the difficulties of the cloud workflow and providing an intuitive and convenient interface for parallelizing computation is thus important for the democratization of deep learning and synthetic data workflows. Much like platforms have emerged for the training and tuning workflows of deep learning, an opportunity exists to create platforms for the generation and tuning workflows of synthetic data.

\subsection{User Interfaces}
\label{sec:cloudbackend}

We provide three different interfaces to interact with our product: an API, a CLI, and a graphical WebApp.

Power users want an API (application programming interface) and CLI (command line interface).

Building a ramp for the bulk of the developer community requires a GUI

\section{Design}
\label{sec:design}

Hidden complexity

When designing software systems, there is usually a tradeoff between flexibility and simplicity. Simplicity is the ability to perform a task with minimal amount of work and a limited understanding of the software package. Flexibility is the ability to support many different tasks and allow for customization.

Random hdri and textures use default random textures unless a specific path is given

Pythonic syntax

One of the core features of Python is the language’s human readable syntax. Python does not enforce function and variable type annotations, which makes it quicker to prototype code.

Functions in zpy are flexible in the arguments that they accept. The `zpy.opject.segment()` function call can accept an object directly of type `bpy.types.Object`, but it will also accept the unique string name of that object.

Extensibility

Zpy modules are separated by dependencies

Zpy modules are independent of each other, a monolithic system is much harder to update and maintain

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{workflow.png}
	\caption{The Synthetic Data Workflow allows for iteration of the dataset.}
	\label{fig:fig3}
\end{figure}

\section{Workflow}
\label{sec:workflow}

See Figure \ref{fig:fig3}.

Design the Sim

Sim is short for simulation.

A sim is controlled through a single run script, which has a single run() function

Relevant parameters are put as kwargs in the run() function, which allows configuration through gin config

Gin configuration allows for modular python library design

Generate the dataset

Datasets are rendered frame by frame. Separate rendering passes are required for segmentation and color images.

Cycles vs Eevee

Evaluate the datasets

Sweeping over dataset hyperparameters (much like sweeping over model architecture parameters)

Fine-tuning pre-trained models as a proxy for dataset performance

Iterate

Least understood part of developing with synthetic data

The promise of AutoML for datasets

\section{Example}
\label{sec:example}

Package detection
Effect of domain randomized lighting
Effect of domain randomized backgrounds
Pre-training w/ real and fine-tuning on synthetic
The Cost of Synthetic Data
Comparison to Data Labeling

\subsection{Lists}
\begin{itemize}
	\item Background material and texture.
	\item Lighting intensity and positioning.
	\item Object material and texture.
	\item Number of objects in view.
\end{itemize}

See results in the Table~\ref{tab:table}.

\begin{table}
	\caption{Sample table title}
	\centering
	\begin{tabular}{lll}
		\toprule
		\multicolumn{2}{c}{Part}                   \\
		\cmidrule(r){1-2}
		Name     & Description     & Size ($\mu$m) \\
		\midrule
		Dendrite & Input terminal  & $\sim$100     \\
		Axon     & Output terminal & $\sim$10      \\
		Soma     & Cell body       & up to $10^6$  \\
		\bottomrule
	\end{tabular}
	\label{tab:table}
\end{table}

\section{Conclusion}
\label{sec:conclusion}

TODO

\bibliographystyle{abbrvnat}
\bibliography{references}

\end{document}

### 2021-06-22 docs/paper/paper.tex
more progress

@@
 
+The full workflow for synthetic data can be reduced into four key steps:
+
+\begin{itemize}
+	\item \emph{Design}.
+	\item \emph{Generation}.
+	\item \emph{Evaluation}.
+	\item \emph{Iteration}.
+\end{itemize}
+
+\subsection{Design}
+\label{sec:worflowdesign}
+
 Design the Sim
@@
 
+\subsection{Generation}
+\label{sec:generation}
+
 Generate the dataset
@@
 
+\subsection{Evaluation}
+\label{sec:evaluation}
+
 Evaluate the datasets
@@
 Fine-tuning pre-trained models as a proxy for dataset performance
+
+\subsection{Iteration}
+\label{sec:iteration}
 
@@
 Package detection
-Effect of domain randomized lighting
-Effect of domain randomized backgrounds
-Pre-training w/ real and fine-tuning on synthetic
-The Cost of Synthetic Data
-Comparison to Data Labeling
 
-\subsection{Lists}
 \begin{itemize}
@@
 
-See results in the Table~\ref{tab:table}.
+\subsection{Domain Randomization}
+\label{sec:domainrandomization}
 
-\begin{table}
-	\caption{Sample table title}
-	\centering
-	\begin{tabular}{lll}
-		\toprule
-		\multicolumn{2}{c}{Part}                   \\
-		\cmidrule(r){1-2}
-		Name     & Description     & Size ($\mu$m) \\
-		\midrule
-		Dendrite & Input terminal  & $\sim$100     \\
-		Axon     & Output terminal & $\sim$10      \\
-		Soma     & Cell body       & up to $10^6$  \\
-		\bottomrule
-	\end{tabular}
-	\label{tab:table}
-\end{table}
+Effect of domain randomized lighting
+
+Effect of domain randomized backgrounds
+
+\subsection{Training Curicculum}
+\label{sec:curicculum}
+
+Pre-training w/ real and fine-tuning on synthetic
+
+Training only on synthetic
+
+Training on mixed synthetic and real
 

### 2021-06-22 docs/paper/paper.tex
webapp image

@@
 \usepackage{doi}
+
+\usepackage{xcolor}
+\usepackage{listings}		% code
+\definecolor{codegreen}{rgb}{0,0.6,0}
+\definecolor{codegray}{rgb}{0.5,0.5,0.5}
+\definecolor{codepurple}{rgb}{0.58,0,0.82}
+\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
+
+\lstdefinestyle{mystyle}{
+    backgroundcolor=\color{backcolour},   
+    commentstyle=\color{codegreen},
+    keywordstyle=\color{magenta},
+    numberstyle=\tiny\color{codegray},
+    stringstyle=\color{codepurple},
+    basicstyle=\ttfamily\footnotesize,
+    breakatwhitespace=false,         
+    breaklines=true,                 
+    captionpos=b,                    
+    keepspaces=true,                 
+    numbers=left,                    
+    numbersep=5pt,                  
+    showspaces=false,                
+    showstringspaces=false,
+    showtabs=false,                  
+    tabsize=2
+}
+
+\lstset{style=mystyle}
 
@@
 	\includegraphics[width=\textwidth]{cover.png}
-	\caption{Synthetic images of a raspberri pi created with zpy: (A) color image, (B) segmentation image, (C) depth image, (D) prediction image}
+	\caption{Synthetic images of a raspberri pi created with zpy: (A) color image, (B) segmentation image, (C) depth image.
+These images are used to train a deep learning model, which predicts bounding boxes on key components as seen in the (D) prediction image}
 	\label{fig:fig1}
@@
 In the entertainment industry, assets are created using modeling software such as Maya \citep{maya}, 3DSMax \citep{3dsmax}, and Cinema4D \citep{cinema4d}.
-Modeling and CAD are two different words for the same thing: deciding the connectivity and placement of a graph of points, also called vertices, which define the boundaries of an object.
+Modeling and CAD are two different words for the same thing: deciding the connectivity and placement of a graph of points, also called vertices, which define the surface of an object.
 Vertices are connected by edges, and a closed loop creates a polygon known as a face.
 Many 3D assets can be organized into scenes, which may contain other unique virtual objects such as simulated lights and cameras.
-Finally, asset creation also encompasses teh process of material creation.
+Finally, asset creation also encompasses the process of material creation.
 The appearance of a virtual object is determined by a material, which may define rules for the reflectivity, specularity, and metallic-ness of the object as a function of lighting conditions.
@@
 The datasets used by companies today are almost exclusively collected.
+Images and annotations are gradually saved as they are generated by users of a product.
+Collecting a dataset large enough to train a robust machine learning model can take years.
 
-Data for ML systems is collected. Only companies that have the scale and have set up the infrastructure to collect and store large datasets will have the datasets required to train models.
+Only companies that have the scale and have set up the infrastructure to collect and store large datasets will have the datasets required to train models.
 
-A huge market for the selling and reselling of collected data has emerged, which presents an existential threat to privacy.
+In order to compete, small or newly formed companies often resort to purchasing data from a third party supplier.
+This market for the selling and reselling of collected data presents an existential threat to privacy.
+Though some regulations have emerged, famously GDPR in Europe, these have yet to change the landscape of the market for collected data.
 
@@
 
-TODO
+Given
 
@@
 \subsection{User Interfaces}
-\label{sec:cloudbackend}
+\label{sec:userinterfaces}
 
-We provide three different interfaces to interact with our product: an API, a CLI, and a graphical WebApp.
+We provide three different interfaces to interact with our product: a Python API \ref{lst:api}, a CLI \ref{lst:cli}, and a graphical WebApp \ref{fig:webapp}.
+Power users want an API (application programming interface) and CLI (command line interface).
+Building a ramp for the bulk of the developer community requires a GUI
 
-Power users want an API (application programming interface) and CLI (command line interface).
+\begin{lstlisting}[language=Python,caption={Generating a dataset using the zpy python API.},label={lst:api}]
+import zpy
+zpy.generate()
+\end{lstlisting}
 
-Building a ramp for the bulk of the developer community requires a GUI
+\begin{lstlisting}[language=bash,caption={Generating a dataset using the zpy CLI},label={lst:cli}]
+# First you will need to log in and set the project (image generation gets billed according to project)
+zpy login $USERNAME 
+zpy project set $PROJECT_UUID
+
+# Generate the dataset
+zpy create dataset "redbull cans and packs" can_v6 num_images 1000
+\end{lstlisting}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{webapp.png}
+	\caption{A visual interface for synthetic data creation via a WebApp.}
+	\label{fig:webapp}
+\end{figure}
 
@@
 	\caption{The Synthetic Data Workflow allows for iteration of the dataset.}
-	\label{fig:fig3}
+	\label{fig:workflow}
 \end{figure}
@@
 
-See Figure \ref{fig:fig3}.
-
-The full workflow for synthetic data can be reduced into four key steps:
-
-\begin{itemize}
-	\item \emph{Design}.
-	\item \emph{Generation}.
-	\item \emph{Evaluation}.
-	\item \emph{Iteration}.
-\end{itemize}
+The full workflow for synthetic data can be reduced into four key steps: \emph{Design} \ref{sec:worflowdesign}, \emph{Generation} \ref{sec:generation}, \emph{Evaluation} \ref{sec:evaluation}, \emph{Iteration} \ref{sec:iteration}.
+The synthetic data workflow is similar to the workflow when using collected data, with the key exception that it allows for iteration on the dataset itself \ref{fig:workflow}.
 
@@
 
-Design the Sim
-
-Sim is short for simulation.
-
-A sim is controlled through a single run script, which has a single run() function
-
-Relevant parameters are put as kwargs in the run() function, which allows configuration through gin config
-
-Gin configuration allows for modular python library design
+The first step in the syntehtic data workflow is to design and create the sim, short for simulation.
+A sim is a collection of assets controlled through a single script.
+The run() function in the script acts as the point of entry for any generation process.
+Relevant parameters are put as kwargs in the run() function, which allows configuration through gin-config, a python package for configuration of python libraries.
 
@@
 
-Generate the dataset
-
 Datasets are rendered frame by frame. Separate rendering passes are required for segmentation and color images.
 
-Cycles vs Eevee
+Datasets can be rendered locally directly inside the Blender GUI.
+This allows for easy debugging when developing a sim.
+Once it is working locally, a sim can be exported into a zip file which will contain all the asset dependencies required.
+This zip file can be uploaded to the cloud with any of the user interfaces described in \ref{sec:userinterfaces}.
+
+Dataset are then generated in the cloud \ref{sec:cloudbackend}.
+
+We provide workflows for packaging several smaller datasets into a single larger dataset, as well as sorting individual datapoints into test, train, and validation buckets.
 
@@
 \label{sec:evaluation}
-
-Evaluate the datasets
 
@@
 \label{sec:iteration}
-
-Iterate
 

### 2021-06-22 cli/cli.py
add logs calls for sims and jobs

@@ -488,6 +488,26 @@ def upload_sim(name, path, project=None):
             click.secho(str(e.response.json()), fg="red", err=True)
 
 
+@sim_group.command("logs")
+@click.argument("name")
+@click.argument(
+    "path",
+    type=click.Path(exists=True, file_okay=False, writable=True, resolve_path=True),
+)
+def logs_sim(name, path):
+    from cli.logs import fetch_logs
+
+    try:
+        fetch_logs("sims", name, path)
+        click.echo(f"Downloaded {path}/[info/debug/error].log from '{name}'.")
+    except requests.exceptions.HTTPError as e:
+        click.secho(f"Failed to fetch logs: {e}", fg="red", err=True)
+        if e.response.status_code == 400:
+            click.secho(str(e.response.json()), fg="red", err=True)
+    except NameError as e:
+        click.secho(f"Failed to fetch logs: {e}", fg="yellow", err=True)
+
+
 # ------- ACCOUNT
 
 
@@ -681,6 +701,26 @@ def create_job(name, operation, filters, configfile, sweepfile, project=None):
                 click.secho(str(e.response.json()), fg="red", err=True)
 
     click.echo(f"Finished creating {len(job_configs)} jobs with name '{name}'")
+
+
+@job_group.command("logs")
+@click.argument("name")
+@click.argument(
+    "path",
+    type=click.Path(exists=True, file_okay=False, writable=True, resolve_path=True),
+)
+def logs_job(name, path):
+    from cli.logs import fetch_logs
+
+    try:
+        fetch_logs("jobs", name, path)
+        click.echo(f"Downloaded {path}/[info/debug/error].log from '{name}'.")
+    except requests.exceptions.HTTPError as e:
+        click.secho(f"Failed to fetch logs: {e}", fg="red", err=True)
+        if e.response.status_code == 400:
+            click.secho(str(e.response.json()), fg="red", err=True)
+    except NameError as e:
+        click.secho(f"Failed to fetch logs: {e}", fg="yellow", err=True)
 
 
 # ------- TRANSFORM

### 2021-06-22 examples/shelf/run.py
Fix code style issues with Black

@@ -10,10 +10,10 @@ import bpy
 import gin
 import zpy
 
-log = logging.getLogger('zpy')
+log = logging.getLogger("zpy")
 
 
-@gin.configurable('run')
+@gin.configurable("run")
 @zpy.blender.save_and_revert
 def run(
     number_of_shelves: Tuple[int] = (2, 6),
@@ -29,57 +29,62 @@ def run(
 
     # Create the saver object
     saver = zpy.saver_image.ImageSaver(
-        description='Shelf of cereal boxes',
+        description="Shelf of cereal boxes",
     )
 
     # Create seg colors
     zpy.color.reset()
-    box_cereal_seg_color = zpy.color.random_color(output_style='frgb')
-    box_distractor_seg_color = zpy.color.random_color(output_style='frgb')
+    box_cereal_seg_color = zpy.color.random_color(output_style="frgb")
+    box_distractor_seg_color = zpy.color.random_color(output_style="frgb")
 
     # HACK: Save the random color idx after creating category colors
     post_category_color_idx = zpy.color.RANDOM_COLOR_IDX + 1
 
     # Add the categories
-    saver.add_category(name='box.cereal',
-                       supercategories=['item', 'box'],
-                       color=box_cereal_seg_color)
-    saver.add_category(name='box.distractor',
-                       supercategories=['item', 'box'],
-                       color=box_distractor_seg_color)
+    saver.add_category(
+        name="box.cereal", supercategories=["item", "box"], color=box_cereal_seg_color
+    )
+    saver.add_category(
+        name="box.distractor",
+        supercategories=["item", "box"],
+        color=box_distractor_seg_color,
+    )
 
     # Pre-create a bunch of random textures
-    random_materials = [zpy.material.random_texture_mat()
-                        for _ in range(number_of_random_materials)]
+    random_materials = [
+        zpy.material.random_texture_mat() for _ in range(number_of_random_materials)
+    ]
 
     # Save the positions of objects so we can jitter them later
-    zpy.objects.save_pose('Camera')
-    zpy.objects.save_pose('Light')
-    zpy.objects.save_pose('Light.001')
-    zpy.objects.save_pose('Light.002')
+    zpy.objects.save_pose("Camera")
+    zpy.objects.save_pose("Light")
+    zpy.objects.save_pose("Light.001")
+    zpy.objects.save_pose("Light.002")
 
     # Run the scene.
     for frame in zpy.blender.step():
 
[…]

### 2021-06-23 cli/cli.py
add environment adding and swapping

@@ -5,7 +5,7 @@ import requests
 from requests.auth import HTTPBasicAuth
 from table_logger import TableLogger
 
-from cli.config import initialize_config, read_config, write_config, get_endpoint
+from cli.config import initialize_config, read_config, write_config, add_env, swap_env
 from cli.loader import Loader
 from cli.utils import parse_args, resolve_sweep, use_project, print_list_as_columns
 from zpy.files import read_json, to_pathlib_path
@@ -44,29 +44,6 @@ def cli_help():
         "github - https://github.com/ZumoLabs/zpy\n"
         "docs   - https://github.com/ZumoLabs/zpy/tree/main/docs/cli"
     )
-
-
-@cli.command("env")
-@click.argument("env", type=click.Choice(["local", "stage", "prod"]))
-def set_env(env):
-    """switch target environment
-
-    This command allows zumo labs developers to swap the endpoint that the
-    cli communicates with. Unlikely to be relevant for non-zumo devs.
-
-    Args:
-        env (str): new environment for endpoint
-    """
-    config = read_config()
-    old_env, old_endpoint = config["ENVIRONMENT"], config["ENDPOINT"]
-    config["ENVIRONMENT"] = env
-    config["ENDPOINT"] = get_endpoint(env)
-    config["TOKEN"] = None
-    write_config(config)
-    click.echo("Swapped environment:")
-    click.echo(f"  {old_env} -> {config['ENVIRONMENT']}")
-    click.echo(f"  {old_endpoint} -> {config['ENDPOINT']}")
-    click.echo("zpy login to fetch token")
 
 
 @cli.command("login")
@@ -114,6 +91,56 @@ def version():
     import zpy
 
     click.echo(f"Version: {zpy.__version__}")
+
+
+# ------- ENV
+
+
+@cli.group("env")
+def env_group():
+    """environment configuration.
+
+    Configure the environment for backend calls.
+    """
+    pass
+
+
+@env_group.command("set")
+@click.argument("env")
+def set_env(env):
+    """switch target environment
+
+    This command allows zumo labs developers to swap the endpoint that the cli communicates with.
+
+    Args:
+        env (str): new environment for endpoint
+    """
+    config = read_config()
+    old_env, old_endpoint = config["ENVIRONMENT"], config["ENDPOINT"]
+    swap_env(env)
+    config = read_config()
+    click.echo("Swapped environment:")
[…]

### 2021-06-23 cli/config.py

@@ -2,25 +2,8 @@ from zpy.files import to_pathlib_path
 import os
 import yaml
 
-ENDPOINTS = {
-    "local": "http://localhost:8000",
-    "stage": "https://ragnarok.stage.zumok8s.org",
-    "prod": "https://ragnarok.zumok8s.org",
-}
+ENDPOINT = "https://ragnarok.zumok8s.org"
 CONFIG_FILE = "~/.zpy/config.yaml"
-
-
-def get_endpoint(env):
-    """get endpoint
-
-    Given an env return endpoint
-    Args:
-        env (str): desired env
-
-    Returns:
-        url (str): endpoint for env
-    """
-    return ENDPOINTS[env]
 
 
 def initialize_config():
@@ -33,26 +16,28 @@ def initialize_config():
     path = to_pathlib_path(os.path.expanduser(CONFIG_FILE))
     if path.exists():
         return
-    CONFIG = {"ENVIRONMENT": "prod", "TOKEN": None, "ENDPOINT": ENDPOINTS["prod"]}
+    CONFIG = {"ENVIRONMENT": "prod", "TOKEN": None, "ENDPOINT": ENDPOINT}
     path.parent.mkdir(parents=True, exist_ok=True)
     write_config(CONFIG)
 
 
-def read_config():
+def read_config(file=CONFIG_FILE):
     """read config
 
     Read zpy cli configuration file.
 
+    Args:
+        env: which enviroment to read config for
     Returns:
         config: dictionary of current configuration
     """
-    path = to_pathlib_path(os.path.expanduser(CONFIG_FILE))
+    path = to_pathlib_path(os.path.expanduser(file))
     with path.open() as f:
         config = yaml.load(f, Loader=yaml.FullLoader)
     return config
 
 
-def write_config(config):
+def write_config(config, file=CONFIG_FILE):
     """write config
 
     Write zpy cli configuration file.
@@ -60,6 +45,33 @@ def write_config(config):
     Args:
         config (dict): new configuration to write
     """
-    path = to_pathlib_path(os.path.expanduser(CONFIG_FILE))
+    path = to_pathlib_path(os.path.expanduser(file))
     with path.open("w") as f:
         yaml.dump(config, f)
+
+
+def add_env(name, endpoint):
+    """add environment
+
+    Add a new environment configuration file.
+
+    Args:
+        name: name of the environment
+        endpoint: endpoint for the new enviroment
+    """
[…]

### 2021-06-23 examples/seg_vertex_group_cube/run.py
vertex group segmentation

@@ -1,0 +1,50 @@
+""" Uses default cube to show segmentation using vertex groups. """
+
+import logging
+from pathlib import Path
+
+import bpy
+import zpy
+
+log = logging.getLogger('zpy')
+
+
+def run():
+
+    # The default cube when you open a new Blender file
+    cube = bpy.data.objects['Cube']
+    
+    # Random boiler plate required to render out images
+    zpy.material.make_aov_material_output_node(obj=cube, style='category')
+    cube.data.sculpt_vertex_colors.new(name='category')
+
+    # Make some random segmentation colors
+    segmentation_color_a = zpy.color.random_color(output_style='frgba')
+    segmentation_color_b = zpy.color.random_color(output_style='frgba')
+
+    # Cubes have 8 vertices, split it into two vertex groups
+    cube.vertex_groups.new(name='sideA').add([0, 1, 4, 5], weight=1.0, type='ADD')
+    cube.vertex_groups.new(name='sideB').add([2, 3, 6, 7], weight=1.0, type='ADD')
+    
+    for vertex in cube.data.vertices:
+        # Color half the cube one color
+        if cube.vertex_groups['sideA'].index == vertex.groups[0].group:
+            cube.data.sculpt_vertex_colors['category'].data[vertex.index].color = segmentation_color_a
+        # and the other one the other color
+        elif cube.vertex_groups['sideB'].index == vertex.groups[0].group:
+            cube.data.sculpt_vertex_colors['category'].data[vertex.index].color = segmentation_color_b
+            
+    # Render out an image
+    zpy.render.render(
+        rgb_path=Path('/tmp/output/color_image.png'),
+        cseg_path=Path('/tmp/output/segmentation_image.png'),
+    )
+
+
+if __name__ == "__main__":
+
+    # Set the logger levels
+    zpy.logging.set_log_levels('info')
+
+    # Run the sim
+    run()

### 2021-06-23 docs/paper/paper.tex
Updated background section

@@
 
-3D, short for the three dimensions of space we experience, is a catch-all term used to describe the varied technologies used to create virtual worlds.
-The technology stack for 3D can be roughly split into two broad categories \emph{asset creation} and \emph{asset scripting}.
-Asset creation \ref{sec:assetcreation} is the process of creating virtual objects, scenes, and materials.
-Asset scripting \ref{sec:assetscripting} is the process of controlling those assets and their behavior over time.
-Both of these technologies require human expertise and artistic talent \ref{sec:humanexpertise}.
+3D, short for the three dimensions of space we live in, is a catch-all term used to describe the varied technologies used to create virtual worlds.
+The technology stack for 3D can be roughly split into two broad categories: \emph{asset creation} and \emph{asset scripting}.
+Asset creation \ref{sec:assetcreation} is the process of creating assets: virtual objects, scenes, and materials.
+Asset scripting \ref{sec:assetscripting} is the process of manipulating those assets and their interactions over the fourth dimension of time.
+Decades of progress have resulted in sophisticated software tools that make 3D workflows easier and more automated, but a significant amount of human expertise and artistic talent is still required.
 
@@
 Assets are digital representations of a 3D object.
-In the engineering and manufacturing world, assets are created using computer aided design (CAD) software such as AutoCAD \citep{autocad}, Solidworks \citep{solidworks}, Onshape \citep{onshape}, and Rhino \citep{rhino}.
-In the entertainment industry, assets are created using modeling software such as Maya \citep{maya}, 3DSMax \citep{3dsmax}, and Cinema4D \citep{cinema4d}.
-Modeling and CAD are two different words for the same thing: deciding the connectivity and placement of a graph of points, also called vertices, which define the surface of an object.
-Vertices are connected by edges, and a closed loop creates a polygon known as a face.
-Many 3D assets can be organized into scenes, which may contain other unique virtual objects such as simulated lights and cameras.
-Finally, asset creation also encompasses the process of material creation.
-The appearance of a virtual object is determined by a material, which may define rules for the reflectivity, specularity, and metallic-ness of the object as a function of lighting conditions.
+One type of asset is a mesh: a connected graph of 3D points, also called vertices, which define the surface of an object.
+Vertices are interconnected by edges, and a closed loop of vertices creates a polygon known as a face.
+In the engineering and manufacturing world, meshes are created using computer aided design (CAD) software such as AutoCAD \citep{autocad}, Solidworks \citep{solidworks}, Onshape \citep{onshape}, and Rhino \citep{rhino}.
+In the entertainment industry, meshes are created using modeling software such as Maya \citep{maya}, 3DSMax \citep{3dsmax}, and Cinema4D \citep{cinema4d}.
+
+Whereas a mesh describes the shape and form of an object, a material asset describes the texture and appearance of a virtual object.
+A material may define rules for the reflectivity, specularity, and metallic-ness of the object as a function of lighting conditions.
+Materials are used by shader programs to calculate the exact pixel values to render for each face of a mesh polygon.
+Modeling software will usually come packaged with tools that allow the creation and configuration of materials.
+
+Finally, asset creation also encompasses the process of scene composition.
+Assets can be organized into scenes, which may contain other unique virtual objects such as simulated lights and cameras.
+Deciding where to place assets, especially lights, is still almost entirely done by hand.
+Automatic scene composition remains an outstanding challenge in the 3D technology stack.
 
@@
 
-There is a fourth dimmension to our reality which is time.
-Asset scripting is the process of defining the behavior of assets and scenes over the dimmension of time.
-One such process is called animation, which consists of an expert human artist pupeteering and deforming a mesh frame by frame to create the illusion of natural movement.
-Specialized software is often used to automate this task as much as possible, and technologies such as Motion Capture (MoCap) are often used to record the movement of real objects and play those movements back on virtual assets.
+The fourth perceivable dimension of our reality is time.
+Asset scripting is the process of defining the behaviors of assets within scenes over time.
+One type of asset scripting is called animation, which consists of creating a set of sequential mesh deformations to create the illusion of natural movement.
+Animation is a tedious manual task since every frame must be defined: expert animators spend decades honing their digital puppeteering skills.
+Specialized software is often used to automate this task as much as possible, and technologies such as Motion Capture (MoCap) can be used to record the movement of real objects and play those movements back on virtual assets.
 
-Game Engines are software tools which allow for manipulation of assets in a more structured and systematic way by providing software interfaces to control the virtual world.
+Game Engines are software tools which allow for asset scripting in a more structured and systematic way, mostly by providing software interfaces (e.g.
+code) to control the virtual world.
 Used extensively in the video game industry after which they were named, examples include Unity \citep{unity3d}, Unreal Engine \citep{unrealengine}, GoDot \citep{godot}, and Roblox \citep{roblox}.
 These game engines allow for rule-based spawning, animation, and complex interactions between assets in the virtual world.
+Programming within game engines is a separate skillset to modeling and animating and is usually done by separate engineers within an organization.
 
-\subsubsection{Human Expertise}
-\label{sec:humanexpertise}
+\subsubsection{Blender}
+\label{sec:blender}
 
-Houdini \citep{houdini} and Blender \citep{blender}
+Blender is an open source 3D software tool originally released in 1994 \citep{blender}.
+It has grown steadily over the decades and has become one of the most popular 3D tools available, with a massive online community of users.
+Blender strength in its breadth: it provides simple tools for every part of the 3D workflow, rather than specializing in a narrow slice of the 3D workflow.
+Organizations such as game studios have traditionally preferred specialization, having separate teams of engineers using separate tools, such as Maya for modeling and Unreal Engine for scripting.
+However, the convenience of using a single tool, combined with the advantage of a single engineer being able to see a project start to finish, make a strong case for Blender as the ultimate winner in the 3D software tools race.
+By focusing on open source and community, Blender continues to gain adoption as more and more of the world’s new 3D developers choose to learn Blender over other more specialized tools.
 
-\subsection{Deep Learning}
-\label{sec:deeplearning}
-
-Modern deep learning can be implemented in a variety of programming languages including Python, R, Julia, Scala, Ruby, Octave, MATLAB, and even C/C++.
-Amongst these, Python has emerged as the lingua franca, rising to the top in part due to the popularity of open source frameworks such as TensorFlow \citep{tensorflow}, PyTorch \citep{pytorch}, and Scikit-Learn \citep{scikit-learn}.
+In addition to encompassing the full breadth of the 3D workflow, Blender has the unique strength of using Python as the programming language of choice for asset scripting.
+Python has emerged as the lingua franca for modern deep learning, rising to the top in part due to the popularity of open source frameworks such as TensorFlow \citep{tensorflow}, PyTorch \citep{pytorch}, and Scikit-Learn \citep{scikit-learn}.
+If we wish for Machine Learning Engineers to perform asset scripting, they will be much more comfortable in Blender’s Python environment compared to the C# of Unity or the C++ of Unreal Engine.
 

### 2021-06-23 zpy_addon/execute_panel.py
Fix code style issues with Black

@@ -39,7 +39,7 @@ class RunOperator(Operator):
         with gin.unlock_config():
             run_text_as_module = run_text.as_module()
         # Parse the gin-config text block
-        zpy.blender.parse_config('config')
+        zpy.blender.parse_config("config")
         # Execute the run function inside the run text
         run_text_as_module.run()
         return {"FINISHED"}

### 2021-06-23 docs/paper/paper.tex
copy edits on 3d

@@
 3D, short for the three dimensions of space we live in, is a catch-all term used to describe the varied technologies used to create virtual worlds.
-The technology stack for 3D can be roughly split into two broad categories: \emph{asset creation} and \emph{asset scripting}.
+3D’s technology stack can be roughly split into two broad categories: \emph{asset creation} and \emph{asset scripting}.
 Asset creation \ref{sec:assetcreation} is the process of creating assets: virtual objects, scenes, and materials.
 Asset scripting \ref{sec:assetscripting} is the process of manipulating those assets and their interactions over the fourth dimension of time.
-Decades of progress have resulted in sophisticated software tools that make 3D workflows easier and more automated, but a significant amount of human expertise and artistic talent is still required.
+Decades of progress have resulted in sophisticated software tools that make 3D workflows more automated and straightforward, but a significant amount of human expertise and artistic talent is still required.
 
@@
 Assets are digital representations of a 3D object.
-One type of asset is a mesh: a connected graph of 3D points, also called vertices, which define the surface of an object.
-Vertices are interconnected by edges, and a closed loop of vertices creates a polygon known as a face.
-In the engineering and manufacturing world, meshes are created using computer aided design (CAD) software such as AutoCAD \citep{autocad}, Solidworks \citep{solidworks}, Onshape \citep{onshape}, and Rhino \citep{rhino}.
-In the entertainment industry, meshes are created using modeling software such as Maya \citep{maya}, 3DSMax \citep{3dsmax}, and Cinema4D \citep{cinema4d}.
+One type of asset is a mesh: a connected graph of 3D points also called vertices, which define the surface of an object.
+Edges interconnect vertices, and a closed loop of vertices creates a polygon known as a face.
+The engineering and manufacturing world creates meshes using computer-aided design (CAD) software such as AutoCAD \citep{autocad}, Solidworks \citep{solidworks}, Onshape \citep{onshape}, and Rhino \citep{rhino}.
+The entertainment industry creates meshes using modeling software such as Maya \citep{maya}, 3DSMax \citep{3dsmax}, and Cinema4D \citep{cinema4d}.
 
@@
 A material may define rules for the reflectivity, specularity, and metallic-ness of the object as a function of lighting conditions.
-Materials are used by shader programs to calculate the exact pixel values to render for each face of a mesh polygon.
-Modeling software will usually come packaged with tools that allow the creation and configuration of materials.
+Shader programs use materials to calculate the exact pixel values to render for each face of a mesh polygon.
+Modeling software usually comes packaged with tools for the creation and configuration of materials.
 
-Finally, asset creation also encompasses the process of scene composition.
+Finally, asset creation encompasses the process of scene composition.
 Assets can be organized into scenes, which may contain other unique virtual objects such as simulated lights and cameras.
 Deciding where to place assets, especially lights, is still almost entirely done by hand.
-Automatic scene composition remains an outstanding challenge in the 3D technology stack.
+Automatic scene composition remains a tremendous challenge in the 3D technology stack.
 
@@
 Asset scripting is the process of defining the behaviors of assets within scenes over time.
-One type of asset scripting is called animation, which consists of creating a set of sequential mesh deformations to create the illusion of natural movement.
-Animation is a tedious manual task since every frame must be defined: expert animators spend decades honing their digital puppeteering skills.
+One type of asset scripting is called animation, which consists of creating sequential mesh deformations that create the illusion of natural movement.
+Animation is a tedious manual task because an artist must define every frame; expert animators spend decades honing their digital puppeteering skills.
 Specialized software is often used to automate this task as much as possible, and technologies such as Motion Capture (MoCap) can be used to record the movement of real objects and play those movements back on virtual assets.
 
-Game Engines are software tools which allow for asset scripting in a more structured and systematic way, mostly by providing software interfaces (e.g.
-code) to control the virtual world.
+Game Engines are software tools that allow for more structured and systematic asset scripting, mostly by providing software interfaces (e.g., code) to control the virtual world.
 Used extensively in the video game industry after which they were named, examples include Unity \citep{unity3d}, Unreal Engine \citep{unrealengine}, GoDot \citep{godot}, and Roblox \citep{roblox}.
-These game engines allow for rule-based spawning, animation, and complex interactions between assets in the virtual world.
+These game engines support rule-based spawning, animation, and complex interactions between assets in the virtual world.
 Programming within game engines is a separate skillset to modeling and animating and is usually done by separate engineers within an organization.
@@
 
-Blender is an open source 3D software tool originally released in 1994 \citep{blender}.
+Blender is an open-source 3D software tool initially released in 1994 \citep{blender}.
 It has grown steadily over the decades and has become one of the most popular 3D tools available, with a massive online community of users.
-Blender strength in its breadth: it provides simple tools for every part of the 3D workflow, rather than specializing in a narrow slice of the 3D workflow.
-Organizations such as game studios have traditionally preferred specialization, having separate teams of engineers using separate tools, such as Maya for modeling and Unreal Engine for scripting.
-However, the convenience of using a single tool, combined with the advantage of a single engineer being able to see a project start to finish, make a strong case for Blender as the ultimate winner in the 3D software tools race.
-By focusing on open source and community, Blender continues to gain adoption as more and more of the world’s new 3D developers choose to learn Blender over other more specialized tools.
+Blender’s strength is in its breadth: it provides simple tools for every part of the 3D workflow, rather than specializing in a narrow slice.
+Organizations such as game studios have traditionally preferred specialization, having separate engineers using separate tools (such as Maya for modeling and Unreal Engine for scripting).
+However, the convenience of using a single tool, and the myriad advantages of a single engineer being able to see a project start to finish, make a strong case for Blender as the ultimate winner in the 3D software tools race.
 
-In addition to encompassing the full breadth of the 3D workflow, Blender has the unique strength of using Python as the programming language of choice for asset scripting.
-Python has emerged as the lingua franca for modern deep learning, rising to the top in part due to the popularity of open source frameworks such as TensorFlow \citep{tensorflow}, PyTorch \citep{pytorch}, and Scikit-Learn \citep{scikit-learn}.
-If we wish for Machine Learning Engineers to perform asset scripting, they will be much more comfortable in Blender’s Python environment compared to the C# of Unity or the C++ of Unreal Engine.
+Many of the world’s new 3D developers opt to get started and build their expertise in Blender for its open-source and community-emphasizing offering.
+This is an example of a common product flywheel: using a growing community of users to improve a product over time.
+With big industry support from Google, Amazon, and even Unreal, Blender also has the funding required to improve its tools with this user feedback.
+
+In addition to supporting the full breadth of the 3D workflow, Blender has the unique strength of using Python as the programming language of choice for asset scripting.
+Python has emerged as the lingua franca for modern deep learning, in part due to the popularity of open-source frameworks such as TensorFlow \citep{tensorflow}, PyTorch \citep{pytorch}, and Scikit-Learn \citep{scikit-learn}.
+Successful adoption of synthetic data will require Machine Learning Engineers to perform asset scripting, and these engineers will be much more comfortable in Blender’s Python environment than Unity’s C# or Unreal Engine’s C++ tools.
 

### 2021-06-24 docs/paper/paper.tex
workflow section

@@
 
-The synthetic data workflow can be broadly divided into three categories: simulation design, generation, and tuning.
-
 BlenderProc, Synthesis, LexSet
@@
 	\includegraphics[width=\textwidth]{workflow.png}
-	\caption{The Synthetic Data Workflow allows for iteration of the dataset.}
+	\caption{The synthetic data workflow allows for iteration of the dataset, unlike the manual data workflow, which depends on data collection.}
 	\label{fig:workflow}
@@
 
-The full workflow for synthetic data can be reduced into four key steps: \emph{Design} \ref{sec:worflowdesign}, \emph{Generation} \ref{sec:generation}, \emph{Evaluation} \ref{sec:evaluation}, \emph{Iteration} \ref{sec:iteration}.
+The full workflow for synthetic data can be reduced into four key steps: \emph{Simulation Creation} \ref{sec:worflowsimcreation}, \emph{Dataset Generation} \ref{sec:generation}, \emph{Model Evaluation} \ref{sec:evaluation}, \emph{Iteration} \ref{sec:iteration}.
 The synthetic data workflow is similar to the workflow when using collected data, with the key exception that it allows for iteration on the dataset itself \ref{fig:workflow}.
 
-\subsection{Design}
-\label{sec:worflowdesign}
+\subsection{Simulation Creation}
+\label{sec:worflowsimcreation}
 
-The first step in the syntehtic data workflow is to design and create the sim, short for simulation.
-A sim is a collection of assets controlled through a single script.
-The run() function in the script acts as the point of entry for any generation process.
-Relevant parameters are put as kwargs in the run() function, which allows configuration through gin-config, a python package for configuration of python libraries.
+The first step in the syntehtic data workflow is to design and create the \emph{sim}, short for simulation.
+A sim is a collection of 3D assets controlled at runtime through a single script called the \emph{run script}.
+The run script defines a function \lstinline{run(*)}, which acts as the point of entry for any generation process.
+Important parameters that configure the behavior of the run script are defined as kwargs, short for keyword arguments, in the \lstinline{run(*)} function.
+These kwargs allow configuration of the simulation through gin-config, a python package for configuration of python libraries \citep{ginconfig}.
 
-\subsection{Generation}
+The run script can be broken into two sections: the \emph{setup} and the \emph{loop}.
+The setup is executed first and typically only once.
+Setup can include code for creating categories, loading assets, and storing the pose of virtual objects in the scene.
+The loop, named after the \lstinline{for} loop python pattern, is repeated for some number of frames.
+Each frame can include code for jittering, saving annotations, and rendering images.
+
+\begin{lstlisting}[language=Python,caption={Basic structure of a run script.},label={lst:setuploop}]
+def run\left(  
+	kwarg_1 : bool = False,
+\right)):
+	# Setup Code
+	for frame in zpy.blender.step():
+		# Loop Code
+\end{lstlisting}
+
+\subsection{Dataset Generation}
 \label{sec:generation}
 
-Datasets are rendered frame by frame. Separate rendering passes are required for segmentation and color images.
+Once a sim has been created it can be used to generate data.
+There is no constraint on the type of data a sim can generate, though images are the most common.
+Each frame of the loop in a run script will render out color and segmentation images.
+Datasets can be generated locally directly inside the Blender GUI through the zpy Blender AddOn \ref{sec:blenderaddon}.
+This makes sim development possible by making the local debuggin loop faster.
+Once a sim is properly generating data locally, it can be exported and uploaded to the cloud backend.
+Exporting is done through the Blender AddOn, and will create a zip file which contains all the asset dependencies required for sim execution.
+The exported sim can be uploaded to the cloud backend through any of the user interfaces described in \ref{sec:userinterfaces}.
 
-Datasets can be rendered locally directly inside the Blender GUI.
-This allows for easy debugging when developing a sim.
-Once it is working locally, a sim can be exported into a zip file which will contain all the asset dependencies required.
-This zip file can be uploaded to the cloud with any of the user interfaces described in \ref{sec:userinterfaces}.
+Datasets can be generated in parallel, with multiple cloud machines running concurrent instances of the same sim.
+Each machine is given a different random seed, resulting in a unique dataset.
+The resulting collection of smaller datasets can be packaged into into a single larger dataset, making it easier for a machine learning practitioner to download and work with the dataset.
+Additional workflows are provided for sorting individual datapoints into test, train, and validation buckets.
 
-Dataset are then generated in the cloud \ref{sec:cloudbackend}.
-
-We provide workflows for packaging several smaller datasets into a single larger dataset, as well as sorting individual datapoints into test, train, and validation buckets.
-
-\subsection{Evaluation}
+\subsection{Model Evaluation}
 \label{sec:evaluation}
 
-Sweeping over dataset hyperparameters (much like sweeping over model architecture parameters)
-
-Fine-tuning pre-trained models as a proxy for dataset performance
+Machine learning models are trained on a dataset for some time, and periodically evaluated on validation and test datasets.
+Model performance in computer vision can be measured in a variety of ways, such as precision and recall, or more aggregate metrics like mean average precision (mAP).
+Picking the right metric is problem specific and usually comes down to which type of failure is the most important: false positives or false negatives.
 
@@
 
-Least understood part of developing with synthetic data
+Those familiar with machine learning model development are aware of \emph{hyperparameters}: parameters whose value are used to control the learning process.
+Common examples of these include batch size, learning rate, and training epochs.
+These parameters, unlike the weights inside the model with are learned through training, must be set by the experiment designer.
+In practice, a human will use their intuition to decide upon a set or range of possible values for these hyperparameters, and then sweep over the possible hyperparameter space to find the best values for a given problem.
+This process, known as tuning, can have a high cost in engineering time and compute footprint.
+A technique known as AutoML has improved tuning by significantly reducing the engineering time cost.
+In AutoML, an automated process will tune these hyperparameters over time by trying different permutations, usually guided through a single heuristic score.
 
-The promise of AutoML for datasets
+The kwargs of the run function in a sim are effectively additional hyperparameters that can also be tuned.
+The human designer of the sim can define plausible values and ranges for these sim hyperparameters, and then use an AutoML-like system to discover the values that result in the best model.
+This presents a unique opportunity in the machine learning workflow, where the dataset used to train a model is no longer static, and can be tuned and improved over time.
 

### 2021-06-24 docs/paper/paper.tex
reference cleanup, more progress

@@
 \author{
-	{\hspace{1mm}Hugo Ponte}\thanks{correspondence author} \\ 
+	{\hspace{1mm}Hugo Ponte}\footnote{Correspondence author} \\ 
 	Zumo Labs \\
@@
 Deep learning has exploded in popularity due to large open source frameworks such as tensorflow and pytorch
-What is synthetic data (references)
+
+What is synthetic data.
 
@@
 Black box nature of ML
+
+For a thorough review of synthetic data literature, we recommend readers go through Nikolenko's 2019 summary paper \citep{nikolenko2019synthetic}.
 
@@
 Python has emerged as the lingua franca for modern deep learning, in part due to the popularity of open-source frameworks such as TensorFlow \citep{tensorflow}, PyTorch \citep{pytorch}, and Scikit-Learn \citep{scikit-learn}.
-Successful adoption of synthetic data will require Machine Learning Engineers to perform asset scripting, and these engineers will be much more comfortable in Blender’s Python environment than Unity’s C# or Unreal Engine’s C++ tools.
-
-\subsection{Synthetic Data}
-\label{sec:syntheticdata}
-
-BlenderProc, Synthesis, LexSet
+Successful adoption of synthetic data will require Machine Learning Engineers to perform asset scripting, and these engineers will be much more comfortable in Blender’s Python environment than Unity's C\# environment or Unreal Engine’s C++ tools.
 
@@
 
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{webapp.png}
+	\caption{A visual interface for synthetic data creation via a WebApp.}
+	\label{fig:webapp}
+\end{figure}
+
 \section{Project Features}
@@
 
-Given
+In this section we outline the key features and components of the zpy synthetic data toolkit.
 
@@
 
-As explained in section X, deep learning is a python-first discipline.
-If we wish to include deep learning practitioners in the 3D stack it is thus of critical importance that we provide a python interface for the 3D workflow.
+Blender allows for user-created AddOns, and provides tooling for integrating addon functionality with the Blender UI.
+
+Popular AddOns include X, X, and X.
+
+Those who use Blender in their 3D workflow are
 
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{webapp.png}
-	\caption{A visual interface for synthetic data creation via a WebApp.}
-	\label{fig:webapp}
-\end{figure}
-
-\section{Design}
-\label{sec:design}
+\subsection{Python Module}
+\label{sec:python module}
 
@@
 
-Pythonic syntax
+As explained in section X, deep learning is a python-first discipline.
+If we wish to include deep learning practitioners in the 3D stack it is thus of critical importance that we provide a python interface for the 3D workflow.
 
@@
 The `zpy.opject.segment()` function call can accept an object directly of type `bpy.types.Object`, but it will also accept the unique string name of that object.
-
-Extensibility
 
@@
 A sim is a collection of 3D assets controlled at runtime through a single script called the \emph{run script}.
-The run script defines a function \lstinline{run(*)}, which acts as the point of entry for any generation process.
-Important parameters that configure the behavior of the run script are defined as kwargs, short for keyword arguments, in the \lstinline{run(*)} function.
+The run script defines a function \lstinline{run(**kwargs)}, which acts as the point of entry for any generation process.
+Important parameters that configure the behavior of the run script are defined as kwargs, short for keyword arguments, in the \lstinline{run(**kwargs)} function.
 These kwargs allow configuration of the simulation through gin-config, a python package for configuration of python libraries \citep{ginconfig}.
@@
 
-\begin{lstlisting}[language=Python,caption={Basic structure of a run script.},label={lst:setuploop}]
-def run\left(  
-	kwarg_1 : bool = False,
-\right)):
+\begin{lstlisting}[language=Python,caption={Basic structure of the run function in a sim run script.},label={lst:setuploop}]
+def run(**kwargs):
 	# Setup Code
@@
 Picking the right metric is problem specific and usually comes down to which type of failure is the most important: false positives or false negatives.
+It is important to note that though quantitative metrics are convenient, there is no replacement for qualitative analysis of model performance.
+We recommend that anyone building computer vision models take the time to examine model predictions on real images.
 
@@
 
-Package detection
+To put into practice what this paper has explained, we present an example of how synthetic data can be used to train a computer vision model.
+In this example, we train a detection model which is tasked with predicting the bounding boxes for packages and parcels in images.
+In section \ref{sec:domainrandomization} we explore the effect of some key dataset hyperparameters on the final model performance.
+In section \ref{sec:curicculum} we discuss how training curriculum can affect model performance when using synthetic data.
 
-\begin{itemize}
-	\item Background material and texture.
-	\item Lighting intensity and positioning.
-	\item Object material and texture.
-	\item Number of objects in view.
-\end{itemize}
+Following the synthetic data workflow,
+
+Armed with our synthetic training dataset and our real test dataset, we are ready to do some model training.
+
+We used a ResNet model implemented in PyTorch inside of the Detectron2 computer vision library \citep{wu2019detectron2}.
 
@@
 
-Effect of domain randomized lighting
+Domain randomization is a technique commonly used in synthetic data to increase the variance of a dataset distribution.
+In the field of synthetic data for computer vision, it might refer to randomizing the intensity of lighting in every frame of a simulation.
+Domain randomization is also important in the space of material assets: using a large variety of textures and material properties will help prevent texture overfitting, a common issue with CNNs \citep{DBLP:journals/corr/abs-1811-12231}.
 
-Effect of domain randomized backgrounds
+In our package experiment, we expose two boolean toggles as run function kwargs that are categorized as forms of domain randomization.
+One toggle enables domain randomization in the lighting space: changing the position and intensity of several lights in the sim.
+The second toggle enables random HDRIs, which change the appearance of the background in the package images.
 

### 2021-06-24 docs/paper/paper.tex
more content

@@
 Blender allows for user-created AddOns, and provides tooling for integrating addon functionality with the Blender UI.
-
-Popular AddOns include X, X, and X.
-
-Those who use Blender in their 3D workflow are
+Examples of popular AddOns are NodeWrangler and Botaniq.
+NodeWrangler adds simple productivity functionality to the Node System, a method of visual scripting common to 3D tools.
+Botaniq is a library of tree and plant assets, with a built in scattering method hugely popular due to the complexity of creating grass and trees from scratch.
+Blender users are comfortable installing and using addons as part of their workflow.
+The zpy-addon allows for mouse and button based versions of the segmentation, sim run script execution, and sim exporting workflows.
+Though these actions are possible entirely through python code, providing convenient button versions in a UI makes these processes available to a larger community of 3D artists who are not as comfortable in a code-only environment.
 
@@
 
-Abstracting away the difficulties of the cloud workflow and providing an intuitive and convenient interface for parallelizing computation is thus important for the democratization of deep learning and synthetic data workflows.
-Much like platforms have emerged for the training and tuning workflows of deep learning, an opportunity exists to create platforms for the generation and tuning workflows of synthetic data.
+Abstracting away the difficulties of the cloud workflow and providing an intuitive and convenient interface for parallelizing computation is thus important for the synthetic data workflow.
+Dataset generation jobs can be made with the zpy CLI and API such that many computers are used, thus speeding up the generation job.
 
@@
 Power users want an API (application programming interface) and CLI (command line interface).
-Building a ramp for the bulk of the developer community requires a GUI
+Building a ramp for the bulk of the developer community requires a GUI.
 

### 2021-06-29 docs/paper/paper.tex
bib debugging, democratization and bias

@@
 \graphicspath{ {./images/} }
-\usepackage[square,numbers]{natbib}
 \usepackage{doi}
+
+\usepackage[backend=biber, style=numeric]{biblatex}
+\addbibresource{references.bib}
+% \RequirePackage[backend=biber,
+% style=apa,
+% citestyle=authoryear
+% ]{biblatex}
+% \usepackage[square,numbers]{natbib}
 
@@
 
-For a thorough review of synthetic data literature, we recommend readers go through Nikolenko's 2019 summary paper \citep{nikolenko2019synthetic}.
+For a thorough review of synthetic data literature, we recommend readers go through Nikolenkos 2019 summary paper \cite{nikolenko2019synthetic}.
 
@@
 Edges interconnect vertices, and a closed loop of vertices creates a polygon known as a face.
-The engineering and manufacturing world creates meshes using computer-aided design (CAD) software such as AutoCAD \citep{autocad}, Solidworks \citep{solidworks}, Onshape \citep{onshape}, and Rhino \citep{rhino}.
-The entertainment industry creates meshes using modeling software such as Maya \citep{maya}, 3DSMax \citep{3dsmax}, and Cinema4D \citep{cinema4d}.
+The engineering and manufacturing world creates meshes using computer-aided design (CAD) software such as AutoCAD \cite{autocad}, Solidworks \cite{solidworks}, Onshape \cite{onshape}, and Rhino \cite{rhino}.
+The entertainment industry creates meshes using modeling software such as Maya \cite{maya}, 3DSMax \cite{3dsmax}, and Cinema4D \cite{cinema4d}.
 
@@
 Game Engines are software tools that allow for more structured and systematic asset scripting, mostly by providing software interfaces (e.g., code) to control the virtual world.
-Used extensively in the video game industry after which they were named, examples include Unity \citep{unity3d}, Unreal Engine \citep{unrealengine}, GoDot \citep{godot}, and Roblox \citep{roblox}.
+Used extensively in the video game industry after which they were named, examples include Unity \cite{unity3d}, Unreal Engine \cite{unrealengine}, GoDot \cite{godot}, and Roblox \cite{roblox}.
 These game engines support rule-based spawning, animation, and complex interactions between assets in the virtual world.
@@
 
-Blender is an open-source 3D software tool initially released in 1994 \citep{blender}.
+Blender is an open-source 3D software tool initially released in 1994 \cite{blender}.
 It has grown steadily over the decades and has become one of the most popular 3D tools available, with a massive online community of users.
@@
 In addition to supporting the full breadth of the 3D workflow, Blender has the unique strength of using Python as the programming language of choice for asset scripting.
-Python has emerged as the lingua franca for modern deep learning, in part due to the popularity of open-source frameworks such as TensorFlow \citep{tensorflow}, PyTorch \citep{pytorch}, and Scikit-Learn \citep{scikit-learn}.
+Python has emerged as the lingua franca for modern deep learning, in part due to the popularity of open-source frameworks such as TensorFlow \cite{tensorflow}, PyTorch \cite{pytorch}, and Scikit-Learn \cite{scikit-learn}.
 Successful adoption of synthetic data will require Machine Learning Engineers to perform asset scripting, and these engineers will be much more comfortable in Blender’s Python environment than Unity's C\# environment or Unreal Engine’s C++ tools.
@@
 
-The datasets used by companies today are almost exclusively collected.
-Images and annotations are gradually saved as they are generated by users of a product.
-Collecting a dataset large enough to train a robust machine learning model can take years.
-
+Modern computer vision systems use learning based methods and thus require large and diverse datasets.
+These datasets are almost exclusively collected: images are stored in databases as they are cumulatively generated by users of a product over time.
+Annotations are created by hand, usually by a third party provider using low-skilled labor in third world countries.
+Collecting and labeling a dataset large enough to train a robust computer vision model can take years.
 Only companies that have the scale and have set up the infrastructure to collect and store large datasets will have the datasets required to train models.
@@
 Though some regulations have emerged, famously GDPR in Europe, these have yet to change the landscape of the market for collected data.
-
-The high cost of data labeling makes it unavailable to those without huge resources
+Synthetic data can democratize access to large-scale datasets by reducing the time required to collect these datasets and eliminating the cost of labeling these datasets.
 
@@
 
-The real world is biased and unfair.
+The large cost to collect and annotate datasets makes it prohibitive for most small organizations to create their own datasets, and as such it is common practice to use one of a small selection of openly available datasets (such as ImageNet).
+However, because of how these datasets have been collected over time, and due to the unequal global distribution of technologies such as cell phone cameras, these datasets are often biased.
+The real world is biased and unfair, and these collected datasets do not represent the large variety of cultural, demographic, or gender diversity  in human datasets \cite{shankar2017classification}.
+These datasets do not capture all geographic differences in object recognition datasets \cite{DBLP:journals/corr/abs-1906-02659}.
+The nature of statistical learning methods means that training on these biased datasets will result in a biased model: a model is only as good as the data on which it is trained.
+As such, it follows that the best way to reduce bias in modern computer vision systems is to improve the datasets these systems are trained on.
 
-ML systems trained on this data will reflect the same bias during inference.
+Synthetic datasets offer full control of the distribution and can thus be designed to be more representative.
+A synthetic human dataset can equally represent cultural, demographic, or gender diversity.
+Synthetic datasets as a method of reducing bias has been explored in a variety of computer vision domains \cite{DBLP:journals/corr/abs-2004-13866}.
 
@@
 Important parameters that configure the behavior of the run script are defined as kwargs, short for keyword arguments, in the \lstinline{run(**kwargs)} function.
-These kwargs allow configuration of the simulation through gin-config, a python package for configuration of python libraries \citep{ginconfig}.
+These kwargs allow configuration of the simulation through gin-config, a python package for configuration of python libraries \cite{ginconfig}.
 
@@
 
-We used a ResNet model implemented in PyTorch inside of the Detectron2 computer vision library \citep{wu2019detectron2}.
+We used a ResNet model implemented in PyTorch inside of the Detectron2 computer vision library \cite{wu2019detectron2}.
 
@@
 In the field of synthetic data for computer vision, it might refer to randomizing the intensity of lighting in every frame of a simulation.
-Domain randomization is also important in the space of material assets: using a large variety of textures and material properties will help prevent texture overfitting, a common issue with CNNs \citep{DBLP:journals/corr/abs-1811-12231}.
+Domain randomization is also important in the space of material assets: using a large variety of textures and material properties will help prevent texture overfitting, a common issue with CNNs \cite{DBLP:journals/corr/abs-1811-12231}.
 
@@
 
-\bibliographystyle{abbrvnat}
-\bibliography{references}
+% \bibliographystyle{abbrvnat}
+% \bibliography{references}
+\printbibliography
 

### 2021-06-29 cli/cli.py
add state to dataset filter

@@ -187,6 +187,7 @@ def list_datasets(filters, project=None):
         columns="name,files,created_at",
         colwidth={
             "name": LARGE_WIDTH,
+            "state": MEDIUM_WIDTH,
             "files": SMALL_WIDTH,
             "created_at": DATETIME_WIDTH,
         },
@@ -194,6 +195,7 @@ def list_datasets(filters, project=None):
     for d in datasets:
         tbl(
             d["name"],
+            d["state"],
             len(d["files"]),
             d["created_at"],
         )

### 2021-06-30 examples/crowd/run.py
keypoint example

@@ -1,0 +1,173 @@
+""" Crowd Sim.
+
+Humans moving around in an HDRI.
+
+"""
+import logging
+import random
+
+import bpy
+import gin
+import mathutils
+import zpy
+
+log = logging.getLogger('zpy')
+
+
+@gin.configurable('run')
+@zpy.blender.save_and_revert
+def run():
+    """ Main run function.
+
+    Any kwargs you put here will show up
+    on the Data Portal. Give them types!
+    """
+
+    # Random seed results in unique behavior
+    zpy.blender.set_seed()
+
+    # Create the saver object
+    saver = zpy.saver_image.ImageSaver(
+        description='Crowd of humans.',
+    )
+
+    camera = bpy.data.objects["Camera"]
+
+    # Make a list of humans and their keypoints
+    human_collections = [
+        bpy.data.collections['MOVING'],
+        bpy.data.collections['IDLE'],
+    ]
+    humans = []
+    keypoints = []
+    for _human_collection in human_collections:
+        for human in _human_collection.all_objects:
+            humans.append(human)
+            _keypoints = zpy.keypoints.Keypoints(
+                root=bpy.data.objects[f'{human.name}_skeletonRoot'],
+                style='coco',
+                armature='anima',
+            )
+            keypoints.append(_keypoints)
+
+    # Get all the subcategories for the humans
+    _subcategories = []
+    for human in humans:
+        _subcategories.append(human.seg.instance_name)
+
+    # Add the categories from the sim-level object
+    _categories = bpy.context.scene.categories
+    saver.add_category(
+        name=_categories['person'].name,
+        subcategories=_subcategories,
+        color=tuple(_categories['person'].color),
+        keypoints=keypoints[0].names,
+        skeleton=keypoints[0].connectivity,
+    )
+
+    # Randomize the hdri
+    zpy.hdris.random_hdri()
+
+    # Run the sim.
+    for step_idx in zpy.blender.step(
+        start_frame=random.randint(0, 250),
+    ):
+
+        # Randomize the camera position
+        zpy.objects.random_position_within_constraints(camera)
+
+        # Name for each of the output images
+        rgb_image_name = zpy.files.make_rgb_image_name(step_idx)
+        iseg_image_name = zpy.files.make_iseg_image_name(step_idx)
+        cseg_image_name = zpy.files.make_cseg_image_name(step_idx)
+        depth_image_name = zpy.files.make_depth_image_name(step_idx)
+
[…]

### 2021-07-06 examples/crowd/run.py
Fix code style issues with Black

@@ -11,13 +11,13 @@ import gin
 import mathutils
 import zpy
 
-log = logging.getLogger('zpy')
+log = logging.getLogger("zpy")
 
 
-@gin.configurable('run')
+@gin.configurable("run")
 @zpy.blender.save_and_revert
 def run():
-    """ Main run function.
+    """Main run function.
 
     Any kwargs you put here will show up
     on the Data Portal. Give them types!
@@ -28,15 +28,15 @@ def run():
 
     # Create the saver object
     saver = zpy.saver_image.ImageSaver(
-        description='Crowd of humans.',
+        description="Crowd of humans.",
     )
 
     camera = bpy.data.objects["Camera"]
 
     # Make a list of humans and their keypoints
     human_collections = [
-        bpy.data.collections['MOVING'],
-        bpy.data.collections['IDLE'],
+        bpy.data.collections["MOVING"],
+        bpy.data.collections["IDLE"],
     ]
     humans = []
     keypoints = []
@@ -44,9 +44,9 @@ def run():
         for human in _human_collection.all_objects:
             humans.append(human)
             _keypoints = zpy.keypoints.Keypoints(
-                root=bpy.data.objects[f'{human.name}_skeletonRoot'],
-                style='coco',
-                armature='anima',
+                root=bpy.data.objects[f"{human.name}_skeletonRoot"],
+                style="coco",
+                armature="anima",
             )
             keypoints.append(_keypoints)
 
@@ -58,9 +58,9 @@ def run():
     # Add the categories from the sim-level object
     _categories = bpy.context.scene.categories
     saver.add_category(
-        name=_categories['person'].name,
+        name=_categories["person"].name,
         subcategories=_subcategories,
-        color=tuple(_categories['person'].color),
+        color=tuple(_categories["person"].color),
         keypoints=keypoints[0].names,
         skeleton=keypoints[0].connectivity,
     )
@@ -93,25 +93,25 @@ def run():
         # Add images to saver
         saver.add_image(
             name=rgb_image_name,
-            style='default',
+            style="default",
             output_path=saver.output_dir / rgb_image_name,
             frame=step_idx,
         )
         saver.add_image(
             name=iseg_image_name,
-            style='segmentation',
+            style="segmentation",
             output_path=saver.output_dir / iseg_image_name,
             frame=step_idx,
         )
         saver.add_image(
             name=cseg_image_name,
-            style='segmentation',
+            style="segmentation",
[…]

### 2021-07-06 zpy/material.py

@@ -215,7 +215,7 @@ def random_texture_mat() -> bpy.types.Material:
 
 
 @gin.configurable
-def filtered_dir_texture_mat(dir_name : Union[Path, str] = None) -> bpy.types.Material:
+def filtered_dir_texture_mat(dir_name: Union[Path, str] = None) -> bpy.types.Material:
     """Generate a material based on a word, which searches for related texture images.
 
     TODO: Requires Zumo Labs Asset Library
@@ -227,7 +227,7 @@ def filtered_dir_texture_mat(dir_name : Union[Path, str] = None) -> bpy.types.Ma
         bpy.types.Material: The newly created material.
     """
     if dir_name is None:
-        log.warning('No filter provided, using random texture mat instead.')
+        log.warning("No filter provided, using random texture mat instead.")
         return random_texture_mat()
     texture_dir = zpy.assets.texture_dir() / dir_name
     texture_path = zpy.files.pick_random_from_dir(

### 2021-07-07 docs/paper/paper.tex
project features

@@
 
-In this section we outline the key features and components of the zpy synthetic data toolkit.
+In this section we outline the key features and components of the zpy synthetic data toolkit: a Blender addon \ref{sec:blenderaddon}, a cloud backend \ref{sec:cloudbackend}, a python module \ref{sec:pythonmodule}, and various types of user interfaces \ref{sec:userinterfaces}.
 
@@
 Abstracting away the difficulties of the cloud workflow and providing an intuitive and convenient interface for parallelizing computation is thus important for the synthetic data workflow.
-Dataset generation jobs can be made with the zpy CLI and API such that many computers are used, thus speeding up the generation job.
+Dataset generation jobs can be made with the zpy Python API \ref{lst:api} and CLI \ref{lst:cli} such that many computers are used, thus speeding up the generation job.
+The ZumoLabs cloud uses orchestration technology, e.g.
+Kubernetes, to spin up and manage new image generation nodes.
+
+\subsection{Python Module}
+\label{sec:pythonmodule}
+
+Python is the most popular programming language for creating and training deep learning systems, which are the primary consumers of synthetic image datasets.
+The zpy synthetic data toolkit is thus written in python, and is available and installable through the Python Package Index PyPI \ref{lst:pipinstall}.
+
+\begin{lstlisting}[language=bash,caption={Installing the zpy python module.},label={lst:pipinstall}]
+pip install zpy-zumo
+\end{lstlisting}
+
+When designing software systems, there is usually a tradeoff between \emph{flexibility} and \emph{simplicity}.
+Simplicity is the ability to perform a task with minimal amount of work and a limited understanding of the software package.
+Flexibility is the ability to support many different tasks and allow for customization.
+To balance these two competing objectives, we opted for the principle of \emph{hidden complexity} when designing the zpy python package.
+One such example is the function calls for random HDRIs and textures: these will default to pre-selected random textures unless a specific path is given.
+Another manifestation of this design principle is in the flexibility of function arguments: the `zpy.opject.segment()` function call can accept an object directly of type `bpy.types.Object`, but it will also accept the unique string name of that object.
+These design principles reinforce one of the core principles of Python: \emph{readability}.
+Python insists on human readable syntax, and does not enforce function and variable type annotations, which makes it quicker to prototype code.
+
+The zpy python package is organized as a collection of seperate modules.
+These modules are separated based on their dependencies and functionality.
+This makes it easier for end users to add custom functionality, or ignore modules with dependencies they do not want.
+This type of modular design can be seen in other popular python libraries, such as Matplotlib \cite{Hunter:2007}.
 
@@
 We provide three different interfaces to interact with our product: a Python API \ref{lst:api}, a CLI \ref{lst:cli}, and a graphical WebApp \ref{fig:webapp}.
-Power users want an API (application programming interface) and CLI (command line interface).
-Building a ramp for the bulk of the developer community requires a GUI.
+The Python API (application programming interface) allows users to generate custom datasets directly inside a python script, which means that model training code and data generation code can be tied together.
+This is especially important for using automatic hyperparameter tuning frameworks.
+The CLI (command line interface) allows for users to generate and manipulate their datasets with unix terminal commands.
+The terminal is extremely popular as an interface for computation tasks and thus a CLI is a must-have for a large swath of the developer community.
+Finally, we also provide a graphical interface in the form of a WebApp.
+Graphical interfaces can provide powerful visualization tools, and are generally more approachable for those less comfortable with code-like interfaces such as an API or CLI.
 
@@
 \begin{lstlisting}[language=bash,caption={Generating a dataset using the zpy CLI},label={lst:cli}]
-# First you will need to log in and set the project (image generation gets billed according to project)
-zpy login $USERNAME 
-zpy project set $PROJECT_UUID
-
-# Generate the dataset
-zpy create dataset "redbull cans and packs" can_v6 num_images 1000
+zpy create dataset "hello world dataset" my_sim num_images 1000
 \end{lstlisting}
-
-\subsection{Python Module}
-\label{sec:python module}
-
-Hidden complexity
-
-When designing software systems, there is usually a tradeoff between flexibility and simplicity.
-Simplicity is the ability to perform a task with minimal amount of work and a limited understanding of the software package.
-Flexibility is the ability to support many different tasks and allow for customization.
-
-Random hdri and textures use default random textures unless a specific path is given
-
-As explained in section X, deep learning is a python-first discipline.
-If we wish to include deep learning practitioners in the 3D stack it is thus of critical importance that we provide a python interface for the 3D workflow.
-
-One of the core features of Python is the language’s human readable syntax. Python does not enforce function and variable type annotations, which makes it quicker to prototype code.
-
-Functions in zpy are flexible in the arguments that they accept.
-The `zpy.opject.segment()` function call can accept an object directly of type `bpy.types.Object`, but it will also accept the unique string name of that object.
-
-Zpy modules are separated by dependencies
-
-Zpy modules are independent of each other, a monolithic system is much harder to update and maintain
 

### 2021-07-07 cli/utils.py
refactor to new design

@@ -2,6 +2,8 @@ import functools
 import math
 from copy import deepcopy
 from itertools import product
+from pathlib import Path
+from typing import Union
 from urllib.request import urlopen
 
 import click
@@ -86,14 +88,14 @@ def parse_args(args):
     return dict(zip(keys, vals))
 
 
-def download_url(url, output_path):
+def download_url(url: str, output_path: Union[Path, str]):
     """download url
 
     Download from url to give output path and visualize using tqdm.
 
     Args:
         url (str): url to download
-        output_path (str): path to download file to
+        output_path (Union[Path, str]): path to download file to
     """
     u = urlopen(url)
     h = u.info()

### 2021-07-07 client/test.py

@@ -1,23 +1,27 @@
+import json
+
 import client.zpy as zpy
 
 
 def test_params(*args, **kwargs):
     """Prints out the available sim params."""
     zpy.init(**kwargs)
-    dataset = zpy.Dataset(**kwargs)
-    dataset.show_params()
-
+    # dataset = zpy.Dataset(**kwargs)
+    # dataset.show_params()
+    sim = zpy.Sim('can_v5')
+    sim.show_params()
+    sim.preview()
 
 def test_preview(*args, **kwargs):
     zpy.init(**kwargs)
     dataset = zpy.Dataset(**kwargs)
 
     # Won't exist on anything besides my custom local tests
-    dataset.cool_nested_prop = "c"
-    dataset.preview()
+    # dataset.cool_nested_prop = "c"
+    # dataset.preview()
 
     # Unset it
-    dataset.cool_nested_prop = None
+    # dataset.cool_nested_prop = None
 
     if "sim_specific_properties" in kwargs:
         # Testing sim specific properties
@@ -29,14 +33,34 @@ def test_preview(*args, **kwargs):
 
 def test_generate(*args, **kwargs):
     zpy.init(**kwargs)
-    dataset = zpy.Dataset(**kwargs)
+    can_v5_sim = zpy.Sim('can_v5')
+    can_v5_sim.show_params()
+    can_v5_sim.preview({})
 
-    if "sim_specific_properties" in kwargs:
-        # Testing sim specific properties
-        for k, v in kwargs["sim_specific_properties"].items():
-            dataset.add_sim_specific_param(k, v)
+    dataset_config = zpy.DatasetConfig('can_v5')
+    print(json.dumps(dataset_config.available_params, indent=4, sort_keys=True))
+    # Won't support "generic" properties yet
+    # config.paramA = 1
+    # config.paramB = 'blah'
+    dataset_config.set('custom_param', 'custom_val')
+    dataset_config.set('nested__custom__param', 'nested_val')
+    dataset_config.remove('nested__custom__param')
 
-    dataset.generate(*args)
+    # Still requires pre-generating datasets, throw warnings if none found
+    zpy.preview(dataset_config, num_samples=5)
+    dataset = zpy.generate('can_v5 test', dataset_config, num_datapoints=10, materialize=True)
+    # Return urls or do ipython
+    # /api/v1/files?dataset=dataset_id&name_icontains="00000001"
+    dataset.sample()
+
[…]

### 2021-07-07 client/util.py

@@ -1,0 +1,121 @@
+import functools
+import math
+import sys
+
+import requests
+from requests import HTTPError
+
+
+def add_newline(func):
+    """Decorator to print a new line after the function call.
+
+    Args:
+        func: function to wrap
+
+    Returns:
+        wrapped function
+    """
+
+    @functools.wraps(func)
+    def wrapper(*args, **kwargs):
+        ret = func(*args, **kwargs)
+        print("\n")
+        return ret
+
+    return wrapper
+
+
+def auth_header(auth_token):
+    return {"Authorization": f"Token {auth_token}"}
+
+
+def handle_response(response: requests.Response):
+    """Shared logic for handling API responses.
+
+    Args:
+        response: Request to handle
+    Returns:
+        deserialized json response
+    """
+    if response.status_code != 200:
+        if response.status_code == 400:
+            # Known error from the server will have a nice message.
+            raise HTTPError(response.json())
+        else:
+            response.raise_for_status()
+
+    return response.json()
+
+
+def get(url, **kwargs):
+    """GET a url. Forwards kwargs to requests.get
+    TODO: Merge with calling code in zpy/cli/
+
+    Args:
+        url (str): Ragnarok API url
+        kwargs: Forwarded to the requests.get function call
+    Returns:
+        deserialized API response
+    Raises:
+        HTTPError
+    """
+    return handle_response(requests.get(url, **kwargs))
+
+
+def post(url, **kwargs):
+    """POST to a url. Forwards kwargs to requests.post
+    TODO: Merge with calling code in zpy/cli/
+
+    Args:
+        url (str): Ragnarok API url
+        kwargs: Forwarded to the requests.post function call
+    Returns:
+        deserialized API response
+    Raises:
+        HTTPError
+    """
+    return handle_response(requests.post(url, **kwargs))
+
+
+def to_query_param_value(config):
+    """Create the special query parameter value string for filtering generated-data-sets via config values.
+
+    Args:
+        config (dict): A dict of gin config values pre-flattened by using django field traversal notation. See Dataset._config
+    Returns:
+        string value for the config url query parameter
+    """
+    query_param_values = []
+    for django_field_traversal, django_field_value in config.items():
+        # Ignore fields set as None. They weren't specifically set or asked for.
+        if django_field_value is not None:
[…]

### 2021-07-07 client/zpy.py

@@ -1,148 +1,88 @@
 import functools
 import json
+import sys
+import time
+from datetime import datetime, timedelta
+from pathlib import Path
 from random import randrange
+from typing import Dict, Union
 
 import requests
 
+from cli.utils import download_url
+from client.util import add_newline, get, post, to_query_param_value, convert_size, auth_header, \
+    clear_last_print, is_done
+
 _auth_token: str = ""
 _base_url: str = ""
+_project: Union[Dict, None] = None
 
 
-def init(auth_token: str, base_url: str = "http://localhost:8000", **kwargs):
-    global _auth_token, _base_url
+def init(auth_token: str, project_uuid: str, base_url: str = "http://localhost:8000", **kwargs):
+    global _auth_token, _base_url, _project
     _auth_token = auth_token
     _base_url = base_url
 
+    try:
+        _project = get(f"{_base_url}/api/v1/projects/{project_uuid}", headers=auth_header(_auth_token))
+    except requests.HTTPError:
+        print("Failed to find project, please double check the id and try again.", file=sys.stderr)
 
-def add_newline(func):
-    """Decorator to print a new line after the function call.
 
-    Args:
-        func: function to wrap
+IMAGES_PER_SAMPLE = 2  # for the iseg and rbg
 
-    Returns:
-        wrapped function
-    """
 
+def require_zpy_init(func):
     @functools.wraps(func)
     def wrapper(*args, **kwargs):
-        ret = func(*args, **kwargs)
-        print("\n")
-        return ret
+        if None in [_project, _auth_token, _base_url]:
+            raise RuntimeError("zpy.init() must be called")
+        return func(*args, **kwargs)
 
     return wrapper
 
 
-def get(url, **kwargs):
-    """Call any rag API url while adding the auth header automatically. Takes any arbitrary requests.get kwargs.
-    TODO: Merge with calling code in zpy/cli/
+class DatasetConfig:
+    @require_zpy_init
+    def __init__(self, sim_name: str, **kwargs):
+        """
+        Create a DatasetConfig. Used by zpy.preview and zpy.generate.
 
-    Args:
-        url (str): Ragnarok API url
-        kwargs: Forwarded to the requests.get function call
-    Returns:
-        deserialized API response
-    """
-    headers = {
-        **(kwargs["headers"] if "headers" in kwargs else {}),
-        "Authorization": f"Token {_auth_token}",
-    }
-    r = requests.get(url, headers=headers, **kwargs)
[…]

### 2021-07-07 zpy_addon/execute_panel.py

@@ -6,6 +6,8 @@ import logging
 from pathlib import Path
 
 import bpy
+
+import client.util
 import zpy
 import gin
 from bpy.types import Operator
@@ -26,7 +28,7 @@ class RunOperator(Operator):
     bl_options = {"REGISTER"}
 
     def execute(self, context):
-        text = bpy.data.texts.get("run", None)
+        text = client.util.get("run", None)
         if text is None:
             raise ValueError(
                 'Running a sim requires a run text, could not find in text with name "run".'

### 2021-07-07 zpy_addon/segment_panel.py

@@ -6,6 +6,8 @@ import logging
 from typing import Tuple
 
 import bpy
+
+import client.util
 import zpy
 from bpy.types import Operator
 from bpy_extras.io_utils import ImportHelper
@@ -292,8 +294,8 @@ class CategoriesFromZUMOJSON(Operator, ImportHelper):
         for category in categories.values():
             _add_category(
                 context,
-                name=category.get("name", None),
-                color=category.get("color", None),
+                name=client.util.get("name", None),
+                color=client.util.get("color", None),
             )
         return {"FINISHED"}
 

### 2021-07-07 client/test.py
Fix code style issues with Black

@@ -8,9 +8,10 @@ def test_params(*args, **kwargs):
     zpy.init(**kwargs)
     # dataset = zpy.Dataset(**kwargs)
     # dataset.show_params()
-    sim = zpy.Sim('can_v5')
+    sim = zpy.Sim("can_v5")
     sim.show_params()
     sim.preview()
+
 
 def test_preview(*args, **kwargs):
     zpy.init(**kwargs)
@@ -33,22 +34,24 @@ def test_preview(*args, **kwargs):
 
 def test_generate(*args, **kwargs):
     zpy.init(**kwargs)
-    can_v5_sim = zpy.Sim('can_v5')
+    can_v5_sim = zpy.Sim("can_v5")
     can_v5_sim.show_params()
     can_v5_sim.preview({})
 
-    dataset_config = zpy.DatasetConfig('can_v5')
+    dataset_config = zpy.DatasetConfig("can_v5")
     print(json.dumps(dataset_config.available_params, indent=4, sort_keys=True))
     # Won't support "generic" properties yet
     # config.paramA = 1
     # config.paramB = 'blah'
-    dataset_config.set('custom_param', 'custom_val')
-    dataset_config.set('nested__custom__param', 'nested_val')
-    dataset_config.remove('nested__custom__param')
+    dataset_config.set("custom_param", "custom_val")
+    dataset_config.set("nested__custom__param", "nested_val")
+    dataset_config.remove("nested__custom__param")
 
     # Still requires pre-generating datasets, throw warnings if none found
     zpy.preview(dataset_config, num_samples=5)
-    dataset = zpy.generate('can_v5 test', dataset_config, num_datapoints=10, materialize=True)
+    dataset = zpy.generate(
+        "can_v5 test", dataset_config, num_datapoints=10, materialize=True
+    )
     # Return urls or do ipython
     # /api/v1/files?dataset=dataset_id&name_icontains="00000001"
     dataset.sample()

### 2021-07-07 client/util.py

@@ -109,7 +109,7 @@ def convert_size(size_bytes: int):
     return "%s %s" % (s, size_name[i])
 
 
-ERASE_LINE = '\x1b[2K'
+ERASE_LINE = "\x1b[2K"
 
 
 def clear_last_print():

### 2021-07-07 client/zpy.py

@@ -10,23 +10,42 @@ from typing import Dict, Union
 import requests
 
 from cli.utils import download_url
-from client.util import add_newline, get, post, to_query_param_value, convert_size, auth_header, \
-    clear_last_print, is_done
+from client.util import (
+    add_newline,
+    get,
+    post,
+    to_query_param_value,
+    convert_size,
+    auth_header,
+    clear_last_print,
+    is_done,
+)
 
 _auth_token: str = ""
 _base_url: str = ""
 _project: Union[Dict, None] = None
 
 
-def init(auth_token: str, project_uuid: str, base_url: str = "http://localhost:8000", **kwargs):
+def init(
+    auth_token: str,
+    project_uuid: str,
+    base_url: str = "http://localhost:8000",
+    **kwargs,
+):
     global _auth_token, _base_url, _project
     _auth_token = auth_token
     _base_url = base_url
 
     try:
-        _project = get(f"{_base_url}/api/v1/projects/{project_uuid}", headers=auth_header(_auth_token))
+        _project = get(
+            f"{_base_url}/api/v1/projects/{project_uuid}",
+            headers=auth_header(_auth_token),
+        )
     except requests.HTTPError:
-        print("Failed to find project, please double check the id and try again.", file=sys.stderr)
+        print(
+            "Failed to find project, please double check the id and try again.",
+            file=sys.stderr,
+        )
 
 
 IMAGES_PER_SAMPLE = 2  # for the iseg and rbg
@@ -58,16 +77,22 @@ class DatasetConfig:
             "project": _project["id"],
             "name": sim_name,
         }
-        sims = get(f"{_base_url}/api/v1/sims/", params=unique_sim_filters, headers=auth_header(_auth_token))["results"]
+        sims = get(
+            f"{_base_url}/api/v1/sims/",
+            params=unique_sim_filters,
+            headers=auth_header(_auth_token),
+        )["results"]
         if len(sims) > 1:
             raise RuntimeError(
-                f"Create DatasetConfig failed: Found more than 1 Sim for unique filters which should not be possible.")
+                f"Create DatasetConfig failed: Found more than 1 Sim for unique filters which should not be possible."
+            )
         elif len(sims) == 1:
             print(f"Found sim <{sim_name}> in project <{_project['name']}>")
             self._sim = sims[0]
         else:
             raise RuntimeError(
-                f"Create DatasetConfig failed: Could not find Sim<{sim_name}> in Project<{_project['name']}>.")
[…]

### 2021-07-07 docs/paper/paper.tex
Fixed citations, better image for software3

@@
 
-\usepackage[backend=biber, style=numeric]{biblatex}
-\addbibresource{references.bib}
-% \RequirePackage[backend=biber,
-% style=apa,
-% citestyle=authoryear
-% ]{biblatex}
-% \usepackage[square,numbers]{natbib}
+\usepackage[square,numbers]{natbib}
 
@@
 Edges interconnect vertices, and a closed loop of vertices creates a polygon known as a face.
+
 The engineering and manufacturing world creates meshes using computer-aided design (CAD) software such as AutoCAD \cite{autocad}, Solidworks \cite{solidworks}, Onshape \cite{onshape}, and Rhino \cite{rhino}.
@@
 	\includegraphics[width=\textwidth]{software3.png}
-	\caption{Software 3.0: the developer transitions from writing explicit algorithms to creating and curating datasets which are used to train machine learning models.}
+	\caption{The developer transitions from writing explicit rule-based algorithms (\emph{Software 2.0}) to creating and curating datasets and labels which are used to train machine learning algorithms (\emph{Software 3.0}).}
 	\label{fig:fig2}
@@
 
-% \bibliographystyle{abbrvnat}
-% \bibliography{references}
-\printbibliography
+\bibliographystyle{abbrvnat}
+\bibliography{references}
 

### 2021-07-07 docs/paper/paper.tex
better cover image

@@
 	\includegraphics[width=\textwidth]{cover.png}
-	\caption{Synthetic images of a raspberri pi created with zpy: (A) color image, (B) segmentation image, (C) depth image.
-These images are used to train a deep learning model, which predicts bounding boxes on key components as seen in the (D) prediction image}
+	\caption{Synthetic images of a Raspberry Pi created with zpy: (A) color image, (B) segmentation image, (C) depth image.
+These images are used to train a deep learning model, which predicts bounding boxes for circuit board components as seen in the (D) prediction image}
 	\label{fig:fig1}

### 2021-07-08 docs/paper/paper.tex
more images, references, thanks

@@
 In this work, we present zpy \footnote{All code is available on GitHub at \url{http://github.com/ZumoLabs/zpy}}, an open source framework for creating synthetic data.
-Built on top of Blender, and designed with modularity and readability in mind.
+Built on top of the popular open source 3D platform Blender.
+And designed with modularity and readability in mind.
 \end{abstract}
@@
 
+Usecases for synthetic data
+
+autonomous vehicles \ref{shermeyer2020rareplanes}, \ref{shermeyer2020rareplanes}, \ref{shermeyer2020rareplanes}, \ref{shermeyer2020rareplanes}
+
+pose estimation for humans \ref{shermeyer2020rareplanes}, \ref{shermeyer2020rareplanes}
+
+person re-id \ref{shermeyer2020rareplanes}
+
+detection in overhead satellite imagery \ref{shermeyer2020rareplanes}
+
+pose estimation of satellites in space \ref{kisantal2020satellite}
+
+segmentation of clouds \ref{shermeyer2020rareplanes}
+
 Challenges with synthetic data
 
-Sim2Real Gap and domain randomization
+We dive deeper into the effects of training curriculum on synthetic data in \ref{sec:curicculum}.
+
+Sim2Real Gap and domain randomization. We perform an ablation study on different types of domain randomization in \ref{sec:domainrandomization}
 
 Black box nature of ML
+
+Other attempts at open source synthetic data \cite{denninger2019blenderproc} \cite{bpycv}
 
@@
 
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{results.png}
+	\caption{Each type of domain randomization is used to create a fully synthetic dataset, which is used to fine-tune a pre-trained model on the task of package detection.
+Results of the model on a manually labeled test dataset of real images are compared.}
+	\label{fig:results}
+\end{figure}
+
 \section{Example}
@@
 
+Each individual training run
+
+Details on the training setup: GPU, total training time, total number of sweeps, epoch and batch size.
+
 \subsection{Domain Randomization}
@@
 
-In our package experiment, we expose two boolean toggles as run function kwargs that are categorized as forms of domain randomization.
+In our package experiment, we expose boolean toggles as run function kwargs that unlock certain forms of domain randomization.
 One toggle enables domain randomization in the lighting space: changing the position and intensity of several lights in the sim.
 The second toggle enables random HDRIs, which change the appearance of the background in the package images.
+The third toggle enables domain randomization for materials, which changes the appearance of the packages themselves, both the texture as well as the material properties.
+We perform an ablation study to pick appart the contributions of each type of domain randomization to the performance of a detection model trained on synthetic data with each respective form of domain randomization \ref{fig:results}.
+
+Deeper discussion of results
 
@@
 
-Training only on synthetic
+Training only on Synthetic
 
-Training on mixed synthetic and real
+ref to rare planes
+
+ref to mixed synthetic data
 
@@
 
-TODO
+\section{Thanks}
+\label{sec:thanks}
+
+Thanks to Aaron Dant and his team at ASRC Federal for discussions about synthetic data and comments on this paper.
+Thanks to the developer community of zpy for their feedback and contributions.
+Thanks to the investors and supporters of Zumo Labs for believing in the future of synthetic data.
 

### 2021-07-08 cli/cli.py
Change mkdocs add release notes and add gifs

@@ -795,16 +795,16 @@ def list_transforms(filters, project=None):
         return
 
     tbl = TableLogger(
-        columns="state,operation,input_data_set,created_at",
+        columns="state,operation,input_dataset,created_at",
         colwidth={
             "state": MEDIUM_WIDTH,
             "operation": SMALL_WIDTH,
-            "input_data_set": LARGE_WIDTH,
+            "input_dataset": LARGE_WIDTH,
             "created_at": DATETIME_WIDTH,
         },
     )
     for t in transforms:
-        tbl(t["state"], t["operation"], t["input_data_set"], t["created_at"])
+        tbl(t["state"], t["operation"], t["input_dataset"], t["created_at"])
 
 
 @transform_group.command("dataset")

### 2021-07-08 cli/datasets.py

@@ -166,7 +166,7 @@ def filter_datasets(dfilter, project, url, auth_headers):
         if r.status_code != 200:
             r.raise_for_status()
         response = json.loads(r.text)
-        for data_set in response["results"]:
-            filtered_datasets[data_set["id"]] = data_set["name"]
+        for dataset in response["results"]:
+            filtered_datasets[dataset["id"]] = dataset["name"]
         endpoint = response["next"]
     return filtered_datasets

### 2021-07-08 cli/transforms.py

@@ -26,7 +26,7 @@ def create_transform(name, operation, config, project, url, auth_headers):
         "project": project,
         "operation": operation,
         "name": name,
-        "input_data_set": dataset["id"],
+        "input_dataset": dataset["id"],
         "config": json.dumps(config),
     }
     r = requests.post(endpoint, data=data, headers=auth_headers)

### 2021-07-09 docs/paper/paper.tex
intro, references

@@
 In this work, we present zpy \footnote{All code is available on GitHub at \url{http://github.com/ZumoLabs/zpy}}, an open source framework for creating synthetic data.
-Built on top of the popular open source 3D platform Blender.
-And designed with modularity and readability in mind.
+Built on top of the popular open source 3D platform Blender, zpy is designed with accessibility and readability in mind.
+Open source synthetic data toolkits like zpy are the bridge between the more mature tools of the 3D workflow and the machine learning frameworks.
+We make the case for why open source synthetic data is important to solve issues such as fairness and bias by democratizing access to data.
 \end{abstract}
@@
 
-Open source machine learning frameworks (references)
+Synthetic data is data that is \emph{created} as opposed to \emph{collected}.
 
-Deep learning has exploded in popularity due to large open source frameworks such as tensorflow and pytorch
+Simulation heavy fields were amongst the first to start using synthetic images to start training deep learning systems.
+Research with the biggest datasets and highest quality can be found in this field, with works on autonomous vehicles \cite{prakash2020structured} \cite{srivastava2019multi} \cite{Hahner_2019} \cite{7780721}, robotic grasping \cite{james2019simtoreal} \cite{tobin2017domain}, and even drone racing \cite{Loquercio_2020}.
+The availability of high quality 3D humans from the video game and movie industries has also made possible applications such as human pose estimation  \cite{shrivastava2017learning} \cite{Varol_2017}, and person re-id \cite{aaronASRC}.
+We dive into what synthetic data could mean for human issues such as fairness and bias in \ref{sec:motivation}.
+Synthetic data has also been used to advance climate and space science, finding applications in detection in overhead satellite imagery \cite{shermeyer2020rareplanes}, pose estimation of satellites in space \cite{kisantal2020satellite}, and segmentation of clouds \cite{lyu2020learning}.
+Other work has dived deeper into the fundamental theory of synthetic data \cite{le2017using}.
+For a thorough review of synthetic data literature, we recommend readers go through Nikolenkos 2019 summary paper \cite{nikolenko2019synthetic}.
 
-What is synthetic data.
+Analogous to the early days of deep learning, synthetic data still has a black box nature.
+How to properly create and use synthetic data is not fully understood, and overcoming challenges such as the sim2real gap are still alchemy.
+We perform an ablation study to examine the effects of domain randomization on synthetic data in \ref{sec:domainrandomization}, and explore the importance of training curriculum in \ref{sec:curicculum}.
 
-Usecases for synthetic data
-
-autonomous vehicles \ref{shermeyer2020rareplanes}, \ref{shermeyer2020rareplanes}, \ref{shermeyer2020rareplanes}, \ref{shermeyer2020rareplanes}
-
-pose estimation for humans \ref{shermeyer2020rareplanes}, \ref{shermeyer2020rareplanes}
-
-person re-id \ref{shermeyer2020rareplanes}
-
-detection in overhead satellite imagery \ref{shermeyer2020rareplanes}
-
-pose estimation of satellites in space \ref{kisantal2020satellite}
-
-segmentation of clouds \ref{shermeyer2020rareplanes}
-
-Challenges with synthetic data
-
-We dive deeper into the effects of training curriculum on synthetic data in \ref{sec:curicculum}.
-
-Sim2Real Gap and domain randomization. We perform an ablation study on different types of domain randomization in \ref{sec:domainrandomization}
-
-Black box nature of ML
-
-Other attempts at open source synthetic data \cite{denninger2019blenderproc} \cite{bpycv}
-
-For a thorough review of synthetic data literature, we recommend readers go through Nikolenkos 2019 summary paper \cite{nikolenko2019synthetic}.
+Part of the maturation process of deep learning has been the emergence of large open source frameworks such as TensorFlow \cite{tensorflow} and PyTorch \cite{pytorch}.
+These tools have hundreds of thousands of developers worldwide, and will be the backbone of the AI technologies of the future.
+As synthetic data itself matures, there too we will see similar open source frameworks emerge.
+A critical piece of the synthetic data stack, the 3D worfklow, has already produced a champion: Blender \cite{blender}.
+We study the unique properties of Blender and why it emerged as the frontrunner in the 3D workflow race in \ref{sec:3d}.
+In fact, zpy is already one of several early attempts at an open source synthetic data toolkit \cite{denninger2019blenderproc} \cite{bpycv}.
 
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{webapp.png}
-	\caption{A visual interface for synthetic data creation via a WebApp.}
-	\label{fig:webapp}
-\end{figure}
-
 \section{Project Features}
@@
 This type of modular design can be seen in other popular python libraries, such as Matplotlib \cite{Hunter:2007}.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{webapp.png}
+	\caption{A visual interface for synthetic data creation via a WebApp.}
+	\label{fig:webapp}
+\end{figure}
 

### 2021-07-09 client/test.py
wip

@@ -75,7 +75,7 @@ if __name__ == "__main__":
         "sim_uuid": "a7188bb0-07b4-4817-9874-53c684eb4d6c",
     }
     staging_kwargs = {
-        "base_url": "https://ragnarok.stage.zumok8s.org",
+        "base_url": "https://ragnarok.zumok8s.org",
         # The rest need to match something on staging
         "auth_token": "4345497e868c4d4a7a563c05f604c41ed4825a049dbc9c38523254d53ef498c9",  # Auth token from localStorage
         "project_uuid": "4b0035d6-7bdd-4be3-adde-939c790437c3",  # Hugo's project has the most sims

### 2021-07-09 client/zpy.py

@@ -305,19 +305,33 @@ class Dataset:
     _dataset = None
 
     @require_zpy_init
-    def __init__(self, name: str):
+    def __init__(self, name: str = None, dataset: dict = None):
+        """
+        Construct a Dataset which is a local representation of a Dataset generated on the API.
+
+        Args:
+            name: If provided, Dataset will be automatically retrieved from the API.
+            dataset: If Dataset has already been retrieved from the API, provide this.
+        Returns
+            Dataset
+        """
         self._name = name
 
-        unique_dataset_filters = {
-            "project": _project["id"],
-            "name": name,
-        }
-        datasets = get(
-            f"{_base_url}/api/v1/datasets/",
-            params=unique_dataset_filters,
-            headers=auth_header(_auth_token),
-        )["results"]
-        self._dataset = datasets[0]
+        if dataset is not None:
+            self._dataset = dataset
+        else:
+            unique_dataset_filters = {
+                "project": _project["id"],
+                "name": name,
+            }
+            datasets = get(f"{_base_url}/api/v1/datasets/",
+                           params=unique_dataset_filters,
+                           headers=auth_header(_auth_token))["results"]
+            self._dataset = datasets[0]
+
+    @property
+    def id(self):
+        return self._dataset["id"]
 
     @property
     def name(self):
@@ -332,3 +346,7 @@ class Dataset:
     @property
     def config(self):
         return
+
+    def view(self):
+        return
+

### 2021-07-09 client/zpy.py
Fix code style issues with Black

@@ -324,9 +324,11 @@ class Dataset:
                 "project": _project["id"],
                 "name": name,
             }
-            datasets = get(f"{_base_url}/api/v1/datasets/",
-                           params=unique_dataset_filters,
-                           headers=auth_header(_auth_token))["results"]
+            datasets = get(
+                f"{_base_url}/api/v1/datasets/",
+                params=unique_dataset_filters,
+                headers=auth_header(_auth_token),
+            )["results"]
             self._dataset = datasets[0]
 
     @property
@@ -349,4 +351,3 @@ class Dataset:
 
     def view(self):
         return
-

### 2021-07-14 test/client.py
only look for .rgb in path now

@@ -18,10 +18,11 @@ def test_2(**init_kwargs):
     """In local env, simruns do NOT exist for config { "run.padding_style": "messy" }"""
     zpy.init(**init_kwargs)
     dataset_config = zpy.DatasetConfig("can_v7")
-    dataset_config.set("run\\.padding_style", "messy")
+    # dataset_config.set("run\\.padding_style", "messy")
     print(dataset_config.config)
     previews = zpy.preview(dataset_config)
     urls = [preview["url"] for preview in previews]
+    print(json.dumps(previews, indent=4, sort_keys=True))
     print(json.dumps(urls, indent=4, sort_keys=True))
 
 
@@ -29,8 +30,8 @@ def test_3(**init_kwargs):
     """"""
     zpy.init(**init_kwargs)
     dataset_config = zpy.DatasetConfig("can_v7")
-    dataset_config.set("run\\.padding_style", "square")
-    zpy.generate("can_v7.", dataset_config, num_datapoints=10, materialize=True)
+    # dataset_config.set("run\\.padding_style", "square")
+    zpy.generate("can_v7.4", dataset_config, num_datapoints=10, materialize=True)
 
 
 if __name__ == "__main__":
@@ -41,7 +42,7 @@ if __name__ == "__main__":
     }
     # init_kwargs = {
     #     "base_url": "https://ragnarok.stage.zumok8s.org",
-    #     "project_uuid": "feb6e594-55e0-4f87-9e75-5a128221499f",  # Zumo Internal
+    #     "project_uuid": "91419af0-4815-41e7-9b77-5ef8154148c8",  # Zumo Internal
     #     "auth_token": "a51cacaa01082ba5237b49f74cd6ffa5cf88339345383d97bcadd1f99e5f9a01",
     # }
     # init_kwargs = {
@@ -51,7 +52,7 @@ if __name__ == "__main__":
     # }
     # print("Running test_1:")
     # test_1(**init_kwargs)
-    # print("Running test_2:")
-    # test_2(**init_kwargs)
-    print("Running test_3:")
-    test_3(**init_kwargs)
+    print("Running test_2:")
+    test_2(**init_kwargs)
+    # print("Running test_3:")
+    # test_3(**init_kwargs)

### 2021-07-14 zpy/client.py

@@ -5,9 +5,9 @@ import time
 from datetime import datetime, timedelta
 from pathlib import Path
 from typing import Dict, Union
-from pydash import set_, unset
 
 import requests
+from pydash import set_, unset
 
 from cli.utils import download_url
 from zpy.client_util import (
@@ -165,20 +165,18 @@ def preview(dataset_config: DatasetConfig, num_samples=10):
         print("\t(no premade simruns matching filter)")
         return []
 
-    print(
-        "getting files with: {}".format(
-            f"{_base_url}/api/v1/files/?run__sim={dataset_config.sim['id']}&path__icontains=.rgb.png"
-        )
+    file_url = (
+        f"{_base_url}/api/v1/files/?run__sim={dataset_config.sim['id']}"
+        f"&path__icontains=.rgb"
+        f"&~path__icontains=.annotated"
     )
-    files_res = get(
-        f"{_base_url}/api/v1/files/?run__sim={dataset_config.sim['id']}&path__icontains=.rgb.png",
-        headers=auth_header(_auth_token),
-    )
+    print("getting files with: {}".format(file_url))
+    files_res = get(file_url, headers=auth_header(_auth_token))
     files = files_res["results"]
     if len(files) == 0:
         print(f"No preview available.")
         print("\t(no images found)")
-        return
+        return []
 
     return files
 

### 2021-07-14 test/client.py
fix no config bug. fix \r print statements (hopefully)

@@ -29,9 +29,9 @@ def test_2(**init_kwargs):
 def test_3(**init_kwargs):
     """"""
     zpy.init(**init_kwargs)
-    dataset_config = zpy.DatasetConfig("can_v7")
+    dataset_config = zpy.DatasetConfig("dumpster_v2")
     # dataset_config.set("run\\.padding_style", "square")
-    zpy.generate("can_v7.4", dataset_config, num_datapoints=10, materialize=True)
+    zpy.generate("dumpster_v2.16", dataset_config, num_datapoints=8, materialize=True)
 
 
 if __name__ == "__main__":
@@ -52,7 +52,7 @@ if __name__ == "__main__":
     # }
     # print("Running test_1:")
     # test_1(**init_kwargs)
-    print("Running test_2:")
-    test_2(**init_kwargs)
-    # print("Running test_3:")
-    # test_3(**init_kwargs)
+    # print("Running test_2:")
+    # test_2(**init_kwargs)
+    print("Running test_3:")
+    test_3(**init_kwargs)

### 2021-07-14 zpy/client.py

@@ -7,7 +7,7 @@ from pathlib import Path
 from typing import Dict, Union
 
 import requests
-from pydash import set_, unset
+from pydash import set_, unset, is_empty
 
 from cli.utils import download_url
 from zpy.client_util import (
@@ -71,7 +71,7 @@ class DatasetConfig:
             sim_name: Name of Sim
         """
         self._sim = None
-        self._config = None
+        self._config = {}
 
         unique_sim_filters = {
             "project": _project["id"],
@@ -114,8 +114,6 @@ class DatasetConfig:
             path: The json gin config path. Ex. given object { a: b: [{ c: 1 }]}, the value at path "a.b[0]c" is 1.
             value: The value for the gin config path provided.
         """
-        if self._config is None:
-            self._config = {}
         set_(self._config, path, value)
 
     def unset(self, path):
@@ -142,7 +140,7 @@ def preview(dataset_config: DatasetConfig, num_samples=10):
 
     config_filters = (
         {}
-        if dataset_config.config is None
+        if is_empty(dataset_config.config)
         else {"config": to_query_param_value(dataset_config.config)}
     )
     filter_params = {
@@ -223,6 +221,7 @@ def generate(
     )
 
     if materialize:
+        print("Materialize requested, waiting until dataset finishes to download it.")
         dataset = get(
             f"{_base_url}/api/v1/datasets/{dataset['id']}/",
             headers=auth_header(_auth_token),
@@ -231,13 +230,14 @@ def generate(
             next_check_datetime = datetime.now() + timedelta(seconds=60)
             while datetime.now() < next_check_datetime:
                 print(
-                    f"Dataset is not ready. Checking again in {(next_check_datetime - datetime.now()).seconds}s.",
-                    end="\r",
+                    "\r{}".format(
+                        f"Dataset is not ready. Checking again in {(next_check_datetime - datetime.now()).seconds}s."),
+                    end="",
                 )
                 time.sleep(1)
 
             clear_last_print()
-            print("Checking dataset...", end="\r")
+            print("\r{}".format("Checking dataset...", end=""))
             dataset = get(
                 f"{_base_url}/api/v1/datasets/{dataset['id']}/",
                 headers=auth_header(_auth_token),

### 2021-07-14 zpy/client.py
Fix code style issues with Black

@@ -231,7 +231,8 @@ def generate(
             while datetime.now() < next_check_datetime:
                 print(
                     "\r{}".format(
-                        f"Dataset is not ready. Checking again in {(next_check_datetime - datetime.now()).seconds}s."),
+                        f"Dataset is not ready. Checking again in {(next_check_datetime - datetime.now()).seconds}s."
+                    ),
                     end="",
                 )
                 time.sleep(1)

### 2021-07-14 test/client.py
show simrun progress, remove url to app

@@ -18,7 +18,7 @@ def test_2(**init_kwargs):
     """In local env, simruns do NOT exist for config { "run.padding_style": "messy" }"""
     zpy.init(**init_kwargs)
     dataset_config = zpy.DatasetConfig("can_v7")
-    # dataset_config.set("run\\.padding_style", "messy")
+    dataset_config.set("run\\.padding_style", "messy")
     print(dataset_config.config)
     previews = zpy.preview(dataset_config)
     urls = [preview["url"] for preview in previews]
@@ -31,7 +31,7 @@ def test_3(**init_kwargs):
     zpy.init(**init_kwargs)
     dataset_config = zpy.DatasetConfig("dumpster_v2")
     # dataset_config.set("run\\.padding_style", "square")
-    zpy.generate("dumpster_v2.16", dataset_config, num_datapoints=8, materialize=True)
+    zpy.generate("dumpster_v2.21", dataset_config, num_datapoints=3, materialize=True)
 
 
 if __name__ == "__main__":
@@ -42,7 +42,7 @@ if __name__ == "__main__":
     }
     # init_kwargs = {
     #     "base_url": "https://ragnarok.stage.zumok8s.org",
-    #     "project_uuid": "91419af0-4815-41e7-9b77-5ef8154148c8",  # Zumo Internal
+    #     "project_uuid": "91419af0-4815-41e7-9b77-5ef8154148c8",  # Compology
     #     "auth_token": "a51cacaa01082ba5237b49f74cd6ffa5cf88339345383d97bcadd1f99e5f9a01",
     # }
     # init_kwargs = {

### 2021-07-14 zpy/client.py

@@ -40,7 +40,7 @@ def init(
         _project = get(
             f"{_base_url}/api/v1/projects/{project_uuid}",
             headers=auth_header(_auth_token),
-        )
+        ).json()
     except requests.HTTPError:
         print(
             "Failed to find project, please double check the id and try again.",
@@ -81,7 +81,7 @@ class DatasetConfig:
             f"{_base_url}/api/v1/sims/",
             params=unique_sim_filters,
             headers=auth_header(_auth_token),
-        )["results"]
+        ).json()["results"]
         if len(sims) > 1:
             raise RuntimeError(
                 f"Create DatasetConfig failed: Found more than 1 Sim for unique filters which should not be possible."
@@ -154,23 +154,21 @@ def preview(dataset_config: DatasetConfig, num_samples=10):
         f"{_base_url}/api/v1/simruns/",
         params=filter_params,
         headers=auth_header(_auth_token),
-        verbose=True,
     )
-    simruns = simruns_res["results"]
+    simruns = simruns_res.json()["results"]
 
     if len(simruns) == 0:
         print(f"No preview available.")
-        print("\t(no premade simruns matching filter)")
+        print("\t(no premade SimRuns matching filter)")
         return []
 
-    file_url = (
-        f"{_base_url}/api/v1/files/?run__sim={dataset_config.sim['id']}"
-        f"&path__icontains=.rgb"
-        f"&~path__icontains=.annotated"
-    )
-    print("getting files with: {}".format(file_url))
-    files_res = get(file_url, headers=auth_header(_auth_token))
-    files = files_res["results"]
+    file_query_params = {
+        "run__sim": dataset_config.sim['id'],
+        "path__icontains": ".rgb",
+        "~path__icontains": ".annotated",
+    }
+    files_res = get(f"{_base_url}/api/v1/files/", params=file_query_params, headers=auth_header(_auth_token))
+    files = files_res.json()["results"]
     if len(files) == 0:
         print(f"No preview available.")
         print("\t(no images found)")
@@ -202,7 +200,7 @@ def generate(
             "name": name,
         },
         headers=auth_header(_auth_token),
-    )
+    ).json()
     post(
         f"{_base_url}/api/v1/datasets/{dataset['id']}/generate/",
         data={
@@ -216,22 +214,34 @@ def generate(
 
     print("Generating dataset:")
     print(json.dumps(dataset, indent=4, sort_keys=True))
-    print(
[…]

### 2021-07-14 zpy/client_util.py

@@ -35,7 +35,7 @@ def handle_response(response: requests.Response):
     Args:
         response: Request to handle
     Returns:
-        deserialized json response
+        requests.Response
     """
     if response.status_code != 200:
         if response.status_code == 400:
@@ -44,7 +44,7 @@ def handle_response(response: requests.Response):
         else:
             response.raise_for_status()
 
-    return response.json()
+    return response
 
 
 def get(url, **kwargs):
@@ -55,7 +55,7 @@ def get(url, **kwargs):
         url (str): Ragnarok API url
         kwargs: Forwarded to the requests.get function call
     Returns:
-        deserialized API response
+        requests.Response
     Raises:
         HTTPError
     """
@@ -74,7 +74,7 @@ def post(url, **kwargs):
         url (str): Ragnarok API url
         kwargs: Forwarded to the requests.post function call
     Returns:
-        deserialized API response
+         requests.Response
     Raises:
         HTTPError
     """

### 2021-07-14 zpy/client.py
Fix code style issues with Black

@@ -163,11 +163,15 @@ def preview(dataset_config: DatasetConfig, num_samples=10):
         return []
 
     file_query_params = {
-        "run__sim": dataset_config.sim['id'],
+        "run__sim": dataset_config.sim["id"],
         "path__icontains": ".rgb",
         "~path__icontains": ".annotated",
     }
-    files_res = get(f"{_base_url}/api/v1/files/", params=file_query_params, headers=auth_header(_auth_token))
+    files_res = get(
+        f"{_base_url}/api/v1/files/",
+        params=file_query_params,
+        headers=auth_header(_auth_token),
+    )
     files = files_res.json()["results"]
     if len(files) == 0:
         print(f"No preview available.")
@@ -222,9 +226,7 @@ def generate(
             headers=auth_header(_auth_token),
         ).json()
         while not is_done(dataset["state"]):
-            all_simruns_query_params = {
-                "datasets": dataset['id']
-            }
+            all_simruns_query_params = {"datasets": dataset["id"]}
             num_simruns = get(
                 f"{_base_url}/api/v1/simruns/",
                 params=all_simruns_query_params,
@@ -232,7 +234,7 @@ def generate(
             ).json()["count"]
             num_ready_simruns = get(
                 f"{_base_url}/api/v1/simruns/",
-                params={**all_simruns_query_params, 'state': 'READY'},
+                params={**all_simruns_query_params, "state": "READY"},
                 headers=auth_header(_auth_token),
             ).json()["count"]
             next_check_datetime = datetime.now() + timedelta(seconds=60)

### 2021-07-15 docs/paper/paper.tex
mvp2 updates

@@
 In this work, we present zpy \footnote{All code is available on GitHub at \url{http://github.com/ZumoLabs/zpy}}, an open source framework for creating synthetic data.
-Built on top of the popular open source 3D platform Blender, zpy is designed with accessibility and readability in mind.
+Built on top of the popular open source 3D toolset Blender, zpy is designed with accessibility and readability in mind.
 Open source synthetic data toolkits like zpy are the bridge between the more mature tools of the 3D workflow and the machine learning frameworks.
@@
 One type of asset scripting is called animation, which consists of creating sequential mesh deformations that create the illusion of natural movement.
-Animation is a tedious manual task because an artist must define every frame; expert animators spend decades honing their digital puppeteering skills.
+Animation is a tedious manual task because an artist must define almost every frame; expert animators spend decades honing their digital puppeteering skills.
 Specialized software is often used to automate this task as much as possible, and technologies such as Motion Capture (MoCap) can be used to record the movement of real objects and play those movements back on virtual assets.
@@
 Game Engines are software tools that allow for more structured and systematic asset scripting, mostly by providing software interfaces (e.g., code) to control the virtual world.
-Used extensively in the video game industry after which they were named, examples include Unity \cite{unity3d}, Unreal Engine \cite{unrealengine}, GoDot \cite{godot}, and Roblox \cite{roblox}.
+Used extensively in the video game industry after which they were named, examples include Unity \cite{unity3d}, Unreal Engine \cite{unrealengine}, Godot \cite{godot}, and Roblox \cite{roblox}.
 These game engines support rule-based spawning, animation, and complex interactions between assets in the virtual world.
@@
 \subsection{Democratization of Data}
+\label{sec:democratizationofdata}
 
 Modern computer vision systems use learning based methods and thus require large and diverse datasets.
-These datasets are almost exclusively collected: images are stored in databases as they are cumulatively generated by users of a product over time.
+The need for large and diverse datasets results in a data moat that precludes small companies from competing in the CV market.
+To amass a good dataset, a company needs time and money: precisely the two things that small nascent companies do not have.
+
+\subsection{The Status Quo}
+
+The problem lies in how the data pipeline works today.
+Currently, datasets are almost exclusively collected.
+mages are stored in databases as they are cumulatively generated by users of a product over time.
 Annotations are created by hand, usually by a third party provider using low-skilled labor in third world countries.
 Collecting and labeling a dataset large enough to train a robust computer vision model can take years.
-Only companies that have the scale and have set up the infrastructure to collect and store large datasets will have the datasets required to train models.
-
-In order to compete, small or newly formed companies often resort to purchasing data from a third party supplier.
-This market for the selling and reselling of collected data presents an existential threat to privacy.
-Though some regulations have emerged, famously GDPR in Europe, these have yet to change the landscape of the market for collected data.
-Synthetic data can democratize access to large-scale datasets by reducing the time required to collect these datasets and eliminating the cost of labeling these datasets.
+Moreover, labeling is not a one-off step, but rather a process that has to be repeated many times.
+Hand labeled data has shown itself to be imperfect.
+As one example, studies have found that the widely used ImageNet test set has an estimated label error rate of 5.8\% \cite{dataerrors}.
+The result is that only companies that have set up the infrastructure to collect and store large datasets, and then the money to subsequently label them, will have the datasets required to train models., Often, the only recourse for a small or newly formed company is to  purchase data from a third party supplier.
 
@@
 The large cost to collect and annotate datasets makes it prohibitive for most small organizations to create their own datasets, and as such it is common practice to use one of a small selection of openly available datasets (such as ImageNet).
-However, because of how these datasets have been collected over time, and due to the unequal global distribution of technologies such as cell phone cameras, these datasets are often biased.
-The real world is biased and unfair, and these collected datasets do not represent the large variety of cultural, demographic, or gender diversity  in human datasets \cite{shankar2017classification}.
-These datasets do not capture all geographic differences in object recognition datasets \cite{DBLP:journals/corr/abs-1906-02659}.
-The nature of statistical learning methods means that training on these biased datasets will result in a biased model: a model is only as good as the data on which it is trained.
-As such, it follows that the best way to reduce bias in modern computer vision systems is to improve the datasets these systems are trained on.
+This practice has resulted in the pervasive phenomenon of biased algorithms that perpetuate and codify racism, sexism, and bigotry.
+In the case of human datasets, irresponsibly collected datasets can also raise serious privacy concerns.
 
-Synthetic datasets offer full control of the distribution and can thus be designed to be more representative.
-A synthetic human dataset can equally represent cultural, demographic, or gender diversity.
-Synthetic datasets as a method of reducing bias has been explored in a variety of computer vision domains \cite{DBLP:journals/corr/abs-2004-13866}.
+\subsection{Algorithmic Bias}
+
+Algorithmic bias is when an algorithm exhibits a prejudice or inclination for one outcome over another.
+Because of how openly available datasets have been collected over time, and due to the unequal global distribution of technologies such as cell phone cameras, datasets are often biased.
+
+Algorithms don’t make fairness; they automate the status quo.
+The real world is biased and unfair.
+In human datasets, inevitably, publicly available image datasets exhibit Amero-centric and Euro-centric representation bias and do not adequately address true cultural, demographic, or gender diversity\cite{shankar2017classification}.
+Widely used public datasets for object recognition also fail to capture all geographic differences\cite{DBLP:journals/corr/abs-1906-02659}.
+
+Biased datasets result in biased algorithms.
+The nature of statistical learning methods means that training on these biased datasets will result in a biased model since a model is only as good as the data on which it is trained.
+The pervasive use of data-driven algorithms has complex social implications: from racial facial recognition (citation: https://nvlpubs.nist.gov/nistpubs/ir/2019/NIST.IR.8280.pdf), to predictive policing systems that act to confirm and deepen existing biases (citation: https://www.technologyreview.com/2020/07/17/1005396/predictive-policing-algorithms-racist-dismantled-machine-learning-bias-criminal-justice/).
+\subsection{Privacy}
+
+Using real data to train models presents very serious privacy risks with the rise of comprehensive privacy regimes like the GDPR in Europe and the CCPA in California.
+Openly available datasets offer no privacy guarantees as to whether all humans and biometrics represented in the dataset have been acquired with consent.
+
+Generally, today, the practice when using real datasets is to subject them to a de-identification process.
+De-identification, sometimes referred to as anonymization, strips a dataset of personal identifiers.
+However, there are two problems with this process: one, all anonymized data is subject to reversal.
+The only real bar is the state of technology at the point in time.
+Anonymized data today becomes pseudonymized data (data that can be reversed and re-identify individuals) tomorrow as models become better at re-identifying data points.
+Second, anonymized data is not as useful: it is less rich and many times lacks the information required to train a model.
+
+\subsection{Synthetic Data as a Solution}
+
+Synthetic data can democratize access to large-scale datasets by reducing the time required to collect these datasets and eliminating the cost of labeling these datasets.
+
+Furthermore, synthetic data presents a solution to algorithmic bias: synthetic datasets offer complete control of the distribution and can thus be representatively designed.
+A synthetic human dataset can be constructed to represent cultural, demographic, and gender diversity equally.
+A variety of computer vision domains have explored using synthetic datasets to reduce bias effectively \cite{DBLP:journals/corr/abs-2004-13866}.
+
+Finally, synthetic datasets, by virtue of being created and not collected, guarantees privacy compliance.
+Synthetic data is free of personal identifiers that could be susceptible to re-identification down the road.
+Synthetic data guarantees privacy by changing the paradigm and getting rid of any need to use real data.
 
@@
 Dataset generation jobs can be made with the zpy Python API \ref{lst:api} and CLI \ref{lst:cli} such that many computers are used, thus speeding up the generation job.
-The ZumoLabs cloud uses orchestration technology, e.g.
+The Zumo Labs cloud uses orchestration technology, e.g.
 Kubernetes, to spin up and manage new image generation nodes.
@@
 
-The zpy python package is organized as a collection of seperate modules.
+The zpy python package is organized as a collection of separate modules.
 These modules are separated based on their dependencies and functionality.

### 2021-07-16 test/client.py
test dataset format function

@@ -1,4 +1,8 @@
 import json
+from os import listdir
+from os.path import join
+import shutil
+import re
 
 import zpy.client as zpy
 
@@ -34,6 +38,41 @@ def test_3(**init_kwargs):
     zpy.generate("dumpster_v2.21", dataset_config, num_datapoints=3, materialize=True)
 
 
+def test_saver_func(images, annotations):
+    '''
+    Same output as:
+    https://gist.github.com/steven-zumo/d44b16ae5173931c7943f8f4531cda41
+    
+    '''
+    output_path = '/mnt/c/Users/georg/Zumo/Datasets/dumpster_v2.1_formatted'
+    for img in images:
+        # maybe an awkward way to match an image to it's annotation
+        img_annotation = next((a for a in annotations['annotations'] if a["filename_image"] in img), None)
+        if img_annotation is not None:
+            category_id = str(img_annotation['category_id'])
+            category_label = annotations['categories'][category_id]['name']
+            # awkward way to access batch name from image uri
+            batch = img.split("/")[-2]
+            # save same result as stevens example
+            output_file_uri = join(output_path, category_label + '-' + batch[:4] + '-' + img_annotation['filename_image'] + '.jpg')
+            shutil.copy(img, output_file_uri)
+
+
+def format_dataset(path_to_zipped_dataset, saver_func):
+    # https://www.geeksforgeeks.org/how-to-validate-image-file-extension-using-regular-expression/
+    # https://realpython.com/regex-python/ - How to fix from example - DeprecationWarning: Flags not at the start of the expression
+    regex = "(?i)([^\\s]+(\\.(jpe?g|png|gif|bmp))$)" # Regex to check valid image file extension.
+    pattern = re.compile(regex)
+    annotation_file_name = '_annotations.zumo.json'
+    for batch in listdir(path_to_zipped_dataset):
+        batch_uri = join(path_to_zipped_dataset, batch)
+        image_names = [str for str in listdir(batch_uri) if re.search(pattern, str)]
+        image_uris = [join(path_to_zipped_dataset, batch, p) for p in image_names]
+        annotation_file_uri = join(batch_uri, annotation_file_name)
+        metadata = json.load(open(annotation_file_uri))
+        saver_func(image_uris, metadata)
+
+
 if __name__ == "__main__":
     init_kwargs = {
         "base_url": "http://localhost:8000",
[…]

### 2021-07-16 test/client.py
Fix code style issues with Black

@@ -39,31 +39,41 @@ def test_3(**init_kwargs):
 
 
 def test_saver_func(images, annotations):
-    '''
+    """
     Same output as:
     https://gist.github.com/steven-zumo/d44b16ae5173931c7943f8f4531cda41
-    
-    '''
-    output_path = '/mnt/c/Users/georg/Zumo/Datasets/dumpster_v2.1_formatted'
+
+    """
+    output_path = "/mnt/c/Users/georg/Zumo/Datasets/dumpster_v2.1_formatted"
     for img in images:
         # maybe an awkward way to match an image to it's annotation
-        img_annotation = next((a for a in annotations['annotations'] if a["filename_image"] in img), None)
+        img_annotation = next(
+            (a for a in annotations["annotations"] if a["filename_image"] in img), None
+        )
         if img_annotation is not None:
-            category_id = str(img_annotation['category_id'])
-            category_label = annotations['categories'][category_id]['name']
+            category_id = str(img_annotation["category_id"])
+            category_label = annotations["categories"][category_id]["name"]
             # awkward way to access batch name from image uri
             batch = img.split("/")[-2]
             # save same result as stevens example
-            output_file_uri = join(output_path, category_label + '-' + batch[:4] + '-' + img_annotation['filename_image'] + '.jpg')
+            output_file_uri = join(
+                output_path,
+                category_label
+                + "-"
+                + batch[:4]
+                + "-"
+                + img_annotation["filename_image"]
+                + ".jpg",
+            )
             shutil.copy(img, output_file_uri)
 
 
 def format_dataset(path_to_zipped_dataset, saver_func):
     # https://www.geeksforgeeks.org/how-to-validate-image-file-extension-using-regular-expression/
     # https://realpython.com/regex-python/ - How to fix from example - DeprecationWarning: Flags not at the start of the expression
-    regex = "(?i)([^\\s]+(\\.(jpe?g|png|gif|bmp))$)" # Regex to check valid image file extension.
+    regex = "(?i)([^\\s]+(\\.(jpe?g|png|gif|bmp))$)"  # Regex to check valid image file extension.
     pattern = re.compile(regex)
-    annotation_file_name = '_annotations.zumo.json'
+    annotation_file_name = "_annotations.zumo.json"
     for batch in listdir(path_to_zipped_dataset):
[…]

### 2021-07-16 cli/cli.py
Update `project create` help to proper CLI format

@@ -361,7 +361,7 @@ def list_projects(filters):
 def create_project(account, name):
     """Create a project under ACCOUNT called NAME.
 
-    See available accounts: zpy list accounts
+    See available accounts: zpy account list
     """
     from cli.projects import create_project
 

### 2021-08-03 test/client.py
Fix code style issues with Black

@@ -215,17 +215,17 @@ class TestClientUtilMethods(unittest.TestCase):
             "/home/korystiger/Downloads/malibu-3k-0aac7584.zip",
             # '/home/korystiger/Downloads/can_v714-8c288ec8.zip',
             # format_dataset('/home/korystiger/Downloads/trailer_empty_v5-f9b7ccb2.zip',
-            datapoint_callback=datapoint_callback)
+            datapoint_callback=datapoint_callback,
+        )
 
         for tvt_type in ["train", "val", "test"]:
             for category_id, count in category_counts[tvt_type].items():
-                metadata[tvt_type]['categories'][category_id]['count'] = count
+                metadata[tvt_type]["categories"][category_id]["count"] = count
 
             print(f"Writing {tvt_type} json...")
             path = str(output_dir / tvt_type / "annotations.json")
             blob = metadata[tvt_type]
             write_json(path, blob)
-
 
     def test_generate_and_format_dataset(self):
         output_dir = Path("/home/korystiger/Downloads/ktest")
@@ -240,7 +240,9 @@ class TestClientUtilMethods(unittest.TestCase):
             tvt_type: {"categories": {}, "images": {}, "annotations": []}
             for tvt_type in ["train", "val", "test"]
         }
-        category_counts = {tvt_type: defaultdict(int) for tvt_type in ["train", "val", "test"]}
+        category_counts = {
+            tvt_type: defaultdict(int) for tvt_type in ["train", "val", "test"]
+        }
 
         def datapoint_callback(images, annotations, categories):
             r = random.random()
@@ -264,9 +266,11 @@ class TestClientUtilMethods(unittest.TestCase):
                     "name": image["id"],
                 }
 
-                filtered_annotations_by_image_id = [a for a in annotations if a['image_id'] == image['id']]
+                filtered_annotations_by_image_id = [
+                    a for a in annotations if a["image_id"] == image["id"]
+                ]
                 for annotation in filtered_annotations_by_image_id:
-                    category_counts[tvt_type][annotation['category_id']] += 1
+                    category_counts[tvt_type][annotation["category_id"]] += 1
 
             metadata[tvt_type]["annotations"].extend(annotations)
 

### 2021-08-03 zpy/client.py
remove ability to instantiate DatasetConfig directly

@@ -4,10 +4,9 @@ import time
 from datetime import datetime, timedelta
 from os import listdir
 from pathlib import Path
-from typing import Dict, Union
-from uuid import UUID
 from typing import Dict
 from typing import Union
+from uuid import UUID
 
 import requests.exceptions
 from pydash import set_, unset, is_empty, pascal_case
@@ -99,6 +98,7 @@ def init(
         elif e.response.status_code == 404:
             raise InvalidProjectError("Init failed: you are not part of this project or it does not exist.") from None
 
+
 DATASET_OUTPUT_PATH = Path("/tmp")  # for generate and default_saver_func
 
 
@@ -118,17 +118,20 @@ DYNAMIC_ATTRIBUTE_GIN_PREFIX = 'run.'
 
 
 class DatasetConfig:
-    @require_zpy_init
-    def __init__(self, sim_name: str):
-        """
-        Create a DatasetConfig. Used by zpy.preview and zpy.generate.
-
-        Args:
-            sim_name (str): Name of Sim.
-        """
+    def __init__(self, *args, **kwargs):
+        # Placeholders to make IDEs happy. Actual value setting happens in the from_sim_name factory method.
         self._sim = None
         self._config = {}
+        raise RuntimeWarning('DatasetConfig is not directly instantiable any more. Use DatasetConfig.from_sim_name!')
 
+    @classmethod
+    @require_zpy_init
+    def from_sim_name(cls, sim_name: str):
+        """Create a Sim specific DatasetConfig with instance attributes corresponding to adjustable Sim parameters.
+
+        Args:
+            sim_name (str): The name of the Sim.
+        """
         unique_sim_filters = {
             "project": _project["id"],
             "name": sim_name,
@@ -140,22 +143,13 @@ class DatasetConfig:
         ).json()["results"]
         if len(sims) == 1:
             print(f"Found Sim<{sim_name}> in Project<{_project['name']}>")
-            self._sim = sims[0]
+            sim = sims[0]
         else:
             raise InvalidSimError(f"Could not find Sim<{sim_name}> in Project<{_project['name']}>.")
 
-    @classmethod
-    def from_sim_name(cls, sim_name: str):
-        """Create a Sim specific DatasetConfig with instance attributes corresponding to adjustable Sim parameters.
-
-        Args:
-            sim_name (str): The name of the Sim.
-        """
-        dataset_config = DatasetConfig(sim_name)
-
         # Add the run_kwargs as attributes to the class
[…]

### 2021-08-03 cli/cli.py
Fix code style issues with Black

@@ -32,7 +32,7 @@ def cli(ctx, api_version):
     """
     initialize_config()
     ctx.ensure_object(dict)
-    ctx.obj['API_VERSION'] = api_version
+    ctx.obj["API_VERSION"] = api_version
 
 
 @cli.command("help")

### 2021-08-03 test/client.py

@@ -136,7 +136,9 @@ class TestClient(unittest.TestCase):
             tvt_type: {"categories": {}, "images": {}, "annotations": []}
             for tvt_type in ["train", "val", "test"]
         }
-        category_counts = {tvt_type: defaultdict(int) for tvt_type in ["train", "val", "test"]}
+        category_counts = {
+            tvt_type: defaultdict(int) for tvt_type in ["train", "val", "test"]
+        }
 
         def datapoint_callback(images, annotations, categories):
             r = random.random()
@@ -160,9 +162,11 @@ class TestClient(unittest.TestCase):
                     "name": image["id"],
                 }
 
-                filtered_annotations_by_image_id = [a for a in annotations if a['image_id'] == image['id']]
+                filtered_annotations_by_image_id = [
+                    a for a in annotations if a["image_id"] == image["id"]
+                ]
                 for annotation in filtered_annotations_by_image_id:
-                    category_counts[tvt_type][annotation['category_id']] += 1
+                    category_counts[tvt_type][annotation["category_id"]] += 1
 
             metadata[tvt_type]["annotations"].extend(annotations)
 

### 2021-08-03 zpy/client.py

@@ -35,16 +35,19 @@ _project: Union[Dict, None] = None
 
 class InvalidAuthTokenError(Exception):
     """Raised when an auth_token is missing or invalid."""
+
     pass
 
 
 class InvalidProjectError(Exception):
     """Raised when accessing a project which does not exist or without appropriate access permissions."""
+
     pass
 
 
 class ClientNotInitializedError(Exception):
     """Raised when trying to use functionality which is dependent on calling client.init()"""
+
     pass
 
 
@@ -53,10 +56,10 @@ class InvalidSimError(Exception):
 
 
 def init(
-        auth_token: str = '',
-        project_uuid: str = '',
-        base_url: str = "https://ragnarok.zumok8s.org",
-        version: str = "v2",
+    auth_token: str = "",
+    project_uuid: str = "",
+    base_url: str = "https://ragnarok.zumok8s.org",
+    version: str = "v2",
 ):
     """
     Initializes the zpy client library.
@@ -79,11 +82,14 @@ def init(
     try:
         UUID(project_uuid, version=4)
     except ValueError:
-        raise InvalidProjectError("Init failed: project_uuid must be a valid uuid4 string.") from None
+        raise InvalidProjectError(
+            "Init failed: project_uuid must be a valid uuid4 string."
+        ) from None
 
     if is_empty(auth_token):
         raise InvalidAuthTokenError(
-            f"Init failed: invalid auth token - find yours at https://app.zumolabs.ai/settings/auth-token.")
+            f"Init failed: invalid auth token - find yours at https://app.zumolabs.ai/settings/auth-token."
+        )
 
     try:
         _project = get(
@@ -94,9 +100,12 @@ def init(
     except requests.exceptions.HTTPError as e:
         if e.response.status_code == 401:
             raise InvalidAuthTokenError(
-                f"Init failed: invalid auth token - find yours at https://app.zumolabs.ai/settings/auth-token.") from None
+                f"Init failed: invalid auth token - find yours at https://app.zumolabs.ai/settings/auth-token."
+            ) from None
         elif e.response.status_code == 404:
-            raise InvalidProjectError("Init failed: you are not part of this project or it does not exist.") from None
+            raise InvalidProjectError(
+                "Init failed: you are not part of this project or it does not exist."
+            ) from None
 
 
 DATASET_OUTPUT_PATH = Path("/tmp")  # for generate and default_saver_func
[…]

### 2021-08-03 zpy/client.py
--wip-- [skip ci]

@@ -121,7 +121,7 @@ class DatasetConfig:
         """Set a value for a configurable parameter.
 
         Args:
-            path: The json gin config path. Ex. given object { a: b: [{ c: 1 }]}, the value at path "a.b[0]c" is 1.
+            path: The json gin config path. Ex. given object { a: b: [{ c: 1 }]}, the value at path "a.b[0].c" is 1.
             value: The value for the gin config path provided.
         """
         set_(self._config, path, value)

### 2021-08-03 zpy/client.py
update docstrings

@@ -34,8 +34,17 @@ def init(
     auth_token: str,
     project_uuid: str,
     base_url: str = "https://ragnarok.zumok8s.org",
-    **kwargs,
 ):
+    """
+    Initializes the zpy client library.
+
+    Args:
+        auth_token (str): API auth_token. Required for all internal API calls.
+        project_uuid (str): A valid uuid4 project id. Required to scope permissions for all requested API objects.
+        base_url (str, optional): API url. Overridable for testing different environments.
+    Returns:
+        None: No return value.
+    """
     global _auth_token, _base_url, _project
     _auth_token = auth_token
     _base_url = base_url
@@ -68,7 +77,7 @@ def require_zpy_init(func):
 
 class DatasetConfig:
     @require_zpy_init
-    def __init__(self, sim_name: str, **kwargs):
+    def __init__(self, sim_name: str):
         """
         Create a DatasetConfig. Used by zpy.preview and zpy.generate.
 
@@ -101,36 +110,70 @@ class DatasetConfig:
 
     @property
     def sim(self):
+        """
+        Returns:
+            dict: The Sim object.
+        """
         return self._sim
 
     @property
     def available_params(self):
+        """
+        Returns:
+            dict[]: The Sim's adjustable parameters.
+        """
         return self._sim["run_kwargs"]
 
     @property
     def config(self):
-        """A dict representing a json object of gin config parameters."""
+        """
+        Property which holds the parameters managed via DatasetConfig.set() and DatasetConfig.unset()
+
+        Returns:
+            dict: A dict representing a json object of gin config parameters.
+        """
         return self._config
 
     @property
     def hash(self):
-        """Return a hash of the config."""
+        """
+        Returns:
+             str: A deterministic hash of the internal _config dictionary.
+        """
         return dict_hash(self._config)
 
     def set(self, path: str, value: any):
-        """Set a value for a configurable parameter.
+        """
+        Set a configurable parameter. Uses pydash.set_.
+
+                https://pydash.readthedocs.io/en/latest/api.html#pydash.objects.set_
 
         Args:
-            path: The json gin config path. Ex. given object { a: b: [{ c: 1 }]}, the value at path "a.b[0].c" is 1.
-            value: The value for the gin config path provided.
+            path: The json gin config path using pydash.set_ notation.
+            value: The value to be set at the provided gin config path.
+        Returns:
+            None: No return value
+        Examples:
+            Given the following object, the value at path `a.b[0].c` is 1.
+
[…]

### 2021-08-03 test/client.py
remove duplicate test

@@ -211,72 +211,6 @@ class TestClientUtilMethods(unittest.TestCase):
             for category in categories:
                 metadata[tvt_type]["categories"][category["id"]] = category
 
-        format_dataset(
-            "/home/korystiger/Downloads/malibu-3k-0aac7584.zip",
-            # '/home/korystiger/Downloads/can_v714-8c288ec8.zip',
-            # format_dataset('/home/korystiger/Downloads/trailer_empty_v5-f9b7ccb2.zip',
-            datapoint_callback=datapoint_callback,
-        )
-
-        for tvt_type in ["train", "val", "test"]:
-            for category_id, count in category_counts[tvt_type].items():
-                metadata[tvt_type]["categories"][category_id]["count"] = count
-
-            print(f"Writing {tvt_type} json...")
-            path = str(output_dir / tvt_type / "annotations.json")
-            blob = metadata[tvt_type]
-            write_json(path, blob)
-
-    def test_generate_and_format_dataset(self):
-        output_dir = Path("/home/korystiger/Downloads/ktest")
-        if output_dir.exists():
-            shutil.rmtree(output_dir)
-
-        os.makedirs(output_dir / "train", exist_ok=True)
-        os.makedirs(output_dir / "val", exist_ok=True)
-        os.makedirs(output_dir / "test", exist_ok=True)
-
-        metadata = {
-            tvt_type: {"categories": {}, "images": {}, "annotations": []}
-            for tvt_type in ["train", "val", "test"]
-        }
-        category_counts = {
-            tvt_type: defaultdict(int) for tvt_type in ["train", "val", "test"]
-        }
-
-        def datapoint_callback(images, annotations, categories):
-            r = random.random()
-
-            if r < 0.4:
-                tvt_type = "train"
-            elif r < 0.8:
-                tvt_type = "test"
-            else:
-                tvt_type = "val"
-
-            for image in images:
-                new_path = output_dir / tvt_type / image["id"]
-
-                shutil.copy(image["output_path"], new_path)
-
-                metadata[tvt_type]["images"][image["id"]] = {
-                    **image,
-                    "output_path": str(new_path),
-                    "relative_path": image["id"],
-                    "name": image["id"],
-                }
-
-                filtered_annotations_by_image_id = [
-                    a for a in annotations if a["image_id"] == image["id"]
-                ]
-                for annotation in filtered_annotations_by_image_id:
[…]

### 2021-08-03 zpy/client.py
clean out cruft in Dataset config

@@ -351,36 +351,20 @@ def generate(
                 f"Dataset is no longer running but cannot be downloaded with state = {dataset['state']}"
             )
 
-    return Dataset(dataset["name"], dataset)
+    return Dataset(internal_dataset_name, dataset_config)
 
 
 class Dataset:
-    _dataset = None
-
-    @require_zpy_init
-    def __init__(self, name: str = None, dataset: dict = None):
+    def __init__(self, name: str = None, dataset_config: DatasetConfig = None):
         """
         Construct a Dataset which is a local representation of a Dataset generated on the API.
 
         Args:
-            name: If provided, Dataset will be automatically retrieved from the API.
-            dataset: If Dataset has already been retrieved from the API, provide this.
+            name (str): The name of the Dataset.
+            dataset_config (DatasetConfig): The DatasetConfig used to generate this Dataset.
         """
         self._name = name
-
-        if dataset is not None:
-            self._dataset = dataset
-        else:
-            unique_dataset_filters = {
-                "project": _project["id"],
-                "name": name,
-            }
-            datasets = get(
-                f"{_base_url}/api/v1/datasets/",
-                params=unique_dataset_filters,
-                headers=auth_header(_auth_token),
-            ).json()["results"]
-            self._dataset = datasets[0]
+        self._config = dataset_config
 
     @property
     def name(self):
@@ -396,4 +380,4 @@ class Dataset:
         Returns:
             DatasetConfig: The configuration used to generate this dataset.
         """
-        return None
+        return self._config

### 2021-08-03 test/client.py
updating prints for consistency. remove debug timing

@@ -213,7 +213,7 @@ class TestClientUtilMethods(unittest.TestCase):
 
         zpy.init(
             project_uuid="feb6e594-55e0-4f87-9e75-5a128221499f",
-            auth_token="6812a36a1613dda3e0458e4ce4893e3e1ccc4c39dcf4368c862e670dabe76d8a",
+            auth_token="12ea8d406b508be8fd0a1fef78f825440347fb10989536fcd1dedb9241327491",
         )
         dataset_config = zpy.DatasetConfig("dumpster_v5.1")
         dataset_config.set("run\.padding_style", "random")

### 2021-08-03 zpy/client.py

@@ -136,16 +136,11 @@ class DatasetConfig:
 
     @property
     def hash(self):
-<<<<<<< HEAD
-        """Return a hash of the config."""
-        return dict_hash(self._config)[:8]
-=======
         """
         Returns:
              str: A deterministic hash of the internal _config dictionary.
         """
-        return dict_hash(self._config)
->>>>>>> 4668008b80e63a1154813c202cdcb31961de7bd3
+        return dict_hash(self._config)[:8]
 
     def set(self, path: str, value: any):
         """
@@ -217,7 +212,7 @@ def preview(dataset_config: DatasetConfig, num_samples=10):
 
     if len(simruns) == 0:
         print("No preview available.")
-        print("\t(no premade SimRuns matching filter)")
+        print("\t(no SimRuns matching filter)")
         return []
 
     file_query_params = {
@@ -288,13 +283,14 @@ def generate(
             },
             headers=auth_header(_auth_token),
         )
-        print("Generating dataset:")
+        print(f"Sending generate request for Dataset<{internal_dataset_name}>...")
         print(json.dumps(dataset, indent=4, sort_keys=True))
     else:
+        print(f"Generate for Dataset<{internal_dataset_name}> has already been requested.")
         dataset = datasets_res["results"][0]
 
     if materialize:
-        print("Materialize requested, waiting until dataset finishes to download it.")
+        print(f"Materializing Dataset<{internal_dataset_name}>...")
         dataset = get(
             f"{_base_url}/api/v1/datasets/{dataset['id']}/",
             headers=auth_header(_auth_token),
@@ -321,41 +317,37 @@ def generate(
                 )
                 time.sleep(1)
             clear_last_print()
-            print("Checking dataset...", end="\r")
+            print(f"Checking state of Dataset<{dataset['name']}>...", end="\r")
             dataset = get(
                 f"{_base_url}/api/v1/datasets/{dataset['id']}/",
                 headers=auth_header(_auth_token),
             ).json()
 
         if dataset["state"] == "READY":
-            print("Dataset is ready for download.")
             dataset_download_res = get(
                 f"{_base_url}/api/v1/datasets/{dataset['id']}/download/",
                 headers=auth_header(_auth_token),
             ).json()
-            name_slug = (
-                f"{str(dataset['name']).replace(' ', '_')}-{dataset['id'][:8]}.zip"
-            )
+            name_slug = f"{dataset['name']}.zip"
[…]

### 2021-08-03 zpy/client_util.py

@@ -1,6 +1,7 @@
 import functools
 import hashlib
 import json
+import logging
 import math
 import os
 import shutil
@@ -192,12 +193,12 @@ def dict_hash(data) -> str:
     return config_hash
 
 
-@track_runtime
 def extract_zip(path_to_zip: Path, output_path: Path):
     """
     Extracts a .zip to a new adjacent folder by the same name.
     Args:
-        path_to_zip: Path to .zip
+        path_to_zip (Path): Path to .zip to extract.
+        output_path (Path): Path of where to extract to.
     Returns:
         None: No return value
     """
@@ -205,7 +206,6 @@ def extract_zip(path_to_zip: Path, output_path: Path):
         zip_ref.extractall(output_path)
 
 
-@track_runtime
 def write_json(path, json_blob):
     """
     Args:
@@ -235,7 +235,6 @@ def group_by(iterable: Iterable, keyfunc: Callable) -> List[List]:
     ]
 
 
-@track_runtime
 def group_metadata_by_datapoint(
     dataset_path: Path,
 ) -> Tuple[Dict, List[Dict], List[Dict]]:
@@ -249,7 +248,6 @@ def group_metadata_by_datapoint(
             categories, datapoints), datapoints being a list of dicts, each containing a list of images and a list of
             annotations.
     """
-    print("Parsing dataset to group by datapoint...")
     accum_metadata = {}
     accum_categories = {}
     accum_datapoints = []
@@ -336,9 +334,7 @@ def format_dataset(
     Returns:
         None: No return value.
     """
-    raw_dataset_path = Path(
-        join(Path(zipped_dataset_path).parent, Path(zipped_dataset_path).name + "_raw")
-    )
+    raw_dataset_path = Path(zipped_dataset_path).parent / (Path(zipped_dataset_path).with_suffix('').name + "_raw")
 
     if not raw_dataset_path.exists():
         print(f"Unzipping {zipped_dataset_path}...")
@@ -356,7 +352,9 @@ def format_dataset(
     else:
         print("Doing default formatting for dataset...")
         output_dir = Path(remove_n_extensions(zipped_dataset_path, n=1))
-        os.makedirs(output_dir, exist_ok=True)
+        if Path(output_dir).exists():
+            shutil.rmtree(output_dir)
+        os.makedirs(output_dir)
 
         accum_metadata = {
             "metadata": {

### 2021-08-03 test/client.py
truncate hash and remove _formatted name. Known bug: _raw dataset name still has .zip in name

@@ -44,7 +44,7 @@ def pretty_print(object):
 
 def test_generate(**init_kwargs):
     zpy.init(**init_kwargs)
-    dataset_config = zpy.DatasetConfig("can_v7")
+    dataset_config = zpy.DatasetConfig("dumpster_v5.1")
 
     def datapoint_callback(images, annotations, categories):
         pretty_print(images)
@@ -53,7 +53,7 @@ def test_generate(**init_kwargs):
 
     dataset = zpy.generate(
         dataset_config,
-        num_datapoints=39,
+        num_datapoints=40,
         materialize=True,
         # datapoint_callback=datapoint_callback
     )
@@ -298,16 +298,17 @@ class TestClientUtilMethods(unittest.TestCase):
 
 
 if __name__ == "__main__":
-    unittest.main()
+    # unittest.main()
+    # unittest.main().test_generate()
     # init_kwargs = {
     #     "base_url": "http://localhost:8000",
     #     "project_uuid": "aad8e2b2-5431-4104-a205-dc3b638b0dab",
     #     "auth_token": "214540cbd525f1ecf2bc52e2ddb7ef76801048e3f55aa4b33a9e501b115a736e",
     # }
     init_kwargs = {
-        "base_url": "https://ragnarok.stage.zumok8s.org",
+        "base_url": "https://ragnarok.zumok8s.org",
         "project_uuid": "feb6e594-55e0-4f87-9e75-5a128221499f",
-        "auth_token": "a19f8a1cef0c1661f7de1fd513d740c499752fc567fc4c6fe6d11fdbce533b65",
+        "auth_token": "d656d40f144221aedcfa774bbf36b4caccf1e16de3f0ac2520d40d450da7bf2e",
     }
     # init_kwargs = {
     #     "base_url": "https://ragnarok.stage.zumok8s.org",
@@ -330,8 +331,7 @@ if __name__ == "__main__":
     #     pretty_print(annotations)
     #     pretty_print(categories)
 
-    # input_path = "/mnt/c/Users/georg/Zumo/Datasets/can_v714-8c288ec8.zip"
-    # dataset_path = extract_zip(input_path)
-    # format_dataset(dataset_path, datapoint_callback)
+    # zip_path = "/mnt/c/Users/georg/Zumo/Datasets/can_v714-8c288ec8.zip"
+    # format_dataset(zip_path)
 
-    # test_generate(**init_kwargs)
+    test_generate(**init_kwargs)

### 2021-08-03 zpy/client.py

@@ -115,7 +115,7 @@ class DatasetConfig:
     @property
     def hash(self):
         """Return a hash of the config."""
-        return dict_hash(self._config)
+        return dict_hash(self._config)[:8]
 
     def set(self, path: str, value: any):
         """Set a value for a configurable parameter.

### 2021-08-03 zpy/client_util.py

@@ -124,7 +124,8 @@ def to_query_param_value(config):
     for django_field_traversal, django_field_value in config.items():
         # Ignore fields set as None. They weren't specifically set or asked for.
         if django_field_value is not None:
-            query_param_values.append(f"{django_field_traversal}:{django_field_value}")
+            query_param_values.append(
+                f"{django_field_traversal}:{django_field_value}")
     return ",".join(query_param_values)
 
 
@@ -193,18 +194,17 @@ def dict_hash(data) -> str:
 
 
 @track_runtime
-def extract_zip(path_to_zip: Path) -> Path:
+def extract_zip(path_to_zip: Path, output_path: Path):
     """
     Extracts a .zip to a new adjacent folder by the same name.
     Args:
         path_to_zip: Path to .zip
     Returns:
-        Path: Extracted folder path
+        None: No return value
     """
-    unzipped_path = Path(remove_n_extensions(path_to_zip, n=1))
     with zipfile.ZipFile(path_to_zip, "r") as zip_ref:
-        zip_ref.extractall(unzipped_path)
-    return unzipped_path
+        zip_ref.extractall(output_path)
+
 
 
 @track_runtime
@@ -290,7 +290,8 @@ def group_metadata_by_datapoint(
 
             # mutate
             image_new_id_map = {
-                img["id"]: datapoint_uuid + "".join(Path(img["name"]).suffixes[-2:])
+                img["id"]: datapoint_uuid +
+                "".join(Path(img["name"]).suffixes[-2:])
                 for img in images
             }
 
@@ -338,13 +339,16 @@ def format_dataset(
     Returns:
         None: No return value.
     """
-    unzipped_dataset_path = Path(remove_n_extensions(zipped_dataset_path, n=1))
-    if not unzipped_dataset_path.exists():
+    raw_dataset_path = Path(join(
+        Path(zipped_dataset_path).parent, Path(zipped_dataset_path).name + "_raw"
+    ))
+
+    if not raw_dataset_path.exists():
         print(f"Unzipping {zipped_dataset_path}...")
-        unzipped_dataset_path = extract_zip(zipped_dataset_path)
+        extract_zip(zipped_dataset_path, raw_dataset_path)
 
     metadata, categories, datapoints = group_metadata_by_datapoint(
-        unzipped_dataset_path
+        raw_dataset_path
     )
 
     if datapoint_callback is not None:
@@ -356,10 +360,8 @@ def format_dataset(
 
     else:
[…]

### 2021-08-03 zpy/client_util.py
Fix code style issues with Black

@@ -124,8 +124,7 @@ def to_query_param_value(config):
     for django_field_traversal, django_field_value in config.items():
         # Ignore fields set as None. They weren't specifically set or asked for.
         if django_field_value is not None:
-            query_param_values.append(
-                f"{django_field_traversal}:{django_field_value}")
+            query_param_values.append(f"{django_field_traversal}:{django_field_value}")
     return ",".join(query_param_values)
 
 
@@ -204,7 +203,6 @@ def extract_zip(path_to_zip: Path, output_path: Path):
     """
     with zipfile.ZipFile(path_to_zip, "r") as zip_ref:
         zip_ref.extractall(output_path)
-
 
 
 @track_runtime
@@ -290,8 +288,7 @@ def group_metadata_by_datapoint(
 
             # mutate
             image_new_id_map = {
-                img["id"]: datapoint_uuid +
-                "".join(Path(img["name"]).suffixes[-2:])
+                img["id"]: datapoint_uuid + "".join(Path(img["name"]).suffixes[-2:])
                 for img in images
             }
 
@@ -339,17 +336,15 @@ def format_dataset(
     Returns:
         None: No return value.
     """
-    raw_dataset_path = Path(join(
-        Path(zipped_dataset_path).parent, Path(zipped_dataset_path).name + "_raw"
-    ))
+    raw_dataset_path = Path(
+        join(Path(zipped_dataset_path).parent, Path(zipped_dataset_path).name + "_raw")
+    )
 
     if not raw_dataset_path.exists():
         print(f"Unzipping {zipped_dataset_path}...")
         extract_zip(zipped_dataset_path, raw_dataset_path)
 
-    metadata, categories, datapoints = group_metadata_by_datapoint(
-        raw_dataset_path
-    )
+    metadata, categories, datapoints = group_metadata_by_datapoint(raw_dataset_path)
 
     if datapoint_callback is not None:
         print("Skipping default formatting, using datapoint_callback instead.")

### 2021-08-04 test/client.py
fix Path vs str

@@ -157,7 +157,7 @@ class TestClientUtilMethods(unittest.TestCase):
                 metadata[tvt_type]["categories"][category_id]["count"] = count
 
             print(f"Writing {tvt_type} json...")
-            path = str(output_dir / tvt_type / "annotations.json")
+            path = output_dir / tvt_type / "annotations.json"
             blob = metadata[tvt_type]
             write_json(path, blob)
 
@@ -218,7 +218,7 @@ class TestClientUtilMethods(unittest.TestCase):
         dataset_config = zpy.DatasetConfig("dumpster_v5.1")
         dataset_config.set("run\.padding_style", "random")
         zpy.generate(
-            dataset_config, num_datapoints=100, datapoint_callback=datapoint_callback
+            dataset_config, num_datapoints=12,  # datapoint_callback=datapoint_callback
         )
 
         for tvt_type in ["train", "val", "test"]:
@@ -226,46 +226,6 @@ class TestClientUtilMethods(unittest.TestCase):
                 metadata[tvt_type]["categories"][category_id]["count"] = count
 
             print(f"Writing {tvt_type} json...")
-            path = str(output_dir / tvt_type / "annotations.json")
+            path = output_dir / tvt_type / "annotations.json"
             blob = metadata[tvt_type]
             write_json(path, blob)
-
-
-if __name__ == "__main__":
-    # unittest.main()
-    # unittest.main().test_generate()
-    # init_kwargs = {
-    #     "base_url": "http://localhost:8000",
-    #     "project_uuid": "aad8e2b2-5431-4104-a205-dc3b638b0dab",
-    #     "auth_token": "214540cbd525f1ecf2bc52e2ddb7ef76801048e3f55aa4b33a9e501b115a736e",
-    # }
-    init_kwargs = {
-        "base_url": "https://ragnarok.zumok8s.org",
-        "project_uuid": "feb6e594-55e0-4f87-9e75-5a128221499f",
-        "auth_token": "d656d40f144221aedcfa774bbf36b4caccf1e16de3f0ac2520d40d450da7bf2e",
-    }
-    # init_kwargs = {
-    #     "base_url": "https://ragnarok.stage.zumok8s.org",
-    #     "project_uuid": "91419af0-4815-41e7-9b77-5ef8154148c8",  # Compology
[…]

### 2021-08-04 zpy/client_util.py

@@ -209,7 +209,7 @@ def extract_zip(path_to_zip: Path, output_path: Path):
 def write_json(path, json_blob):
     """
     Args:
-        path (str): Path to output to.
+        path (Path or str): Path to output to.
         json_blob (obj): JSON serializable object.
     """
     with open(path, "w") as outfile:
@@ -359,7 +359,7 @@ def format_dataset(
         accum_metadata = {
             "metadata": {
                 **metadata,
-                "save_path": output_dir,
+                "save_path": str(output_dir),
             },
             "categories": {category["id"]: category for category in categories},
             "images": {},
@@ -374,21 +374,21 @@ def format_dataset(
                 original_image_uri = image["output_path"]
 
                 # build new path
-                output_image_uri = join(output_dir, image["id"])
+                output_image_uri = output_dir / image["id"]
 
                 # add to accumulator
                 accum_metadata["images"][image["id"]] = {
                     **image,
                     "name": image["id"],
                     "relative_path": image["id"],
-                    "output_path": join(output_dir, image["id"]),
+                    "output_path": str(output_dir / image["id"]),
                 }
 
                 # copy image to new folder
                 shutil.copy(original_image_uri, output_image_uri)
 
         # write json
-        metadata_output_path = join(output_dir, Path("_annotations.zumo.json"))
+        metadata_output_path = output_dir / "_annotations.zumo.json"
 
         os.makedirs(os.path.dirname(metadata_output_path), exist_ok=True)
         write_json(metadata_output_path, accum_metadata)

### 2021-08-04 test/client.py
Fix code style issues with Black

@@ -218,7 +218,8 @@ class TestClientUtilMethods(unittest.TestCase):
         dataset_config = zpy.DatasetConfig("dumpster_v5.1")
         dataset_config.set("run\.padding_style", "random")
         zpy.generate(
-            dataset_config, num_datapoints=12,  # datapoint_callback=datapoint_callback
+            dataset_config,
+            num_datapoints=12,  # datapoint_callback=datapoint_callback
         )
 
         for tvt_type in ["train", "val", "test"]:

### 2021-08-04 zpy/client.py

@@ -286,7 +286,9 @@ def generate(
         print(f"Sending generate request for Dataset<{internal_dataset_name}>...")
         print(json.dumps(dataset, indent=4, sort_keys=True))
     else:
-        print(f"Generate for Dataset<{internal_dataset_name}> has already been requested.")
+        print(
+            f"Generate for Dataset<{internal_dataset_name}> has already been requested."
+        )
         dataset = datasets_res["results"][0]
 
     if materialize:

### 2021-08-04 zpy/client_util.py

@@ -334,7 +334,9 @@ def format_dataset(
     Returns:
         None: No return value.
     """
-    raw_dataset_path = Path(zipped_dataset_path).parent / (Path(zipped_dataset_path).with_suffix('').name + "_raw")
+    raw_dataset_path = Path(zipped_dataset_path).parent / (
+        Path(zipped_dataset_path).with_suffix("").name + "_raw"
+    )
 
     if not raw_dataset_path.exists():
         print(f"Unzipping {zipped_dataset_path}...")

### 2021-08-04 zpy/client_util.py
add print out of default location

@@ -1,7 +1,6 @@
 import functools
 import hashlib
 import json
-import logging
 import math
 import os
 import shutil
@@ -352,8 +351,9 @@ def format_dataset(
             )
 
     else:
-        print("Doing default formatting for dataset...")
         output_dir = Path(remove_n_extensions(zipped_dataset_path, n=1))
+        print(f"Doing default formatting and outputting to {output_dir}")
+
         if Path(output_dir).exists():
             shutil.rmtree(output_dir)
         os.makedirs(output_dir)

### 2021-08-04 test/client.py
change materialize to download

@@ -1,66 +1,16 @@
-import json
 import os
 import random
 import shutil
 import unittest
 from collections import defaultdict
 from pathlib import Path
+from pprint import pprint
 
 import zpy.client as zpy
 from zpy.client_util import remove_n_extensions, format_dataset, write_json
 
 
-def test_1(**init_kwargs):
-    """In local env, simruns exist for config { "run.padding_style": "square" }"""
-    zpy.init(**init_kwargs)
-    dataset_config = zpy.DatasetConfig(sim_name="can_v7")
-    dataset_config.set("run\\.padding_style", "square")
-    print(dataset_config.config)
-    previews = zpy.preview(dataset_config)
-    urls = [preview["url"] for preview in previews]
-    print(json.dumps(urls, indent=4, sort_keys=True))
-
-
-def test_2(**init_kwargs):
-    """In local env, simruns do NOT exist for config { "run.padding_style": "messy" }"""
-    zpy.init(**init_kwargs)
-    dataset_config = zpy.DatasetConfig("can_v7")
-    dataset_config.set("run\\.padding_style", "messy")
-    print(dataset_config.config)
-    previews = zpy.preview(dataset_config)
-    urls = [preview["url"] for preview in previews]
-    print(json.dumps(previews, indent=4, sort_keys=True))
-    print(json.dumps(urls, indent=4, sort_keys=True))
-
-
-def pretty_print(object):
-    try:
-        json.dumps(object)
-    except TypeError:
-        print("Unable to serialize the object")
-    else:
-        print(json.dumps(object, indent=4))
-
-
-def test_generate(**init_kwargs):
-    zpy.init(**init_kwargs)
-    dataset_config = zpy.DatasetConfig("dumpster_v5.1")
-
-    def datapoint_callback(images, annotations, categories):
-        pretty_print(images)
-        pretty_print(annotations)
-        pretty_print(categories)
-
-    dataset = zpy.generate(
-        dataset_config,
-        num_datapoints=40,
-        materialize=True,
-        # datapoint_callback=datapoint_callback
-    )
-
-
-# https://docs.python.org/3/library/unittest.html#module-unittest
-class TestClientUtilMethods(unittest.TestCase):
+class TestClient(unittest.TestCase):
     def test_remove_n_extensions(self):
         self.assertTrue("/foo" == remove_n_extensions("/foo.rgb.png", 2))
[…]

### 2021-08-04 zpy/client.py

@@ -238,7 +238,7 @@ def preview(dataset_config: DatasetConfig, num_samples=10):
 def generate(
     dataset_config: DatasetConfig,
     num_datapoints: int = 10,
-    materialize: bool = True,
+    download: bool = True,
     datapoint_callback=None,
 ):
     """
@@ -248,9 +248,9 @@ def generate(
         num_datapoints (int): Number of datapoints in the dataset. A datapoint is an instant in time composed of all
                               the output images (rgb, iseg, cseg, etc) along with the annotations.
         datapoint_callback (fn): Callback function to be called with every datapoint in the generated Dataset.
-        materialize (bool): Optionally download the dataset. Defaults to True.
+        download (bool): Optionally download the dataset. Defaults to True.
     Returns:
-        None: No return value.
+        Dataset: The created Dataset.
     """
     dataset_config_hash = dataset_config.hash
     sim_name = dataset_config.sim["name"]
@@ -291,8 +291,8 @@ def generate(
         )
         dataset = datasets_res["results"][0]
 
-    if materialize:
-        print(f"Materializing Dataset<{internal_dataset_name}>...")
+    if download:
+        print(f"Downloading Dataset<{internal_dataset_name}>...")
         dataset = get(
             f"{_base_url}/api/v1/datasets/{dataset['id']}/",
             headers=auth_header(_auth_token),

### 2021-08-04 test/client.py
Fix code style issues with Black

@@ -29,7 +29,7 @@ class TestClient(unittest.TestCase):
         self.assertNotEqual(hash([1]), hash([1, 1]))
 
     def test_preview(self):
-        zpy.init(project_uuid='', auth_token='')
+        zpy.init(project_uuid="", auth_token="")
         dataset_config = zpy.DatasetConfig(sim_name="can_v7")
         dataset_config.set("run\\.padding_style", "square")
         previews = zpy.preview(dataset_config)

### 2021-08-04 test/client.py
change datapoint_callback to dataset_callback

@@ -46,70 +46,84 @@ class TestClient(unittest.TestCase):
         zpy.generate(dataset_config, num_datapoints=3)
 
     def test_format_dataset(self):
-        output_dir = Path("/home/korystiger/Downloads/ktest")
-        if output_dir.exists():
-            shutil.rmtree(output_dir)
+        def dataset_callback(datapoints, categories):
+            """
+            Args:
+                datapoints (list of dict of {images: [], annotations: []}): A list of all datapoints in the Dataset.
+                 A datapoint is a dict with keys `images` and `annotations`. Images is a list of the images in a
+                 datapoint (ie. rgb, iseg, cseg, depth, etc) and annotations is a list of the annotations describing
+                 the images.
+                categories (list of dict): A list of category objects describing the categories in the dataset.
+            """
+            # Setup directories
+            output_dir = Path("/home/korystiger/Downloads/ktest")
+            if output_dir.exists():
+                shutil.rmtree(output_dir)
 
-        os.makedirs(output_dir / "train", exist_ok=True)
-        os.makedirs(output_dir / "val", exist_ok=True)
-        os.makedirs(output_dir / "test", exist_ok=True)
+            os.makedirs(output_dir / "train", exist_ok=True)
+            os.makedirs(output_dir / "val", exist_ok=True)
+            os.makedirs(output_dir / "test", exist_ok=True)
 
-        metadata = {
-            tvt_type: {"categories": {}, "images": {}, "annotations": []}
-            for tvt_type in ["train", "val", "test"]
-        }
-        category_counts = {
-            tvt_type: defaultdict(int) for tvt_type in ["train", "val", "test"]
-        }
+            # Setup accumulators
+            metadata = {
+                tvt_type: {"categories": {}, "images": {}, "annotations": []}
+                for tvt_type in ["train", "val", "test"]
+            }
+            category_counts = {
+                tvt_type: defaultdict(int) for tvt_type in ["train", "val", "test"]
+            }
 
-        def datapoint_callback(images, annotations, categories):
-            r = random.random()
+            for datapoint in datapoints:
+                images = datapoint['images']
+                annotations = datapoint['annotations']
 
-            if r < 0.4:
-                tvt_type = "train"
-            elif r < 0.8:
-                tvt_type = "test"
-            else:
-                tvt_type = "val"
+                r = random.random()
 
-            for image in images:
-                new_path = output_dir / tvt_type / image["id"]
+                if r < 0.4:
+                    tvt_type = "train"
+                elif r < 0.8:
[…]

### 2021-08-04 zpy/client_util.py

@@ -268,10 +268,7 @@ def group_metadata_by_datapoint(
         for category_id, category in metadata["categories"].items():
             accum_categories[category_id] = category
 
-        images_grouped_by_datapoint = group_by(
-            values(metadata["images"]),
-            lambda image: remove_n_extensions(image["relative_path"], n=2),
-        )
+        images_grouped_by_datapoint = group_by(values(metadata["images"]), lambda image: image["frame"])
 
         # datapoint level
         for images in images_grouped_by_datapoint:
@@ -294,6 +291,7 @@ def group_metadata_by_datapoint(
                     **i,
                     "output_path": join(batch_uri, Path(i["relative_path"])),
                     "id": image_new_id_map[i["id"]],
+                    "frame": datapoint_uuid,
                 }
                 for i in images
             ]
@@ -302,6 +300,7 @@ def group_metadata_by_datapoint(
                 {
                     **a,
                     "image_id": image_new_id_map[a["image_id"]],
+                    "frame": datapoint_uuid,
                 }
                 for a in annotations
             ]
@@ -321,7 +320,7 @@ def group_metadata_by_datapoint(
 
 
 def format_dataset(
-    zipped_dataset_path: Union[str, Path], datapoint_callback=None
+        zipped_dataset_path: Union[str, Path], dataset_callback=None
 ) -> None:
     """
     Updates metadata with new ids and accurate image paths.
@@ -334,7 +333,7 @@ def format_dataset(
         None: No return value.
     """
     raw_dataset_path = Path(zipped_dataset_path).parent / (
-        Path(zipped_dataset_path).with_suffix("").name + "_raw"
+            Path(zipped_dataset_path).with_suffix("").name + "_raw"
     )
 
     if not raw_dataset_path.exists():
@@ -343,13 +342,9 @@ def format_dataset(
 
     metadata, categories, datapoints = group_metadata_by_datapoint(raw_dataset_path)
 
-    if datapoint_callback is not None:
-        print("Skipping default formatting, using datapoint_callback instead.")
-        for datapoint in datapoints:
-            datapoint_callback(
-                datapoint["images"], datapoint["annotations"], categories
-            )
-
+    if dataset_callback is not None:
+        print("Skipping default formatting, using dataset_callback instead.")
+        dataset_callback(datapoints, categories)
     else:
         output_dir = Path(remove_n_extensions(zipped_dataset_path, n=1))
         print(f"Doing default formatting and outputting to {output_dir}")

### 2021-08-04 test/client.py
Fix code style issues with Black

@@ -74,8 +74,8 @@ class TestClient(unittest.TestCase):
             }
 
             for datapoint in datapoints:
-                images = datapoint['images']
-                annotations = datapoint['annotations']
+                images = datapoint["images"]
+                annotations = datapoint["annotations"]
 
                 r = random.random()
 

### 2021-08-04 zpy/client_util.py

@@ -268,7 +268,9 @@ def group_metadata_by_datapoint(
         for category_id, category in metadata["categories"].items():
             accum_categories[category_id] = category
 
-        images_grouped_by_datapoint = group_by(values(metadata["images"]), lambda image: image["frame"])
+        images_grouped_by_datapoint = group_by(
+            values(metadata["images"]), lambda image: image["frame"]
+        )
 
         # datapoint level
         for images in images_grouped_by_datapoint:
@@ -320,7 +322,7 @@ def group_metadata_by_datapoint(
 
 
 def format_dataset(
-        zipped_dataset_path: Union[str, Path], dataset_callback=None
+    zipped_dataset_path: Union[str, Path], dataset_callback=None
 ) -> None:
     """
     Updates metadata with new ids and accurate image paths.
@@ -333,7 +335,7 @@ def format_dataset(
         None: No return value.
     """
     raw_dataset_path = Path(zipped_dataset_path).parent / (
-            Path(zipped_dataset_path).with_suffix("").name + "_raw"
+        Path(zipped_dataset_path).with_suffix("").name + "_raw"
     )
 
     if not raw_dataset_path.exists():

### 2021-08-04 docs/paper/paper.tex
results section wip

@@
 
-To put into practice what this paper has explained, we present an example of how synthetic data can be used to train a computer vision model.
-In this example, we train a detection model which is tasked with predicting the bounding boxes for packages and parcels in images.
-In section \ref{sec:domainrandomization} we explore the effect of some key dataset hyperparameters on the final model performance.
-In section \ref{sec:curicculum} we discuss how training curriculum can affect model performance when using synthetic data.
+To put into practice what this paper has explained, we present a simple example of how synthetic data can be used to train a computer vision model.
+In this example, we train a detection model which predicts the bounding boxes for cardboard packages and parcels in images.
+In section \ref{sec:domainrandomization} we explore how domain randomization in different aspects of the simulation can affect final model performance.
 
-Following the synthetic data workflow,
-
-Armed with our synthetic training dataset and our real test dataset, we are ready to do some model training.
-
-We used a ResNet model implemented in PyTorch inside of the Detectron2 computer vision library \cite{wu2019detectron2}.
-
-Each individual training run
-
-Details on the training setup: GPU, total training time, total number of sweeps, epoch and batch size.
+We used a variant of Faster R-CNN implemented in PyTorch as part of the Detectron2 model zoo \cite{wu2019detectron2}.
+Training was done on a single Nvidia GeForce RTX 3090, with each training run lasting at most an hour: this experiment consisted only of fine-tuning a model pre-trained on ImageNet as opposed to training a model from scratch.
+We sweeped over various learning rates and used the largest batch size we could given our GPU memory, model size, and image size.
+We picked the best performing permutation of hyperparameters when comparing results, keeping the model and test dataset consistent.
 
@@
 We perform an ablation study to pick appart the contributions of each type of domain randomization to the performance of a detection model trained on synthetic data with each respective form of domain randomization \ref{fig:results}.
+These toggles are used to create the following four synthetic training datasets:
 
-Deeper discussion of results
+\begin{itemize}
+	\item \lstinline{package_sim_dr_light} - Synthetic dataset of 512 images. Domain randomization is applied to lighting only.
+	\item \lstinline{package_sim_dr_mat} - Synthetic dataset of 512 images. Domain randomization is applied to materials only.
+	\item \lstinline{package_sim_dr_bg} - Synthetic dataset of 512 images. Domain randomization is applied to background only.
+	\item \lstinline{package_sim_dr_all} - Synthetic dataset of 512 images. Domain randomization is applied to lighting, background, and materials.
+\end{itemize}
 
-\subsection{Training Curicculum}
-\label{sec:curicculum}
-
-Pre-training w/ real and fine-tuning on synthetic
-
-Training only on Synthetic
-
-ref to rare planes
-
-ref to mixed synthetic data
+The best performing single run is fine tuned for XX iterations at a learning rate of XX on the \lstinline{package_sim_dr_all} dataset.
+By comparing the top performing runs for each type of domain randomization, we can thus rank the relative importance of each as such: lighting, materials, and background.
+One possible explanation may be that this XXX.
+Finally, as a caveat: it is important to underline that this is a small experiment, and we do not claim that these insights can be applied to other usecases or even further explorations of this particular problem.
 

### 2021-08-04 test/client.py
huge doc pass

@@ -7,7 +7,7 @@ from pathlib import Path
 from pprint import pprint
 
 import zpy.client as zpy
-from zpy.client_util import remove_n_extensions, format_dataset, write_json
+from zpy.client_util import remove_n_extensions, write_json
 
 
 class TestClient(unittest.TestCase):
@@ -126,54 +126,66 @@ class TestClient(unittest.TestCase):
         )
 
     def test_generate_and_format_dataset(self):
-        output_dir = Path("/home/korystiger/Downloads/ktest")
-        if output_dir.exists():
-            shutil.rmtree(output_dir)
+        def dataset_callback(datapoints, categories, output_dir):
+            if output_dir.exists():
+                shutil.rmtree(output_dir)
 
-        os.makedirs(output_dir / "train", exist_ok=True)
-        os.makedirs(output_dir / "val", exist_ok=True)
-        os.makedirs(output_dir / "test", exist_ok=True)
+            os.makedirs(output_dir / "train", exist_ok=True)
+            os.makedirs(output_dir / "val", exist_ok=True)
+            os.makedirs(output_dir / "test", exist_ok=True)
 
-        metadata = {
-            tvt_type: {"categories": {}, "images": {}, "annotations": []}
-            for tvt_type in ["train", "val", "test"]
-        }
-        category_counts = {
-            tvt_type: defaultdict(int) for tvt_type in ["train", "val", "test"]
-        }
+            metadata = {
+                tvt_type: {"categories": {}, "images": {}, "annotations": []}
+                for tvt_type in ["train", "val", "test"]
+            }
+            category_counts = {
+                tvt_type: defaultdict(int) for tvt_type in ["train", "val", "test"]
+            }
 
-        def datapoint_callback(images, annotations, categories):
-            r = random.random()
+            for datapoint in datapoints:
+                images = datapoint['images']
+                annotations = datapoint['annotations']
 
-            if r < 0.4:
-                tvt_type = "train"
-            elif r < 0.8:
-                tvt_type = "test"
-            else:
-                tvt_type = "val"
+                r = random.random()
 
-            for image in images:
-                new_path = output_dir / tvt_type / image["id"]
+                if r < 0.4:
+                    tvt_type = "train"
+                elif r < 0.8:
+                    tvt_type = "test"
+                else:
+                    tvt_type = "val"
 
-                shutil.copy(image["output_path"], new_path)
+                for image in images:
[…]

### 2021-08-04 zpy/client.py

@@ -1,11 +1,12 @@
 import functools
 import json
+import os
+import shutil
 import sys
 import time
 from datetime import datetime, timedelta
-from os import listdir
 from pathlib import Path
-from typing import Dict
+from typing import Dict, Optional
 from typing import Union
 
 import requests
@@ -21,8 +22,7 @@ from zpy.client_util import (
     auth_header,
     clear_last_print,
     is_done,
-    format_dataset,
-    dict_hash,
+    dict_hash, group_metadata_by_datapoint, extract_zip, write_json,
 )
 
 _auth_token: str = ""
@@ -178,6 +178,35 @@ class DatasetConfig:
         unset(self._config, path)
 
 
+class Dataset:
+    def __init__(self, name: str = None, dataset_config: DatasetConfig = None):
+        """
+        Construct a Dataset which is a local representation of a Dataset generated on the API.
+
+        Args:
+            name (str): The name of the Dataset.
+            dataset_config (DatasetConfig): The [zpy.client.DatasetConfig][] used to generate this Dataset.
+        """
+        self._name = name
+        self._config = dataset_config
+
+    @property
+    def name(self):
+        """
+        Returns:
+            str: The Dataset's name.
+        """
+        return self._name
+
+    @property
+    def config(self):
+        """
+        Returns:
+            DatasetConfig: The [zpy.client.DatasetConfig][] used to generate this Dataset.
+        """
+        return self._config
+
+
 @add_newline
 def preview(dataset_config: DatasetConfig, num_samples=10):
     """
@@ -234,23 +263,140 @@ def preview(dataset_config: DatasetConfig, num_samples=10):
     return files
 
 
+def default_dataset_callback(datapoints: list, categories: list, output_dir: Optional[Path]):
+    """
+    The default Dataset formatting function. It will flatten the Dataset into a single directory of images with a
+    single annotation file.
+
+    A Datapoint object is of the following shape:
+
+            {
+                "images": list of Image,
+                "annotations": list of Annotation,
+            }
+
+    An Image object is of the following shape:
+
+            {
+                # Globally unique identifier for the image
+                "id": uuid.uuid4(),
+
+                # Globally unique identifier for the datapoint (collection of images and annotations)
+                "datapoint_id": uuid.uuid4(),
+
+                # Absolute path to the image
+                "output_path": "absolute/path/to/image-name.file-suffix",
+
+                # Relative path to the image within its parent folder
+                "relative_path": "image-name.file-suffix",
+
+                # Name of the image without the file suffix
[…]

### 2021-08-04 zpy/client_util.py

@@ -2,8 +2,6 @@ import functools
 import hashlib
 import json
 import math
-import os
-import shutil
 import sys
 import uuid
 import zipfile
@@ -192,12 +190,13 @@ def dict_hash(data) -> str:
     return config_hash
 
 
-def extract_zip(path_to_zip: Path, output_path: Path):
+def extract_zip(path_to_zip: Union[str, Path], output_path: Union[str, Path]):
     """
-    Extracts a .zip to a new adjacent folder by the same name.
+    Extracts a .zip at `path_to_zip` to a directory at `output_path`.
+
     Args:
-        path_to_zip (Path): Path to .zip to extract.
-        output_path (Path): Path of where to extract to.
+        path_to_zip (Union[str, Path]): Location of .zip to extract.
+        output_path (Union[str, Path]): Location of where to extract to.
     Returns:
         None: No return value
     """
@@ -291,9 +290,9 @@ def group_metadata_by_datapoint(
             images_mutated = [
                 {
                     **i,
-                    "output_path": join(batch_uri, Path(i["relative_path"])),
                     "id": image_new_id_map[i["id"]],
-                    "frame": datapoint_uuid,
+                    "output_path": join(batch_uri, Path(i["relative_path"])),
+                    "datapoint_id": datapoint_uuid,
                 }
                 for i in images
             ]
@@ -301,8 +300,9 @@ def group_metadata_by_datapoint(
             annotations_mutated = [
                 {
                     **a,
+                    "id": str(uuid.uuid4()),
                     "image_id": image_new_id_map[a["image_id"]],
-                    "frame": datapoint_uuid,
+                    "datapoint_id": datapoint_uuid,
                 }
                 for a in annotations
             ]
@@ -319,75 +319,3 @@ def group_metadata_by_datapoint(
         accum_categories[category_id]["count"] = category_count
 
     return accum_metadata, values(accum_categories), accum_datapoints
-
-
-def format_dataset(
-    zipped_dataset_path: Union[str, Path], dataset_callback=None
-) -> None:
-    """
-    Updates metadata with new ids and accurate image paths.
-    If a datapoint_callback is provided, it is called once per datapoint with the updated metadata.
-    Otherwise the default is to write out an updated _annotations.zumo.json, along with all images, to a new adjacent folder.
-    Args:
-        zipped_dataset_path (str): Path to unzipped dataset.
-        datapoint_callback (Callable) -> None: User defined function.
-    Returns:
-        None: No return value.
-    """
[…]

### 2021-08-04 test/client.py
Fix code style issues with Black

@@ -143,8 +143,8 @@ class TestClient(unittest.TestCase):
             }
 
             for datapoint in datapoints:
-                images = datapoint['images']
-                annotations = datapoint['annotations']
+                images = datapoint["images"]
+                annotations = datapoint["annotations"]
 
                 r = random.random()
 
@@ -176,7 +176,10 @@ class TestClient(unittest.TestCase):
                 metadata[tvt_type]["annotations"].extend(annotations)
 
                 for category in categories:
-                    metadata[tvt_type]["categories"][category["id"]] = { **category, "count": 0}
+                    metadata[tvt_type]["categories"][category["id"]] = {
+                        **category,
+                        "count": 0,
+                    }
 
             for tvt_type in ["train", "val", "test"]:
                 for category_id, count in category_counts[tvt_type].items():
@@ -194,7 +197,5 @@ class TestClient(unittest.TestCase):
         dataset_config = zpy.DatasetConfig("dumpster_v5.1")
         dataset_config.set("run\.padding_style", "random")
         zpy.generate(
-            dataset_config,
-            num_datapoints=15,
-            dataset_callback=dataset_callback
+            dataset_config, num_datapoints=15, dataset_callback=dataset_callback
         )

### 2021-08-04 zpy/client.py

@@ -22,7 +22,10 @@ from zpy.client_util import (
     auth_header,
     clear_last_print,
     is_done,
-    dict_hash, group_metadata_by_datapoint, extract_zip, write_json,
+    dict_hash,
+    group_metadata_by_datapoint,
+    extract_zip,
+    write_json,
 )
 
 _auth_token: str = ""
@@ -263,7 +266,9 @@ def preview(dataset_config: DatasetConfig, num_samples=10):
     return files
 
 
-def default_dataset_callback(datapoints: list, categories: list, output_dir: Optional[Path]):
+def default_dataset_callback(
+    datapoints: list, categories: list, output_dir: Optional[Path]
+):
     """
     The default Dataset formatting function. It will flatten the Dataset into a single directory of images with a
     single annotation file.
@@ -381,10 +386,10 @@ def default_dataset_callback(datapoints: list, categories: list, output_dir: Opt
 
 @add_newline
 def generate(
-        dataset_config: DatasetConfig,
-        num_datapoints: int = 10,
-        download: bool = True,
-        dataset_callback=default_dataset_callback,
+    dataset_config: DatasetConfig,
+    num_datapoints: int = 10,
+    download: bool = True,
+    dataset_callback=default_dataset_callback,
 ):
     """
     Generate a dataset.
@@ -498,9 +503,13 @@ def generate(
                 print(f"Dataset<{dataset['name']}> already exists locally.")
 
             print(f"Formatting Dataset<{dataset['name']}>...")
-            metadata, categories, datapoints = group_metadata_by_datapoint(dataset_unzipped_path)
+            metadata, categories, datapoints = group_metadata_by_datapoint(
+                dataset_unzipped_path
+            )
 
-            dataset_callback(datapoints, categories, output_dir=dataset_zip_path.with_suffix(""))
+            dataset_callback(
+                datapoints, categories, output_dir=dataset_zip_path.with_suffix("")
+            )
         else:
             print(
                 f"Dataset<{dataset['name']}> is no longer running but cannot be downloaded with "

### 2021-08-04 test/client.py
remove old test

@@ -45,86 +45,6 @@ class TestClient(unittest.TestCase):
 
         zpy.generate(dataset_config, num_datapoints=3)
 
-    def test_format_dataset(self):
-        def dataset_callback(datapoints, categories):
-            """
-            Args:
-                datapoints (list of dict of {images: [], annotations: []}): A list of all datapoints in the Dataset.
-                 A datapoint is a dict with keys `images` and `annotations`. Images is a list of the images in a
-                 datapoint (ie. rgb, iseg, cseg, depth, etc) and annotations is a list of the annotations describing
-                 the images.
-                categories (list of dict): A list of category objects describing the categories in the dataset.
-            """
-            # Setup directories
-            output_dir = Path("/home/korystiger/Downloads/ktest")
-            if output_dir.exists():
-                shutil.rmtree(output_dir)
-
-            os.makedirs(output_dir / "train", exist_ok=True)
-            os.makedirs(output_dir / "val", exist_ok=True)
-            os.makedirs(output_dir / "test", exist_ok=True)
-
-            # Setup accumulators
-            metadata = {
-                tvt_type: {"categories": {}, "images": {}, "annotations": []}
-                for tvt_type in ["train", "val", "test"]
-            }
-            category_counts = {
-                tvt_type: defaultdict(int) for tvt_type in ["train", "val", "test"]
-            }
-
-            for datapoint in datapoints:
-                images = datapoint["images"]
-                annotations = datapoint["annotations"]
-
-                r = random.random()
-
-                if r < 0.4:
-                    tvt_type = "train"
-                elif r < 0.8:
-                    tvt_type = "test"
-                else:
-                    tvt_type = "val"
-
-                for image in images:
-                    new_path = output_dir / tvt_type / image["id"]
-
-                    shutil.copy(image["output_path"], new_path)
-
-                    metadata[tvt_type]["images"][image["id"]] = {
-                        **image,
-                        "output_path": str(new_path),
-                        "relative_path": image["id"],
-                        "name": image["id"],
-                    }
-
-                    filtered_annotations_by_image_id = [
-                        a for a in annotations if a["image_id"] == image["id"]
-                    ]
-                    for annotation in filtered_annotations_by_image_id:
-                        category_counts[tvt_type][annotation["category_id"]] += 1
-
-                metadata[tvt_type]["annotations"].extend(annotations)
-
-                for category in categories:
[…]

### 2021-08-04 zpy/client.py
move datapoint id out of images/annotations into datapoint

@@ -64,7 +64,6 @@ def init(
         )
 
 
-IMAGES_PER_SAMPLE = 2  # for the iseg and rbg
 DATASET_OUTPUT_PATH = Path("/tmp")  # for generate and default_saver_func
 
 
@@ -267,16 +266,22 @@ def preview(dataset_config: DatasetConfig, num_samples=10):
 
 
 def default_dataset_callback(
-    datapoints: list, categories: list, output_dir: Optional[Path]
+    datapoints: list, categories: list, output_dir: Path
 ):
     """
     The default Dataset formatting function. It will flatten the Dataset into a single directory of images with a
-    single annotation file.
+    single annotation json file.
 
     A Datapoint object is of the following shape:
 
             {
+                # Globally unique identifier for the datapoint
+                "id": uuid.uuid4(),
+
+                # The images in the datapoint
                 "images": list of Image,
+
+                # The annotations in the datapoint
                 "annotations": list of Annotation,
             }
 
@@ -285,9 +290,6 @@ def default_dataset_callback(
             {
                 # Globally unique identifier for the image
                 "id": uuid.uuid4(),
-
-                # Globally unique identifier for the datapoint (collection of images and annotations)
-                "datapoint_id": uuid.uuid4(),
 
                 # Absolute path to the image
                 "output_path": "absolute/path/to/image-name.file-suffix",
@@ -310,9 +312,6 @@ def default_dataset_callback(
 
                 # Id of the image which this annotation is describing.
                 "image_id": uuid.uuid4(),
-
-                # Id of the datapoint which this annotation belongs to.
-                "datapoint_id": uuid.uuid4(),
 
                 # There may be other arbitrary keys as per the Sim creator's discretion
                 ...
@@ -340,7 +339,7 @@ def default_dataset_callback(
     Args:
         datapoints (list of dict): List of Datapoint objects.
         categories (list of dict): List of Category objects.
-        output_dir (Optional[Path]): Default output location.
+        output_dir (Path): Default output location.
     Returns:
         None: No return value.
     """

### 2021-08-04 zpy/client_util.py

@@ -292,7 +292,6 @@ def group_metadata_by_datapoint(
                     **i,
                     "id": image_new_id_map[i["id"]],
                     "output_path": join(batch_uri, Path(i["relative_path"])),
-                    "datapoint_id": datapoint_uuid,
                 }
                 for i in images
             ]
@@ -302,7 +301,6 @@ def group_metadata_by_datapoint(
                     **a,
                     "id": str(uuid.uuid4()),
                     "image_id": image_new_id_map[a["image_id"]],
-                    "datapoint_id": datapoint_uuid,
                 }
                 for a in annotations
             ]
@@ -310,6 +308,7 @@ def group_metadata_by_datapoint(
             # accumulate
             accum_datapoints.append(
                 {
+                    "id": datapoint_uuid,
                     "images": images_mutated,
                     "annotations": annotations_mutated,
                 }

### 2021-08-04 docs/paper/paper.tex
updated results

@@
 We sweeped over various learning rates and used the largest batch size we could given our GPU memory, model size, and image size.
-We picked the best performing permutation of hyperparameters when comparing results, keeping the model and test dataset consistent.
+We picked the best performing permutation of hyperparameters when comparing results, using APm on a holdout test dataset of real images.
 
@@
 	\item \lstinline{package_sim_dr_light} - Synthetic dataset of 512 images. Domain randomization is applied to lighting only.
-	\item \lstinline{package_sim_dr_mat} - Synthetic dataset of 512 images. Domain randomization is applied to materials only.
+	\item \lstinline{package_sim_dr_mats} - Synthetic dataset of 512 images. Domain randomization is applied to materials only.
 	\item \lstinline{package_sim_dr_bg} - Synthetic dataset of 512 images. Domain randomization is applied to background only.
@@
 
-The best performing single run is fine tuned for XX iterations at a learning rate of XX on the \lstinline{package_sim_dr_all} dataset.
-By comparing the top performing runs for each type of domain randomization, we can thus rank the relative importance of each as such: lighting, materials, and background.
-One possible explanation may be that this XXX.
-Finally, as a caveat: it is important to underline that this is a small experiment, and we do not claim that these insights can be applied to other usecases or even further explorations of this particular problem.
+The best performing single run is fine tuned for 500 iterations at a learning rate of 0.001 on the \lstinline{package_sim_dr_mats} dataset.
+Comparing the top performing runs for each type of domain randomization, we rank the relative importance of each type: materials (44.9 APm), all (44.5 APm), lighting (42.1 APm), and background (40.4 APm).
+One possible explanation for material domain randomization being most important is that the shape of the cardboard box is the more important feature for the model to focus on (as opposed to the material and texture).
+As a caveat: it is important to underline that this is a small experiment: small models trained for a short amount of time on small datasets.
+We do not claim that these insights can be applied to other usecases or even further explorations of this particular problem.
 

### 2021-08-04 zpy/client.py
Fix code style issues with Black

@@ -265,9 +265,7 @@ def preview(dataset_config: DatasetConfig, num_samples=10):
     return files
 
 
-def default_dataset_callback(
-    datapoints: list, categories: list, output_dir: Path
-):
+def default_dataset_callback(datapoints: list, categories: list, output_dir: Path):
     """
     The default Dataset formatting function. It will flatten the Dataset into a single directory of images with a
     single annotation json file.

### 2021-08-05 test/client.py
updating objects to dicts

@@ -63,9 +63,6 @@ class TestClient(unittest.TestCase):
             }
 
             for datapoint in datapoints:
-                images = datapoint["images"]
-                annotations = datapoint["annotations"]
-
                 r = random.random()
 
                 if r < 0.4:
@@ -75,28 +72,30 @@ class TestClient(unittest.TestCase):
                 else:
                     tvt_type = "val"
 
-                for image in images:
-                    new_path = output_dir / tvt_type / image["id"]
+                # Annotations are stored by image_id so the dict update should not have any collisions
+                annotations = datapoint["annotations"]
+                metadata[tvt_type]["annotations"].update(annotations)
+
+                images = datapoint["images"]
+                for image_type, image in images.items():
+                    old_image_name = Path(image["output_path"]).name
+                    # Prefix old image name with the datapoint id to prevent naming collisions when moving directories
+                    # and combining images from other datapoints
+                    new_image_name = f'{datapoint["id"][:8]}.{old_image_name}'
+                    new_path = output_dir / tvt_type / new_image_name
+
+                    # Add the image and update the path to reflect its new location
+                    metadata[tvt_type]["images"][image["id"]] = image
+                    metadata[tvt_type]["images"][image["id"]]["output_path"] = str(new_path)
 
                     shutil.copy(image["output_path"], new_path)
 
-                    metadata[tvt_type]["images"][image["id"]] = {
-                        **image,
-                        "output_path": str(new_path),
-                        "relative_path": image["id"],
-                        "name": image["id"],
-                    }
-
-                    filtered_annotations_by_image_id = [
-                        a for a in annotations if a["image_id"] == image["id"]
-                    ]
-                    for annotation in filtered_annotations_by_image_id:
+                    # Add to the category counts for each annotation that this image has
+                    for annotation in annotations[image["id"]]:
                         category_counts[tvt_type][annotation["category_id"]] += 1
 
-                metadata[tvt_type]["annotations"].extend(annotations)
-
-                for category in categories:
-                    metadata[tvt_type]["categories"][category["id"]] = {
+                for category_id, category in categories.items():
+                    metadata[tvt_type]["categories"][category_id] = {
                         **category,
                         "count": 0,
                     }
@@ -117,5 +116,5 @@ class TestClient(unittest.TestCase):
         dataset_config = zpy.DatasetConfig("dumpster_v5.1")
         dataset_config.set("run\.padding_style", "random")
[…]

### 2021-08-05 zpy/client.py

@@ -4,9 +4,10 @@ import os
 import shutil
 import sys
 import time
+from collections import defaultdict
 from datetime import datetime, timedelta
 from pathlib import Path
-from typing import Dict, Optional
+from typing import Dict
 from typing import Union
 
 import requests
@@ -265,10 +266,10 @@ def preview(dataset_config: DatasetConfig, num_samples=10):
     return files
 
 
-def default_dataset_callback(datapoints: list, categories: list, output_dir: Path):
+def flatten_dataset(datapoints: list, categories: dict, output_dir: Path):
     """
-    The default Dataset formatting function. It will flatten the Dataset into a single directory of images with a
-    single annotation json file.
+    Used as the default Dataset formatting function. It will flatten the Dataset into a single directory of images
+    with a single annotation json file.
 
     A Datapoint object is of the following shape:
 
@@ -277,26 +278,26 @@ def default_dataset_callback(datapoints: list, categories: list, output_dir: Pat
                 "id": uuid.uuid4(),
 
                 # The images in the datapoint
-                "images": list of Image,
+                "images": dict of image_type to Image,
 
                 # The annotations in the datapoint
-                "annotations": list of Annotation,
+                "annotations": dict of image_id to Annotation,
             }
 
     An Image object is of the following shape:
 
             {
-                # Globally unique identifier for the image
-                "id": uuid.uuid4(),
+                # Locally unique identifier within the datapoint
+                "id": int,
 
                 # Absolute path to the image
-                "output_path": "absolute/path/to/image-name.file-suffix",
+                "output_path": "absolute/path/to/image.image-id.image-type.file-type-suffix",
 
                 # Relative path to the image within its parent folder
-                "relative_path": "image-name.file-suffix",
+                "relative_path": "image.image-id.image-type.file-type-suffix",
 
-                # Name of the image without the file suffix
-                "name": "image-name",
+                # Name of the image (Redundant with relative_path)
+                "name": "image.image-id.image-type.file-type-suffix",
 
                 # There may be other arbitrary keys as per the Sim creator's discretion
                 ...
@@ -305,11 +306,11 @@ def default_dataset_callback(datapoints: list, categories: list, output_dir: Pat
     An Annotation object is of the following shape:
 
             {
-                # Globally unique identifier for the annotation
-                "id": uuid.uuid4(),
+                # Locally unique identifier within the datapoint
[…]

### 2021-08-05 zpy/client_util.py

@@ -233,17 +233,42 @@ def group_by(iterable: Iterable, keyfunc: Callable) -> List[List]:
     ]
 
 
-def group_metadata_by_datapoint(
-    dataset_path: Path,
-) -> Tuple[Dict, List[Dict], List[Dict]]:
+def get_image_type_from_name(image_name):
     """
-    Updates metadata with new ids and accurate image paths.
-    Returns a list of dicts, each item containing metadata relevant to a single datapoint.
+    Extracts the image type from the name.
+
+    Args:
+        image_name (str): Name of the image in the format `image.000000.rgb.png`
+    Returns:
+        str: The type of the image. Ex: `"image.000000.rgb.png"` -> `"rgb"`, `"image.000123.iseg.jpg"` -> `"iseg"`
+    """
+    return image_name.split('.')[-2]
+
+
+def get_global_id(datapoint_uuid: str, local_id: int):
+    """
+    Creates a globally unique id by combining a locally unique id with its globally unique datapoint uuid.
+    
+    Args:
+        datapoint_uuid (str): Id of the datapoint.
+        local_id (int): Id of the local object (ex. image or annotation)
+    Returns:
+        str: The globally unique id of the local object.
+    """
+    return f'{datapoint_uuid[:8]}.{local_id}'
+
+
+def group_metadata_by_datapoint(
+        dataset_path: Path,
+) -> Tuple[Dict, Dict, List[Dict]]:
+    """
+    Aggregates and reformats the zumo metadata across all batches of a dataset.
+
     Args:
         dataset_path (Path): Path to unzipped dataset.
     Returns:
-        tuple (metadata: dict, categories: list[dict], datapoints: list[dict]): Returns a tuple of (metadata,
-            categories, datapoints), datapoints being a list of dicts, each containing a list of images and a list of
+        tuple (metadata: dict, categories: dict, datapoints: list[dict]): Returns a tuple of (metadata,
+            categories, datapoints), datapoints being a list of dicts, each containing a dict of images and a list of
             annotations.
     """
     accum_metadata = {}
@@ -251,70 +276,91 @@ def group_metadata_by_datapoint(
     accum_datapoints = []
     category_count_sums = defaultdict(int)
 
-    # batch level - group images by satapoint
+    # batch level - group images by datapoint
     for batch in listdir(dataset_path):
+        # Read batch specific zumo json file
         batch_uri = join(dataset_path, batch)
[…]

### 2021-08-05 test/client.py
adding actual test for csv formatter and fixing bug

@@ -1,3 +1,4 @@
+import csv
 import os
 import random
 import shutil
@@ -45,7 +46,7 @@ class TestClient(unittest.TestCase):
 
         zpy.generate(dataset_config, num_datapoints=3)
 
-    def test_generate_and_format_dataset(self):
+    def test_generate_and_tvt_format_dataset(self):
         def dataset_callback(datapoints, categories, output_dir):
             if output_dir.exists():
                 shutil.rmtree(output_dir)
@@ -108,6 +109,64 @@ class TestClient(unittest.TestCase):
                 path = output_dir / tvt_type / "annotations.json"
                 blob = metadata[tvt_type]
                 write_json(path, blob)
+
+        zpy.init(
+            project_uuid="feb6e594-55e0-4f87-9e75-5a128221499f",
+            auth_token="12ea8d406b508be8fd0a1fef78f825440347fb10989536fcd1dedb9241327491",
+        )
+        dataset_config = zpy.DatasetConfig("dumpster_v5.1")
+        dataset_config.set("run\.padding_style", "random")
+        zpy.generate(
+            dataset_config, num_datapoints=15, #  dataset_callback=dataset_callback
+        )
+
+    def test_generate_and_csv_format_dataset(self):
+        def dataset_callback(datapoints, categories, output_dir):
+            """
+            Example of using dataset_callback to format a dataset into CSV format.
+
+            See [zpy.client.default_dataset_callback][] for how the dataset is flattened by default.
+
+            Args:
+                datapoints (list): List of datapoints. See [zpy.client.default_dataset_callback][].
+                categories (dict): Dict of category_id to Category. See [zpy.client.default_dataset_callback][].
+                output_dir (Path): Path of where dataset is output normally. You can use it or use something else.
+            """
+            # The default location is passed in, but you can change it to whatever you want
+            output_dir = Path('/tmp/output_dir')
+            if output_dir.exists():
+                shutil.rmtree(output_dir)
+            os.makedirs(output_dir, exist_ok=True)
+
+            # Define row accumulator
+            rows = []
+            # Loop over datapoints to build rows
+            for datapoint in datapoints:
+                # Dict of image_type to image
+                images = datapoint['images']
+
+                # Get annotations via the image id
+                rgb_annotations = datapoint['annotations'][images['rgb']['id']]
+                # iseg_annotations = datapoint['annotations'][images['iseg']['id']]
+
+                # The Sim design determines the annotation intrinsics. In this example we know there is only
[…]

### 2021-08-05 zpy/client.py

@@ -342,8 +342,6 @@ def flatten_dataset(datapoints: list, categories: dict, output_dir: Path):
     Returns:
         None: No return value.
     """
-    print(f"Doing default formatting and outputting to {output_dir}")
-
     if Path(output_dir).exists():
         shutil.rmtree(output_dir)
     os.makedirs(output_dir)
@@ -504,13 +502,14 @@ def generate(
                 dataset_unzipped_path
             )
 
+            dataset_callback_output_dir = dataset_zip_path.with_suffix("")
             if dataset_callback:
                 print("Calling user defined dataset_callback...")
-                dataset_callback(datapoints, categories, dataset_zip_path.with_suffix(""))
+                dataset_callback(datapoints, categories, dataset_callback_output_dir)
                 print("User defined dataset_callback has finished.")
             else:
-                print(f"Flattening Dataset<{dataset['name']}>...")
-                flatten_dataset(datapoints, categories, dataset_zip_path.with_suffix(""))
+                print(f"Flattening Dataset<{dataset['name']}> to {dataset_callback_output_dir}...")
+                flatten_dataset(datapoints, categories, dataset_callback_output_dir)
         else:
             print(
                 f"Dataset<{dataset['name']}> is no longer running but cannot be downloaded with "

### 2021-08-05 test/client.py
Fix code style issues with Black

@@ -87,7 +87,9 @@ class TestClient(unittest.TestCase):
 
                     # Add the image and update the path to reflect its new location
                     metadata[tvt_type]["images"][image["id"]] = image
-                    metadata[tvt_type]["images"][image["id"]]["output_path"] = str(new_path)
+                    metadata[tvt_type]["images"][image["id"]]["output_path"] = str(
+                        new_path
+                    )
 
                     shutil.copy(image["output_path"], new_path)
 
@@ -117,7 +119,8 @@ class TestClient(unittest.TestCase):
         dataset_config = zpy.DatasetConfig("dumpster_v5.1")
         dataset_config.set("run\.padding_style", "random")
         zpy.generate(
-            dataset_config, num_datapoints=15, #  dataset_callback=dataset_callback
+            dataset_config,
+            num_datapoints=15,  #  dataset_callback=dataset_callback
         )
 
     def test_generate_and_csv_format_dataset(self):
@@ -133,7 +136,7 @@ class TestClient(unittest.TestCase):
                 output_dir (Path): Path of where dataset is output normally. You can use it or use something else.
             """
             # The default location is passed in, but you can change it to whatever you want
-            output_dir = Path('/tmp/output_dir')
+            output_dir = Path("/tmp/output_dir")
             if output_dir.exists():
                 shutil.rmtree(output_dir)
             os.makedirs(output_dir, exist_ok=True)
@@ -143,28 +146,28 @@ class TestClient(unittest.TestCase):
             # Loop over datapoints to build rows
             for datapoint in datapoints:
                 # Dict of image_type to image
-                images = datapoint['images']
+                images = datapoint["images"]
 
                 # Get annotations via the image id
-                rgb_annotations = datapoint['annotations'][images['rgb']['id']]
+                rgb_annotations = datapoint["annotations"][images["rgb"]["id"]]
                 # iseg_annotations = datapoint['annotations'][images['iseg']['id']]
 
                 # The Sim design determines the annotation intrinsics. In this example we know there is only
                 # one annotation per datapoint, but there could be all sorts of interesting metadata here!
-                category_id = rgb_annotations[0]['category_id']
+                category_id = rgb_annotations[0]["category_id"]
 
                 # Lookup category information if you need it
                 # category = categories[category_id]
 
                 # Accumulate new row
-                row = (datapoint['id'], images['rgb']['output_path'], category_id)
[…]

### 2021-08-05 zpy/client.py

@@ -508,7 +508,9 @@ def generate(
                 dataset_callback(datapoints, categories, dataset_callback_output_dir)
                 print("User defined dataset_callback has finished.")
             else:
-                print(f"Flattening Dataset<{dataset['name']}> to {dataset_callback_output_dir}...")
+                print(
+                    f"Flattening Dataset<{dataset['name']}> to {dataset_callback_output_dir}..."
+                )
                 flatten_dataset(datapoints, categories, dataset_callback_output_dir)
         else:
             print(

### 2021-08-05 zpy/client_util.py

@@ -242,24 +242,24 @@ def get_image_type_from_name(image_name):
     Returns:
         str: The type of the image. Ex: `"image.000000.rgb.png"` -> `"rgb"`, `"image.000123.iseg.jpg"` -> `"iseg"`
     """
-    return image_name.split('.')[-2]
+    return image_name.split(".")[-2]
 
 
 def get_global_id(datapoint_uuid: str, local_id: int):
     """
     Creates a globally unique id by combining a locally unique id with its globally unique datapoint uuid.
-    
+
     Args:
         datapoint_uuid (str): Id of the datapoint.
         local_id (int): Id of the local object (ex. image or annotation)
     Returns:
         str: The globally unique id of the local object.
     """
-    return f'{datapoint_uuid[:8]}.{local_id}'
+    return f"{datapoint_uuid[:8]}.{local_id}"
 
 
 def group_metadata_by_datapoint(
-        dataset_path: Path,
+    dataset_path: Path,
 ) -> Tuple[Dict, Dict, List[Dict]]:
     """
     Aggregates and reformats the zumo metadata across all batches of a dataset.
@@ -325,7 +325,9 @@ def group_metadata_by_datapoint(
                 if "frame" in updated_image:
                     del updated_image["frame"]
 
-                image_type_to_image[get_image_type_from_name(image["name"])] = updated_image
+                image_type_to_image[
+                    get_image_type_from_name(image["name"])
+                ] = updated_image
 
             # Get datapoint specific annotations
             image_ids = [i["id"] for i in images]
@@ -361,6 +363,6 @@ def group_metadata_by_datapoint(
         accum_categories[int(category_id)]["count"] = category_count
 
     # save_path doesn't have meaning any more. Batches are combined in memory but haven't been relocated to one spot.
-    del accum_metadata['save_path']
+    del accum_metadata["save_path"]
 
     return accum_metadata, accum_categories, accum_datapoints

### 2021-08-05 docs/paper/paper.tex
wording cleanup

@@
 The nature of statistical learning methods means that training on these biased datasets will result in a biased model since a model is only as good as the data on which it is trained.
-The pervasive use of data-driven algorithms has complex social implications: from racial facial recognition (citation: https://nvlpubs.nist.gov/nistpubs/ir/2019/NIST.IR.8280.pdf), to predictive policing systems that act to confirm and deepen existing biases (citation: https://www.technologyreview.com/2020/07/17/1005396/predictive-policing-algorithms-racist-dismantled-machine-learning-bias-criminal-justice/).
+The pervasive use of data-driven algorithms has complex social implications: from racial facial recognition \cite{fvrt}, to predictive policing systems that act to confirm and deepen existing biases \cite{predictivepolicing}.
+
 \subsection{Privacy}
@@
 
-\begin{lstlisting}[language=Python,caption={Generating a dataset using the zpy python API.},label={lst:api}]
+\begin{lstlisting}[language=Python,caption={Generating a dataset of 1000 images using the zpy python API.},label={lst:api}]
 import zpy
-zpy.generate()
+zpy.generate("hello world dataset", 1000)
 \end{lstlisting}
 
-\begin{lstlisting}[language=bash,caption={Generating a dataset using the zpy CLI},label={lst:cli}]
+\begin{lstlisting}[language=bash,caption={Generating a dataset of 1000 images using the zpy CLI},label={lst:cli}]
 zpy create dataset "hello world dataset" my_sim num_images 1000
@@
 	\includegraphics[width=\textwidth]{results.png}
-	\caption{Each type of domain randomization is used to create a fully synthetic dataset, which is used to fine-tune a pre-trained model on the task of package detection.
-Results of the model on a manually labeled test dataset of real images are compared.}
+	\caption{(Left) Sample images from synthetic training datasets with different kinds of domain randomization: lighting, background, material, and all of the above.
+(Right) Bounding box predictions of a model fine-tuned on the corresponding synthetic dataset along with confidence for each detection, false positives shown for context.}
 	\label{fig:results}
@@
 In this example, we train a detection model which predicts the bounding boxes for cardboard packages and parcels in images.
+In section \ref{sec:trainingmodel} we provide some details on the model and training setup.
 In section \ref{sec:domainrandomization} we explore how domain randomization in different aspects of the simulation can affect final model performance.
 
-We used a variant of Faster R-CNN implemented in PyTorch as part of the Detectron2 model zoo \cite{wu2019detectron2}.
-Training was done on a single Nvidia GeForce RTX 3090, with each training run lasting at most an hour: this experiment consisted only of fine-tuning a model pre-trained on ImageNet as opposed to training a model from scratch.
+\subsection{Training and Model Specs}
+\label{sec:trainingmodel}
+
+We used several variants of Faster R-CNN implemented in PyTorch as part of the Detectron2 model zoo \cite{wu2019detectron2}.
+Training was done on a single Nvidia GeForce RTX 3090, with each training run lasting at most several thousand iterations, which corresponds to at most 10 epochs given the training dataset size of 512 images.
+For this experiment we fine-tune a model pre-trained on the COCO detection task as opposed to training the model from scratch.
+This type of transfer learning is common when using machine learning in the real world due to the quick training speed and relatively good performance.
 We sweeped over various learning rates and used the largest batch size we could given our GPU memory, model size, and image size.
@@
 \begin{itemize}
-	\item \lstinline{package_sim_dr_light} - Synthetic dataset of 512 images. Domain randomization is applied to lighting only.
-	\item \lstinline{package_sim_dr_mats} - Synthetic dataset of 512 images. Domain randomization is applied to materials only.
-	\item \lstinline{package_sim_dr_bg} - Synthetic dataset of 512 images. Domain randomization is applied to background only.
+	\item \lstinline{package_sim_dr_light} - Synthetic dataset of 512 images.
+Domain randomization is applied to lighting only.
+The position of a sun light object in the scene, as well as the intensity of the light, is randomized within a range for every image
+	\item \lstinline{package_sim_dr_mats} - Synthetic dataset of 512 images.
+Domain randomization is applied to materials only.
+The material of each individial package is created in each image, starting with a randomly chosen texture from a library of thousands of textures scraped from the internet.
+Several properties of the material, such as specular, metallic, and roughness are then jittered within a broad range.
+	\item \lstinline{package_sim_dr_bg} - Synthetic dataset of 512 images.
+Domain randomization is applied to background only.
+Each image is rendered with a different HDRI, which is chosen from a library of hundreds of HDRIs scraped from the internet.
 	\item \lstinline{package_sim_dr_all} - Synthetic dataset of 512 images. Domain randomization is applied to lighting, background, and materials.

### 2021-08-06 docs/paper/paper.tex

@@
 \author{
-	{\hspace{1mm}Hugo Ponte}\footnote{Correspondence author} \\ 
+	{\hspace{1mm}Hugo Ponte} \footnote{Correspondence author} \\ 
 	Zumo Labs \\
@@
 % Uncomment to remove the date
-\date{}
+\date{\emph{Updated on August 6, 2021}}
 
@@
 Synthetic data presents a unique solution to the huge data requirements of computer vision with deep learning.
-In this work, we present zpy \footnote{All code is available on GitHub at \url{http://github.com/ZumoLabs/zpy}}, an open source framework for creating synthetic data.
+In this work, we present zpy, an open source framework for creating synthetic data in Python.
 Built on top of the popular open source 3D toolset Blender, zpy is designed with accessibility and readability in mind.
@@
 We make the case for why open source synthetic data is important to solve issues such as fairness and bias by democratizing access to data.
+Finally, we explore the effect of different types of domain randomization on synthetic training data by fine tuning a CNN on small synthetic training datasets and testing the model on a holdout test dataset of real images.
+All code is available on GitHub at \url{http://github.com/ZumoLabs/zpy}
 \end{abstract}
@@
 Synthetic data is data that is \emph{created} as opposed to \emph{collected}.
+Datasets are designed by engineers and researchers such that a statistical learning system trained on this data will behave more predictably and sometimes even perform better.
+Synthetic data goes beyond curation and allows engineers and researchers to carefully craft the distribution of training data, making sure it has variety in the dimmensions that need it and consistency in other dimmensions.
 
 Simulation heavy fields were amongst the first to start using synthetic images to start training deep learning systems.
-Research with the biggest datasets and highest quality can be found in this field, with works on autonomous vehicles \cite{prakash2020structured} \cite{srivastava2019multi} \cite{Hahner_2019} \cite{7780721}, robotic grasping \cite{james2019simtoreal} \cite{tobin2017domain}, and even drone racing \cite{Loquercio_2020}.
+Research with the biggest datasets and highest quality can be found in these fields, with works on autonomous vehicles \cite{prakash2020structured} \cite{srivastava2019multi} \cite{Hahner_2019} \cite{7780721}, robotic grasping \cite{james2019simtoreal} \cite{tobin2017domain}, and even drone racing \cite{Loquercio_2020}.
 The availability of high quality 3D humans from the video game and movie industries has also made possible applications such as human pose estimation  \cite{shrivastava2017learning} \cite{Varol_2017}, and person re-id \cite{aaronASRC}.
@@
 
-Data creation as a new paradigm for “programming”.
+In the software world today, developers write explicit sets of rules also known as algorithms.
+These algorithms are deployed into production systems, where they consume inputs (i.e.
+images, text, speech) and produce outputs (i.e.
+actions, predictions, labels) \ref{fig:fig2}.
+The relationship between outputs and inputs is carefully managed and designed by developers, and edge cases are identified and bubbled up as exceptions before they can cause unwanted behavior.
+We nickname this type of explicit heuristic design as \emph{Software 2.0}.
 
-In the software world today, developers write explicit sets of rules (known as algorithms). These algorithms are then deployed into production systems, which consume input data and output actions.
-
-In the software of tomorrow, developers will curate a dataset which will be used to train a deep learning model.
-This model will then be deployed into a production system, which will consume input data and output actions.
-This changes the workflow of developers from explicitly writing rules to instead creating the datasets which are then parsed to create algorithms.
+Machine learning based systems, which we nickname \emph{Software 3.0} works differently from these explicitly designed algorithms.
+Machine learning systems are trained on a dataset, and their behavior in production is often not predictable.
+Instead of spending their time designing the set of rules that define behavior, or \emph{programming}, we predict the developers of tomorrow will instead spend their time designing a dataset, on which a machine learning system is trained.
+By designing the dataset, developers will be able to better understand and even make guarantees on the behavior of the machine learning algorithms in production systems.
+This fundamentally changes the workflow of system development from explicitly writing rules to instead designing datasets, and as such the tools and methods used for programming today will be replaced by dataset design and curation tools.
 
@@
 	\caption{(Left) Sample images from synthetic training datasets with different kinds of domain randomization: lighting, background, material, and all of the above.
-(Right) Bounding box predictions of a model fine-tuned on the corresponding synthetic dataset along with confidence for each detection, false positives shown for context.}
+(Right) Bounding box predictions of a model fine-tuned on the corresponding synthetic dataset along with confidence for each detection.}
 	\label{fig:results}
@@
 The best performing single run is fine tuned for 500 iterations at a learning rate of 0.001 on the \lstinline{package_sim_dr_mats} dataset.
-Comparing the top performing runs for each type of domain randomization, we rank the relative importance of each type: materials (44.9 APm), all (44.5 APm), lighting (42.1 APm), and background (40.4 APm).
+Comparing the top performing runs for each type of domain randomization, we rank the relative importance of each type: all (46.3 APm), materials (44.9 APm),  lighting (42.1 APm), and background (40.4 APm).
 One possible explanation for material domain randomization being most important is that the shape of the cardboard box is the more important feature for the model to focus on (as opposed to the material and texture).
@@
 
+Synthetic data, data that is \emph{created} as opposed to \emph{collected}, presents a unique solution to the huge data requirements of computer vision with deep learning.
+The software for the design and creation of synthetic datasets are still primitive, and in this paper we present our attempt at this new type of developer tool: zpy, an open source framework for creating synthetic data in Python.
+Built on top of the popular open source 3D toolset Blender, zpy is designed with accessibility and readability in mind.
+Open source synthetic data toolkits like zpy are the bridge between the more mature tools of the 3D workflow and the machine learning frameworks.
+We make the case for why open source synthetic data is important to solve issues such as fairness and bias by democratizing access to data.
+Finally, we explore the effect of different types of domain randomization on synthetic training data by fine tuning a CNN on small synthetic training datasets and testing the model on a holdout test dataset of real images.
+All code is available on GitHub at \url{http://github.com/ZumoLabs/zpy}
+
 \section{Thanks}
@@
 
-Thanks to Aaron Dant and his team at ASRC Federal for discussions about synthetic data and comments on this paper.
  Thanks to the developer community of zpy for their feedback and contributions.
 Thanks to the investors and supporters of Zumo Labs for believing in the future of synthetic data.
+Thanks to Aaron Dant and his team at ASRC Federal for discussions about synthetic data and comments on this paper.
 
